---
title: "Social environmental (i.e. geospatial) RECORD"
output: html_document
---
# Connecting with Opal data server
## Login to server and assign study data
```{r, echo=FALSE}
#Load Opal R library
library(opal)
library(dplyr)
# Create an opal object with the login information
erasmus_opal <- opal.login()
#Login to Opal server and assign the content of the RECORD table(s) to your RStudio environment
# RECORD wave 1, part 1
opal.assign.table.tibble(erasmus_opal, 'RECORD_w1_1', 'RECORD.RECORD_w1_1', variables = list(' '))
RECORD_w1_1 <- opal.execute(erasmus_opal,'RECORD_w1_1')
# RECORD wave 1, part 2
opal.assign.table.tibble(erasmus_opal, 'RECORD_w1_2', 'RECORD.RECORD_w1_2', variables = list('' )) 
RECORD_w1_2<- opal.execute(erasmus_opal,'RECORD_w1_2')
# RECORD wave 2
opal.assign.table.tibble(erasmus_opal, 'RECORD_w2', 'RECORD.RECORD_W2',variables=list('')) 
RECORD_w2 <- opal.execute(erasmus_opal,'RECORD_w2')
```
## Assign participant id as first column of your harmonized dataframes
```{r, echo=FALSE}
socenv_RECORD_0 <- data.frame(id = RECORD_w1_1$id)
socenv_RECORD_1 <- data.frame(id = RECORD_w2$id)
```

## When you are done with your work, logout of Opal server
```{r, echo=FALSE}
opal.logout(erasmus_opal) 
```
---
# Table of Contents
1. [Urbanization grade](#Urbanization grade)  
2. [Demographics](#Demographics)  
3. [Housing](#Housing)  
4. [Income](#Income)  
5. [Unemployment](#Unemployment)  
6. [Social security](#Social security)  
7. [Educational level](#Educational level)  
8. [Immigrants and ethnic minority groups](#Immigrants and ethnic minority groups)
9. [Crime](#Crime)  
  

# Urbanization grade

### **Variable label**: Urbanization grade in 2006  
**Variable name**: socenv_urbanization_grade_2006    
**Variable description**: Population density of the residential area (number of residents per km2) in 2006.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:
For RECORD, these data are available for neighbourhoods in 2009 and 2014, not in 2006.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  

### **Variable label**: Urbanization grade in 2007 
**Variable name**: socenv_urbanization_grade_2007    
**Variable description**: Population density of the residential area (number of residents per km2) in 2007.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
For RECORD, these data are available for neighbourhoods in 2009 and 2014, not in 2007.
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  

### **Variable label**: Urbanization grade in 2009 
**Variable name**: socenv_urbanization_grade_2009    
**Variable description**: Population density of the residential area (number of residents per km2) in 2009.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete 
**Harmonization comment**:  For RECORD, these data are available for neighbourhoods in 2009 and 2014. This variable was calculated by: number of residents in area / area size. This variable has been linked to cohort respondents using their 5-digit postal code. References to the original data sources are listed in the WP7 deliverable report. 
**R script**:  
```{r, echo=TRUE}
socenv_RECORD_2009_W1$socenv_urbanization_grade_2009<-as.integer(RECORD_W1_SocioEnviro$URBANIZATION_GRADE_2009) 

socenv_RECORD_2009_W2$socenv_urbanization_grade_2009<-as.integer(RECORD_W2_SocioEnviro$URBANIZATION_GRADE_2009) 

```  

### **Variable label**: Urbanization grade in 2011 
**Variable name**: socenv_urbanization_grade_2011    
**Variable description**: Population density of the residential area (number of residents per km2) in 2011.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**: 
For RECORD, these data are available for neighbourhoods in 2009 and 2014, not in 2006.
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  

### **Variable label**: Urbanization grade in 2014
**Variable name**: socenv_urbanization_grade_2014    
**Variable description**: Population density of the residential area (number of residents per km2) in 2014.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete 
**Harmonization comment**:  For RECORD, these data are available for neighbourhoods in 2009 and 2014. This variable was calculated by: number of residents in area / area size. This variable has been linked to cohort respondents using their 5-digit postal code. References to the original data sources are listed in the WP7 deliverable report. 
**R script**:  
```{r, echo=TRUE}
socenv_RECORD_2014_W1$socenv_urbanization_grade_2014<-as.integer(RECORD_W1_SocioEnviro$URBANIZATION_GRADE_2014) 

socenv_RECORD_2014_W2$socenv_urbanization_grade_2014<-as.integer(RECORD_W2_SocioEnviro$URBANIZATION_GRADE_2014) 
```    



# Demographics

### **Variable label**: Proportion of men in 2006  
**Variable name**: socenv_proportion_men_2006    
**Variable description**: Proportion of men in the residential area in 2006.  
**Variable type**: decimal
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of men in 2011  
**Variable name**: socenv_proportion_men_2011    
**Variable description**: Proportion of men in the residential area in 2011.  
**Variable type**: decimal
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of women in 2006  
**Variable name**: socenv_proportion_women_2006    
**Variable description**: Proportion of women in the residential area in 2006.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of women in 2011    
**Variable name**: socenv_proportion_women_2011    
**Variable description**: Proportion of women in the residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of residents aged 65 or older in 2006   
**Variable name**: socenv_proportion_65_older_2006   
**Variable description**: Proportion of residents aged 65 or older in residential area in 2006.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of residents aged 65 or older in 2007   
**Variable name**: socenv_proportion_65_older_2007   
**Variable description**: Proportion of residents aged 65 or older in residential area in 2007.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:   
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of residents aged 65 or older in 2011   
**Variable name**: socenv_proportion_65_older_2011   
**Variable description**: Proportion of residents aged 65 or older in residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of unmaried residents in 2008   
**Variable name**: socenv_proportion_unmaried_2008   
**Variable description**: Proportion of unmaried residents in residential area in 2008.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of unmaried residents in 2011   
**Variable name**: socenv_proportion_unmaried_2011   
**Variable description**: Proportion of unmaried residents in residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of maried residents in 2006   
**Variable name**: socenv_proportion_maried_2006   
**Variable description**: Proportion of maried residents in residential area in 2006.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of maried residents in 2008   
**Variable name**: socenv_proportion_maried_2008   
**Variable description**: Proportion of maried residents in residential area in 2008.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of maried residents in 2011   
**Variable name**: socenv_proportion_maried_2011   
**Variable description**: Proportion of maried residents in residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of divorced residents in 2006   
**Variable name**: socenv_proportion_divorced_2006   
**Variable description**: Proportion of divorced residents in residential area in 2006.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of divorced residents in 2008   
**Variable name**: socenv_proportion_divorced_2008   
**Variable description**: Proportion of divorced residents in residential area in 2008.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of divorced residents in 2011   
**Variable name**: socenv_proportion_divorced_2011   
**Variable description**: Proportion of divorced residents in residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of widowed residents in 2006   
**Variable name**: socenv_proportion_widowed_2006   
**Variable description**: Proportion of widowed residents in residential area in 2006.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of widowed residents in 2008     
**Variable name**: socenv_proportion_widowed_2008   
**Variable description**: Proportion of widowed residents in residential area in 2008.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of widowed residents in 2011    
**Variable name**: socenv_proportion_widowed_2011   
**Variable description**: Proportion of widowed residents in residential area in 2011.  
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:   
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average household size in 2006   
**Variable name**: socenv_average_hh_size_2006   
**Variable description**: Average household size in residential area in 2006.  
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**: 
For RECORD, these data are available for neighbourhoods in 2014, not in 2006.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average household size in 2009   
**Variable name**: socenv_average_hh_size_2009   
**Variable description**: Average household size in residential area in 2009.  
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**: 
For RECORD, these data are available for neighbourhoodsin 2014, not in 2009. 
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average household size in 2011   
**Variable name**: socenv_average_hh_size_2011   
**Variable description**: Average household size in residential area in 2011.  
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**: 
For RECORD, these data are available for neighbourhoods in 2014, not in 2011. 
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average household size in 2014   
**Variable name**: socenv_average_hh_size_2014   
**Variable description**: Average household size in residential area in 2014.  
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  complete
**Harmonization comment**: 
For RECORD, these data are available for neighbourhoods in 2014. This variable was calculated by: total number of residents in area / total number of households in area * 100. This variable has been linked cohort respondents using their 5-digit postal code.References of all data sources are listed in the WP7 deliverable report.
**R script**:  
```{r, echo=TRUE}  
socenv_RECORD_2014_W1$socenv_average_hh_size_2014<-as.integer(RECORD_W1_SocioEnviro$AVERAGE_HOUSEHOLD_SIZE_2014) 

socenv_RECORD_2014_W2$socenv_average_hh_size_2014<-as.integer(RECORD_W2_SocioEnviro$AVERAGE_HOUSEHOLD_SIZE_2014) 
```    

### **Variable label**: Average household size in 2015      
**Variable name**: socenv_average_hh_size_2015     
**Variable description**: Average household size in residential area in 2015.    
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**: 
For RECORD, these data are available for neighbourhoods in 2014, not in 2015.  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average household size in 2016      
**Variable name**: socenv_average_hh_size_2016      
**Variable description**: Average household size in residential area in 2016.    
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**: 
For RECORD, these data are available for neighbourhoods in 2014, not in 2016.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    


# Housing

### **Variable label**: Average value of dwellings in 1000 euros in 2006    
**Variable name**: socenv_avv_dwellings_2006  
**Variable description**: Average value of dwellings in 1000 euros in residential area in 2006.    
**Variable type**: integer   
**Variable unit**: 1000 euros   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**: 
Related data is available in RECORD (mean rank of price of sold dwellings in different street network buffers in 2002-2007), but these data cannot be harmonized into average value of dwellings in 1000 euros.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average value of dwellings in 1000 euros in 2011    
**Variable name**: socenv_avv_dwellings_2011  
**Variable description**: Average value of dwellings in 1000 euros in residential area in 2011.    
**Variable type**: integer   
**Variable unit**: 1000 euros   
**Category coding**:   

**Harmonization status**: Impossible 
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average value of a plot (m2) in euros in 2007 (dwellings)    
**Variable name**: socenv_avv_dwelling_m2_2007  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area in 2007.    
**Variable type**: integer   
**Variable unit**: euros   
**Category coding**:   

**Harmonization status**: Impossible 
**Harmonization comment**:  
For RECORD, these data are not available.  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average value of a plot (m2) in euros in 2011 (dwellings)  
**Variable name**: socenv_avv_dwelling_m2_2011  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area in 2011.    
**Variable type**: integer   
**Variable unit**: euros   
**Category coding**:   

**Harmonization status**: Impossible 
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average value of a plot (m2) in euros in 2013 (dwellings)  
**Variable name**: socenv_avv_dwelling_m2_2013  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area in 2013.    
**Variable type**: integer   
**Variable unit**: euros   
**Category coding**:   

**Harmonization status**: Impossible 
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average value of a plot (m2) in euros in 2014 (dwellings)  
**Variable name**: socenv_avv_dwelling_m2_2014  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area in 2014.    
**Variable type**: integer   
**Variable unit**: euros   
**Category coding**:   

**Harmonization status**: Impossible 
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average value of a plot (m2) in euros in 2015 (dwellings)  
**Variable name**: socenv_avv_dwelling_m2_2015   
**Variable description**: Average value of a plot in euros (dwellings) in the residential area in 2015.    
**Variable type**: integer   
**Variable unit**: euros    
**Category coding**:   

**Harmonization status**: Impossible 
**Harmonization comment**:  
For RECORD, these data are not available. 
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of unoccupied dwellings in 2011   
**Variable name**: socenv_prop_unocc_dwellings_2011
**Variable description**: Proportion of unoccupied dwellings in residential area in 2011.    
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: Impossible  
**Harmonization comment**:  
For RECORD, these data are available for neighbourhoods in 2014, not in 2011. 
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of unoccupied dwellings in 2012   
**Variable name**: socenv_prop_unocc_dwellings_2012
**Variable description**: Proportion of unoccupied dwellings in residential area in 2012.    
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: Impossible  
**Harmonization comment**:  
For RECORD, these data are available for neighbourhoods in 2014, not in 2011.  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of unoccupied dwellings in 2014   
**Variable name**: socenv_prop_unocc_dwellings_2014
**Variable description**: Proportion of unoccupied dwellings in residential area in 2014.    
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete 
**Harmonization comment**:  
For RECORD, these data are available for neighbourhoods in 2014. This variable was caluclated by: total number of unoccupied dwellings in the area / total number of dwellings in the area * 100. This variable has been linked to cohort respondents using their 5-digit postal code. References of all data sources are listed in the WP7 deliverable report.
**R script**:  
```{r, echo=TRUE}  
socenv_RECORD_2014_W1$socenv_prop_unocc_dwellings_2014<-as.decimal(RECORD_W1_SocioEnviro$PROPORTION_UNOCCUPIED_DWELLINGS_2014) 

socenv_RECORD_2014_W2$socenv_prop_unocc_dwellings_2014<-as.decimal(RECORD_W2_SocioEnviro$PROPORTION_UNOCCUPIED_DWELLINGS_2014)  

```    

# Income

### **Variable label**: Average income in 1000 euros in 2005  
**Variable name**: socenv_av_inc1000_2005  
**Variable description**: Average income in 1000 euros of residents in residential area in 2005.    
**Variable type**: integer     
**Variable unit**: 1000 euros   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in 1000 euros in 2006  
**Variable name**: socenv_av_inc1000_2006 
**Variable description**: Average income in 1000 euros of residents in residential area in 2006.    
**Variable type**: integer     
**Variable unit**: 1000 euros    
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in 1000 euros in 2011   
**Variable name**: socenv_av_inc1000_2011 
**Variable description**: Average income in 1000 euros of residents in residential area in 2011.    
**Variable type**: integer     
**Variable unit**: 1000 euros    
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2006  
**Variable name**: socenv_av_inc_2006  
**Variable description**: Average income in euros of residents in residential area in 2006.    
**Variable type**: integer     
**Variable unit**: euros    
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2007  
**Variable name**: socenv_av_inc_2007
**Variable description**: Average income in euros of residents in residential area in 2007.    
**Variable type**: integer     
**Variable unit**: euros    
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2011  
**Variable name**: socenv_av_inc_2011  
**Variable description**: Average income in euros of residents in residential area in 2011.    
**Variable type**: integer     
**Variable unit**: euros    
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2013  
**Variable name**: socenv_av_inc_2013  
**Variable description**: Average income in euros of residents in residential area in 2013.    
**Variable type**: integer     
**Variable unit**: euros    
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2014  
**Variable name**: socenv_av_inc_2014  
**Variable description**: Average income in euros of residents in residential area in 2014.    
**Variable type**: integer     
**Variable unit**: euros    
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2015  
**Variable name**: socenv_av_inc_2015  
**Variable description**: Average income in euros of residents in residential area in 2015.    
**Variable type**: integer     
**Variable unit**: euros     
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2016  
**Variable name**: socenv_av_inc_2016  
**Variable description**: Average income in euros of residents in residential area in 2016.    
**Variable type**: integer     
**Variable unit**: euros    
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in 1000 euros in 2005 (dichotomized)  
**Variable name**: socenv_av_inc1000dich_2005  
**Variable description**: Average income in 1000 euros of residents in residential area in 2005 (dichotomized: below/above country-specific net mean household income (OECD)).      
**Variable type**: integer     
**Variable unit**:   
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  


```    

### **Variable label**: Average income in 1000 euros in 2006 (dichotomized)  
**Variable name**: socenv_av_inc1000dich_2006 
**Variable description**: Average income in 1000 euros of residents in residential area in 2006 (dichotomized: below/above country-specific net mean household income (OECD)).       
**Variable type**: integer     
**Variable unit**:    
**Category coding**:

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in 1000 euros in 2011 (dichotomized)   
**Variable name**: socenv_av_inc1000dich_2011 
**Variable description**: Average income in 1000 euros of residents in residential area in 2011 (dichotomized: below/above country-specific net mean household income (OECD)).      
**Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  


```    

### **Variable label**: Average income in euros in 2006 (dichotomized)  
**Variable name**: socenv_av_incdich_2006  
**Variable description**: Average income in euros of residents in residential area in 2006 (dichotomized: below/above country-specific net mean household income (OECD)).      
**Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2007 (dichotomized) 
**Variable name**: socenv_av_incdich_2007
**Variable description**: Average income in euros of residents in residential area in 2007 (dichotomized: below/above country-specific net mean household income (OECD)).       
**Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2011 (dichotomized)  
**Variable name**: socenv_av_incdich_2011  
**Variable description**: Average income in euros of residents in residential area in 2011 (dichotomized: below/above country-specific net mean household income (OECD)).       
**Variable type**: integer     
**Variable unit**: euros    
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2013 (dichotomized)  
**Variable name**: socenv_av_incdich_2013
**Variable description**: Average income in euros of residents in residential area in 2013 (dichotomized: below/above country-specific net mean household income (OECD)).      
**Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2014 (dichotomized) 
**Variable name**: socenv_av_incdich_2014  
**Variable description**: Average income in euros of residents in residential area in 2014 (dichotomized: below/above country-specific net mean household income (OECD)).      
**Variable type**: integer     
**Variable unit**:  
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2015 (dichotomized) 
**Variable name**: socenv_av_incdich_2015  
**Variable description**: Average income in euros of residents in residential area in 2015 (dichotomized: below/above country-specific net mean household income (OECD)).     
**Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2016 (dichotomized)  
**Variable name**: socenv_av_inc_2016  
**Variable description**: Average income in euros of residents in residential area in 2016 (dichotomized: below/above country-specific net mean household income (OECD)).     
**Variable type**: integer     
**Variable unit**:     
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```   


 ### **Variable label**: Average household income in euros in 2006
**Variable name**: socenv_av_hhinc_500m_2006  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address in 2006 
**Variable type**: integer     
**Variable unit**: in euros   
**Category coding**:   

**Harmonization status**: complete
**Harmonization comment**: In RECORD, these data were already available.
**R script**:  
```{r, echo=TRUE}
socenv_RECORD_2009_W1$socenv_av_hhinc_500m_2006<-as.integer(RECORD_W1_1$Inc_St500)

```     

### **Variable label**: Average household income in euros in 2006
**Variable name**: socenv_av_hhinc_1000m_2006  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address in 2006 
**Variable type**: integer     
**Variable unit**: in euros   
**Category coding**:   

**Harmonization status**: complete
**Harmonization comment**: In RECORD, these data were already available.
**R script**:  
```{r, echo=TRUE}
socenv_RECORD_2009_W1$socenv_av_hhinc_1000m_2006<-as.integer(RECORD_W1_1$Inc_St1000)

```     

### **Variable label**: Average household income in euros in 2006
**Variable name**: socenv_av_hhinc_2000m_2006  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address in 2006 
**Variable type**: integer     
**Variable unit**: in euros   
**Category coding**:   

**Harmonization status**: complete
**Harmonization comment**: In RECORD, these data were already available.
**R script**:  
```{r, echo=TRUE}
socenv_RECORD_2009_W1$socenv_av_hhinc_2000m_2006<-as.integer(RECORD_W1_1$Inc_St2000)

```     


### **Variable label**: Average household income in euros in 2006 (dichotomized)
**Variable name**: socenv_av_hhincdich_500m_2006  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address in 2006 (dichotomized: below/above country-specific net mean household income (OECD)).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**: complete
**Harmonization comment**: We dichotomized average household income in 500 meter street network buffer around participants (see variable socenv_av_hhinc_500m_2006) by comparing it with the country-specific net mean household income (OECD) in 2005 (€21536).
**R script**:   
```{r, echo=TRUE}  
socenv_RECORD_2009_W1$socenv_av_hhincdich_500m_2006 <
ifelse (RECORD_W1_1$Inc_St500 >= 21536, 1, 0)

```  



### **Variable label**: Average household income in euros in 2006 (dichotomized)
**Variable name**: socenv_av_hhincdich_1000m_2006  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address in 2006 (dichotomized: below/above country-specific net mean household income (OECD)).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**: complete
**Harmonization comment**: We dichotomized average household income in 1000 meter street network buffer around participants (see variable socenv_av_hhinc_1000m_2006) by comparing it with the country-specific net mean household income (OECD) in 2005 (€21536).
**R script**:   
```{r, echo=TRUE}  
socenv_RECORD_2009_W1$socenv_av_hhincdich_1000m_2006 <
ifelse (RECORD_W1_1$Inc_St1000 >= 21536, 1, 0)

```     

### **Variable label**: Average household income in euros in 2006 (dichotomized)
**Variable name**: socenv_av_hhincdich_2000m_2006  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address in 2006 (dichotomized: below/above country-specific net mean household income (OECD)).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**: complete
**Harmonization comment**: We dichotomized average household income in 2000 meter street network buffer around participants (see variable socenv_av_hhinc_2000m_2006) by comparing it with the country-specific net mean household income (OECD) in 2005 (€21536).
**R script**:   
```{r, echo=TRUE}  
socenv_RECORD_2009_W1$socenv_av_hhincdich_2000m_2006 <
ifelse (RECORD_W1_1$Inc_St2000 >= 21536, 1, 0)

```    


### **Variable label**: Average income in 1000 euros in 2005 (Z standardised)  
**Variable name**: socenv_av_inc1000Z_2005  
**Variable description**: Average income in 1000 euros of residents in residential area in 2005 (standardized: mean=0 and sd=1)
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible  
**Harmonization comment**: 
These data are not available for RECORD.
**R script**:  
```{r, echo=TRUE} 



```       

### **Variable label**: Average income in 1000 euros in 2006 (Z standardized)  
**Variable name**: socenv_av_inc1000Z_2006 
**Variable description**: Average income in 1000 euros of residents in residential area in 2006 (standardized: mean=0 and sd=1)      
**Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Harmonization status**: impossible  
**Harmonization comment**: 
These data are not available for RECORD.
**R script**:  
```{r, echo=TRUE} 



```    

### **Variable label**: Average income in 1000 euros in 2011 (Z standardized)   
**Variable name**: socenv_av_inc1000Z_2011 
**Variable description**: Average income in 1000 euros of residents in residential area in 2011 (standardized: mean=0 and sd=1)   
**Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Harmonization status**: impossible  
**Harmonization comment**: 
These data are not available for RECORD.
**R script**:  
```{r, echo=TRUE} 



```      



### **Variable label**: Average income in euros in 2006 (Z standardized)  
**Variable name**: socenv_av_incZ_2006  
**Variable description**: Average income in euros of residents in residential area in 2006 (standardized: mean=0 and sd=1) 
**Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Harmonization status**: impossible  
**Harmonization comment**: 
These data are not available for RECORD.
**R script**:  
```{r, echo=TRUE} 



```     

### **Variable label**: Average income in euros in 2007 (Z standardized) 
**Variable name**: socenv_av_incZ_2007
**Variable description**: Average income in euros of residents in residential area in 2007 (standardized: mean=0 and sd=1)        
**Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Harmonization status**: impossible  
**Harmonization comment**: 
These data are not available for RECORD.
**R script**:  
```{r, echo=TRUE} 


```       

### **Variable label**: Average income in euros in 2011 (Z standardized)  
**Variable name**: socenv_av_incZ_2011  
**Variable description**: Average income in euros of residents in residential area in 2011 (standardized: mean=0 and sd=1)        
**Variable type**: integer     
**Variable unit**: euros    
**Category coding**:   

**Harmonization status**: impossible  
**Harmonization comment**: 
These data are not available for RECORD.
**R script**:  
```{r, echo=TRUE} 


```     

### **Variable label**: Average income in euros in 2013 (Z standardized)  
**Variable name**: socenv_av_incZ_2013
**Variable description**: Average income in euros of residents in residential area in 2013 (standardized: mean=0 and sd=1)      
**Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Harmonization status**: impossible  
**Harmonization comment**: 
These data are not available for RECORD.
**R script**:  
```{r, echo=TRUE} 


```    

### **Variable label**: Average income in euros in 2014 (Z standardized) 
**Variable name**: socenv_av_incZ_2014  
**Variable description**: Average income in euros of residents in residential area in 2014 (standardized: mean=0 and sd=1)       
**Variable type**: integer     
**Variable unit**:  
**Category coding**:   

**Harmonization status**: impossible  
**Harmonization comment**: 
These data are not available for RECORD.
**R script**:  
```{r, echo=TRUE} 


```     

### **Variable label**: Average income in euros in 2015 (Z standardized) 
**Variable name**: socenv_av_incZ_2015  
**Variable description**: Average income in euros of residents in residential area in 2015 (standardized: mean=0 and sd=1)    
**Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Harmonization status**: impossible  
**Harmonization comment**: 
These data are not available for RECORD.
**R script**:  
```{r, echo=TRUE} 


```     

### **Variable label**: Average income in euros in 2016 (Z standardized)  
**Variable name**: socenv_av_incZ_2016  
**Variable description**: Average income in euros of residents in residential area in 2016 (standardized: mean=0 and sd=1)    
**Variable type**: integer     
**Variable unit**:     
**Category coding**:   

**Harmonization status**: impossible  
**Harmonization comment**: 
These data are not available for RECORD.
**R script**:  
```{r, echo=TRUE} 


```   

### **Variable label**: Average household income in euros in 2006 (Z standardized)
**Variable name**: socenv_av_hhincZ_500m_2006  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address in 2006 (standardized: mean=0 and sd=1)    .       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**: Data on average household income in euros in 500 meter street network buffer zone around participants address are available in RECORD, but y and o are not available for France and therefore we cannot apply the formula Z=(x-y)/o (Z=standardized income variable with mean=0, sd=1; x=area-level average income from respondent; y=area-level average income in entire country; o=standard deviation of area-level income in entire country).
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    


### **Variable label**: Average household income in euros in 2006 (Z standardized)
**Variable name**: socenv_av_hhincZ_1000m_2006  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address in 2006 (standardized: mean=0 and sd=1).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**: Data on average household income in euros in 1000 meter street network buffer zone around participants address are available in RECORD, but y and o are not available for France and therefore we cannot apply the formula Z=(x-y)/o (Z=standardized income variable with mean=0, sd=1; x=area-level average income from respondent; y=area-level average income in entire country; o=standard deviation of area-level income in entire country).
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average household income in euros in 2006 (Z standardized)
**Variable name**: socenv_av_hhincZ_2000m_2006  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address in 2006 (standardized: mean=0 and sd=1).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**: Data on average household income in euros in 2000 meter street network buffer zone around participants address are available in RECORD, but y and o are not available for France and therefore we cannot apply the formula Z=(x-y)/o (Z=standardized income variable with mean=0, sd=1; x=area-level average income from respondent; y=area-level average income in entire country; o=standard deviation of area-level income in entire country).
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Proportion of income recipients in 2005
**Variable name**: socenv_av_inc_recipients_2005  
**Variable description**: Proportion of income recipients in residential area in 2005.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:   
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of income recipients in 2011  
**Variable name**: socenv_av_inc_recipients_2011  
**Variable description**: Proportion of income recipients in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

# Unemployment

### **Variable label**: Proportion of unemployed residents in 2006  
**Variable name**: socenv_prop_unemployment_2006  
**Variable description**: Proportion of unemployed residents in residential area in 2006.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are available for neighbourhoods in 2014, not in 2006.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of unemployed residents in 2007    
**Variable name**: socenv_prop_unemployment_2007    
**Variable description**: Proportion of unemployed residents in residential area in 2007.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are available for neighbourhoods in 2014, not in 2007.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of unemployed residents in 2011    
**Variable name**: socenv_prop_unemployment_2011    
**Variable description**: Proportion of unemployed residents in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are available for neighbourhoods in 2014, not in 2011.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of unemployed residents in 2014  
**Variable name**: socenv_prop_unemployment_2014  
**Variable description**: Proportion of unemployed residents in residential area in 2014.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  complete
**Harmonization comment**:
For RECORD, these data are available for neighbourhoods in 2014. This variable includes the proportion of unemployed residents aged 15-64 years in the neighbourhood. This variable was calculated by: total number of unemployed residents aged 15-64 years old in the area / total number of residents aged 15-64 years old in the area * 100. This variable has been linked to cohort respondents using their 5-digit postal code. References of the original data sources are listed in WP7 deliverable report.
**R script**:  
```{r, echo=TRUE}  
socenv_RECORD_2014_W1$socenv_prop_unemployment_2014<-as.decimal(RECORD_W1_SocioEnviro$UNEMPLOYMENT_RATE_2014) 

socenv_RECORD_2014_W2$socenv_prop_unemployment_2014<-as.decimal(RECORD_W2_SocioEnviro$UNEMPLOYMENT_RATE_2014)  
```    

### **Variable label**: Proportion of unemployed residents in 2015  
**Variable name**: socenv_prop_unemployment_2015  
**Variable description**: Proportion of unemployed residents in residential area in 2015.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are available for neighbourhoods in 2014, not in 2015.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

# Social security

### **Variable label**: Proportion of social security beneficiaries in 2006  
**Variable name**: socenv_proportion_socsecben_2006   
**Variable description**: Proportion of social security beneficiaries in residential area in 2006.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of social security beneficiaries in 2007    
**Variable name**: socenv_proportion_socsecben_2007   
**Variable description**: Proportion of social security beneficiaries in residential area in 2007.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of social security beneficiaries in 2010  
**Variable name**: socenv_proportion_socsecben_2010   
**Variable description**: Proportion of social security beneficiaries in residential area in 2010.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of social security beneficiaries in 2011  
**Variable name**: socenv_proportion_socsecben_2011   
**Variable description**: Proportion of social security beneficiaries in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of social security beneficiaries in 2015  
**Variable name**: socenv_proportion_socsecben_2015   
**Variable description**: Proportion of social security beneficiaries in residential area in 2015.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of social security beneficiaries in 2016  
**Variable name**: socenv_proportion_socsecben_2016   
**Variable description**: Proportion of social security beneficiaries in residential area in 2016.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of residents with disability benefit in 2010  
**Variable name**: socenv_proportion_disben_2010   
**Variable description**: Proportion of residents with a disability benefit in residential area in 2010.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of residents with unemployment benefit in 2010  
**Variable name**: socenv_proportion_unemplben_2010   
**Variable description**: Proportion of residents with a unemployment benefit in residential area in 2010.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

# Educational level  

### **Variable label**: Proportion of low educated residents in 2011  
**Variable name**: socenv_prop_low_education_2011  
**Variable description**: Proportion of low educated residents in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of low educated residents in 2014 
**Variable name**: socenv_prop_low_education_2014  
**Variable description**: Proportion of low educated residents in residential area in 2014.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of intermediate educated residents in 2011  
**Variable name**: socenv_prop_itm_education_2011  
**Variable description**: Proportion of intermediate educated residents in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of intermediate educated residents in 2014  
**Variable name**: socenv_prop_itm_education_2014  
**Variable description**: Proportion of intermediate educated residents in residential area in 2014.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of high educated residents in 2011  
**Variable name**: socenv_prop_high_education_2011  
**Variable description**: Proportion of high educated residents in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of high educated residents in 2014  
**Variable name**: socenv_prop_high_education_2014  
**Variable description**: Proportion of high educated residents in residential area in 2014.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

# Immigrants and ethnic minority groups

### **Variable label**: Proportion of immigrants in 2011  
**Variable name**: socenv_prop_immigrants_2011
**Variable description**: Proportion of immigrants in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible. 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts.
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of western immigrants in 2006  
**Variable name**: socenv_prop_west_imgs_2006  
**Variable description**: Proportion of western immigrants in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible. 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts.
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of western immigrants in 2011  
**Variable name**: socenv_prop_west_imgs_2011  
**Variable description**: Proportion of western immigrants in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible. 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts.
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of non-western immigrants in 2006  
**Variable name**: socenv_prop_nonwest_imgs_2006  
**Variable description**: Proportion of non-western immigrants in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible. 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts.
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of non-western immigrants in 2011  
**Variable name**: socenv_prop_nonwest_imgs_2011  
**Variable description**: Proportion of non-western immigrants in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible. 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts.
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of immigrants of Moroccan origin in 2006  
**Variable name**: socenv_prop_moroccan_2006  
**Variable description**: Proportion of immigrants of Moroccan origin in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible. 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts.
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of immigrants of Moroccan origin in 2011  
**Variable name**: socenv_prop_moroccan_2011  
**Variable description**: Proportion of immigrants of Moroccan origin in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible. 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts.
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of immigrants of Antillian and Aruban origin in 2006  
**Variable name**: socenv_prop_antaru_2006  
**Variable description**: Proportion of immigrants of Antillian and Aruban origin in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible. 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts. 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of immigrants of Antillian and Aruban origin in 2011  
**Variable name**: socenv_prop_antaru_2011  
**Variable description**: Proportion of immigrants of Antillian and Aruban origin in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible. 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts. 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of immigrants of Surinamese origin in 2006  
**Variable name**: socenv_prop_surinamese_2006  
**Variable description**: Proportion of immigrants of Surinamese origin in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible. 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts.
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of immigrants of Surinamese origin in 2011  
**Variable name**: socenv_prop_surinamese_2011  
**Variable description**: Proportion of immigrants of Surinamese origin in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible. 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts.
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of immigrants of Turkish origin in 2006  
**Variable name**: socenv_prop_turkey_2006  
**Variable description**: Proportion of immigrants of Turkish origin in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible. 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts.
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of immigrants of Turkish origin in 2011  
**Variable name**: socenv_prop_turkey_2011  
**Variable description**: Proportion of immigrants of Turkish origin in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible. 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts.
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of immigrants of other origin in 2006  
**Variable name**: socenv_prop_other_2006  
**Variable description**: Proportion of immigrants of other origin in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible. 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts.
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of immigrants of other origin in 2011  
**Variable name**: socenv_prop_other_2011  
**Variable description**: Proportion of immigrants of other origin in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible. 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts.
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of foreigners in 2007  
**Variable name**: socenv_prop_foreigners_2007  
**Variable description**: Proportion of foreigners in residential area in 2007.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible. 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts.
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of foreigners in 2011  
**Variable name**: socenv_prop_foreigners_2011  
**Variable description**: Proportion of foreigners in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible. 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts.
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

# Crime  

### **Variable label**: Number of criminal offenses per 1000 residents in 2007  
**Variable name**: socenv_crimoff_2007    
**Variable description**: Number of criminal offenses per 1000 residents in residential area in 2007.       
**Variable type**: integer    
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of criminal offenses per 1000 residents in 2011  
**Variable name**: socenv_crimoff_2011    
**Variable description**: Number of criminal offenses per 1000 residents in residential area in 2011.       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of criminal offenses per 1000 residents in 2014    
**Variable name**: socenv_crimoff_2014    
**Variable description**: Number of criminal offenses per 1000 residents in residential area in 2014.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of criminal offenses per 1000 residents in 2015    
**Variable name**: socenv_crimoff_2015    
**Variable description**: Number of criminal offenses per 1000 residents in residential area in 2015.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of criminal offenses per 1000 residents in 2016    
**Variable name**: socenv_crimoff_2016    
**Variable description**: Number of criminal offenses per 1000 residents in residential area in 2016.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of violent crimes per 1000 residents in 2007  
**Variable name**: socenv_violentcrim_2007    
**Variable description**: Number of violent crimes per 1000 residents in residential area in 2007.       
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of violent crimes per 1000 residents in 2011    
**Variable name**: socenv_violentcrim_2011    
**Variable description**: Number of violent crimes per 1000 residents in residential area in 2011.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of violent crimes per 1000 residents in 2016    
**Variable name**: socenv_violentcrim_2016   
**Variable description**: Number of violent crimes per 1000 residents in residential area in 2016.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of thefts per 1000 residents in 2007  
**Variable name**: socenv_thefts_2007    
**Variable description**: Number of thefts per 1000 residents in residential area in 2007.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of thefts per 1000 residents in 2011    
**Variable name**: socenv_thefts_2011    
**Variable description**: Number of thefts per 1000 residents in residential area in 2011.       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of thefts per 1000 residents in 2016  
**Variable name**: socenv_thefts_2016    
**Variable description**: Number of thefts per 1000 residents in residential area in 2016.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of vandalism and public disorder per 1000 residents in 2011  
**Variable name**: socenv_vandalism_po_2011   
**Variable description**: Number of vandalism and public disorder per 1000 residents in residential area in 2011.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of vandalism and public disorder per 1000 residents in 2016    
**Variable name**: socenv_vandalism_po_2016   
**Variable description**: Number of vandalism and public disorder per 1000 residents in residential area in 2016.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of violent crimes and sexual offenses per 1000 residents in 2011    
**Variable name**: socenv_violentcrim_sexoff_2011    
**Variable description**: Number of violent crimes and sexual offenses per 1000 residents in residential area in 2011.         
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of violent crimes and sexual offenses per 1000 residents in 2016  
**Variable name**: socenv_violentcrim_sexoff_2016   
**Variable description**: Number of violent crimes and sexual offenses per 1000 residents in residential area in 2016.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of vandalism per 1000 residents in 2011   
**Variable name**: socenv_vandalism_2011    
**Variable description**: Number of vandalism per 1000 residents in residential area in 2011.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of vandalism per 1000 residents in 2016    
**Variable name**: socenv_vandalism_2016    
**Variable description**: Number of vandalism per 1000 residents in residential area in 2016.          
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of public disorder per 1000 residents in 2011    
**Variable name**: socenv_po_2011    
**Variable description**: Number of public disorder per 1000 residents in residential area in 2011.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of public disorder per 1000 residents in 2016    
**Variable name**: socenv_po_2016    
**Variable description**: Number of public disorder per 1000 residents in residential area in 2016.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Area indicator: city  
**Variable name**: socenv_city_2004   
**Variable description**: City indicator in 2004        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


```  


### **Variable label**: Area indicator: city  
**Variable name**: socenv_city_2006   
**Variable description**: City indicator in 2006       
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


```  




### **Variable label**: Area indicator: city  
**Variable name**: socenv_city_2009   
**Variable description**: City indicator in 2009        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete
**Harmonization comment**:  
For RECORD, the indicator variables start with 33.
**R script**:  
```{r, echo=TRUE}  
socenv_RECORD_2009_W1$socenv_city_2009<-as.integer(RECORD_W1_area_identifiers$city) 



```


### **Variable label**: Area indicator: city  
**Variable name**: socenv_city_2011   
**Variable description**: City indicator in 2011        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


```  


### **Variable label**: Area indicator: city  
**Variable name**: socenv_city_2014   
**Variable description**: City indicator in 2014        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


```  



### **Variable label**: Area indicator: municipality  
**Variable name**: socenv_municipality_2006   
**Variable description**: Municipality indicator in 2006        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


```  



### **Variable label**: Area indicator: municipality  
**Variable name**: socenv_municipality_2011   
**Variable description**: Municipality indicator in 2011        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


```  


### **Variable label**: Area indicator: municipality  
**Variable name**: socenv_municipality_2016   
**Variable description**: Municipality indicator in 2016        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


```  


### **Variable label**: Area indicator: neighbourhood 
**Variable name**: socenv_neighbourhood_2004
**Variable description**: Neighbourhood indicator in 2004        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:     

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  

```  


### **Variable label**: Area indicator: neighbourhood 
**Variable name**: socenv_neighbourhood_2006
**Variable description**: Neighbourhood indicator in 2006        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:     

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


``` 




### **Variable label**: Area indicator: neighbourhood  
**Variable name**: socenv_neighbourhood_2009   
**Variable description**: Neighbourhood indicator in 2009        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete
**Harmonization comment**:  
For RECORD, the indicator variables start with 33.
**R script**:  
```{r, echo=TRUE}  
socenv_RECORD_2009_W1$socenv_neighbourhood_2009<-as.integer(RECORD_W1_area_identifiers$neighbourhood) 

socenv_RECORD_2009_W2$socenv_neighbourhood_2009<-as.integer(RECORD_W2_area_identifiers$neighbourhood)

```


### **Variable label**: Area indicator: neighbourhood 
**Variable name**: socenv_neighbourhood_2011
**Variable description**: Neighbourhood indicator in 2011        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:     

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


``` 


### **Variable label**: Area indicator: neighbourhood 
**Variable name**: socenv_neighbourhood_2014
**Variable description**: Neighbourhood indicator in 2014       
**Variable type**: integer      
**Variable unit**:   
**Category coding**:     

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


``` 


### **Variable label**: Area indicator: 4-digit postal code 
**Variable name**: socenv_PC4_2004
**Variable description**: 4-digit postal code (PC4) indicator in 2004        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:     

**Harmonization status**: complete
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


```  



### **Variable label**: Area indicator: 4-digit postal code 
**Variable name**: socenv_PC4_2006
**Variable description**: 4-digit postal code (PC4) indicator in 2006        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:     

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


```  

### **Variable label**: Area indicator: 4-digit postal code 
**Variable name**: socenv_PC4_2011
**Variable description**: 4-digit postal code (PC4) indicator in 2011      
**Variable type**: integer      
**Variable unit**:   
**Category coding**:     

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


``` 



### **Variable label**: Area indicator: 4-digit postal code 
**Variable name**: socenv_PC4_2011
**Variable description**: 4-digit postal code (PC4) indicator in 2014     
**Variable type**: integer      
**Variable unit**:   
**Category coding**:     

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


``` 



### **Variable label**: Area indicator: 6-digit postal code
**Variable name**: socenv_PC6_2004
**Variable description**: 6-digit postal code (PC6) indicator in 2004       
**Variable type**: integer      
**Variable unit**:   
**Category coding**:     

**Harmonization status**: impossible
**Harmonization comment**:
**R script**:  
```{r, echo=TRUE}  


```  



### **Variable label**: Area indicator: 6-digit postal code
**Variable name**: socenv_PC6_2006
**Variable description**: 6-digit postal code (PC6) indicator in 2006       
**Variable type**: integer      
**Variable unit**:   
**Category coding**:     

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


``` 


### **Variable label**: Area indicator: 6-digit postal code
**Variable name**: socenv_PC6_2011
**Variable description**: 6-digit postal code (PC6) indicator in 2011      
**Variable type**: integer      
**Variable unit**:   
**Category coding**:     

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


```  


### **Variable label**: Area indicator: 6-digit postal code
**Variable name**: socenv_PC6_2014
**Variable description**: 6-digit postal code (PC6) indicator in 2014      
**Variable type**: integer      
**Variable unit**:   
**Category coding**:     

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


```  

### **Variable label**: Area indicator: 5-digit postal code 
**Variable name**: socenv_PC5_2009 
**Variable description**: 5-digit postal code (PC5) indicator in 2009        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete
**Harmonization comment**:  
For RECORD, the indicator variables start with 33.
**R script**:  
```{r, echo=TRUE}  
socenv_RECORD_2009_W1$socenv_pc5_2009<-as.integer(RECORD_W1_area_identifiers$pc5) 

socenv_RECORD_2009_W2$socenv_pc5_2009<-as.integer(RECORD_W2_area_identifiers$pc5)

```

