---
title: "Social environmental (i.e. geospatial) DataSchema"
output: html_document
---
# Table of Contents
1. [Urbanization grade] #(Urbanzation grade)  
2. [Demographics] #(Demographics)  
3. [Housing] #(Housing)  
4. [Income] #(Income)  
5. [Unemployment rate] #(Unemployment rate)  
6. [Social security] #(Social security)  
7. [Educational level] #(Educational level)  
8. [Immigrants and ethnic minority groups] #(Immigrants and ethnic minority groups)  
9. [Crime] #(Crime)  
10. [Social cohesion] (#Social cohesion)  

# Urbanization grade

### **Variable label**: Urbanization grade in 2006  
**Variable name**: socenv_urbanization_grade_2006    
**Variable description**: Population density of the residential area (number of residents per km2) in 2006.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  

### **Variable label**: Urbanization grade in 2007 
**Variable name**: socenv_urbanization_grade_2007    
**Variable description**: Population density of the residential area (number of residents per km2) in 2007.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  

### **Variable label**: Urbanization grade in 2009 
**Variable name**: socenv_urbanization_grade_2009    
**Variable description**: Population density of the residential area (number of residents per km2) in 2009.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  

### **Variable label**: Urbanization grade in 2011 
**Variable name**: socenv_urbanization_grade_2011    
**Variable description**: Population density of the residential area (number of residents per km2) in 2011.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  

### **Variable label**: Urbanization grade in 2014
**Variable name**: socenv_urbanization_grade_2014    
**Variable description**: Population density of the residential area (number of residents per km2) in 2014.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written


```  

# Demographics

### **Variable label**: Proportion of men in 2006  
**Variable name**: socenv_proportion_men_2006    
**Variable description**: Proportion of men in the residential area in 2006.  
**Variable type**: decimal
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written

```  

### **Variable label**: Proportion of men in 2011  
**Variable name**: socenv_proportion_men_2011    
**Variable description**: Proportion of men in the residential area in 2011.  
**Variable type**: decimal
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written

```  

### **Variable label**: Proportion of women in 2006  
**Variable name**: socenv_proportion_women_2006    
**Variable description**: Proportion of women in the residential area in 2006.  
**Variable type**: decimal
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written

```  

### **Variable label**: Proportion of women in 2011  
**Variable name**: socenv_proportion_women_2011    
**Variable description**: Proportion of women in the residential area in 2011.  
**Variable type**: decimal
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written
