---
title: "Social environmental (i.e. geospatial) DataSchema"
output: html_document
---
# Table of Contents

---
title: "Social environmental (i.e. geospatial) DataSchema"
output: html_document
---
# Table of Contents
1. [Urbanization grade] #(Urbanzation grade)  
2. [Demographics] #(Demographics)  
3. [Housing] #(Housing)  
4. [Income] #(Income)  
5. [Unemployment rate] #(Unemployment rate)  
6. [Social security] #(Social security)  
7. [Educational level] #(Educational level)  
8. [Immigrants and ethnic minority groups] #(Immigrants and ethnic minority groups)  
9. [Crime] #(Crime)  
  

# Urbanization grade

### **Variable label**: Urbanization grade in 2006  
**Variable name**: socenv_urbanization_grade_2006    
**Variable description**: Population density of the residential area (number of residents per km2) in 2006.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  

### **Variable label**: Urbanization grade in 2007 
**Variable name**: socenv_urbanization_grade_2007    
**Variable description**: Population density of the residential area (number of residents per km2) in 2007.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  

### **Variable label**: Urbanization grade in 2009 
**Variable name**: socenv_urbanization_grade_2009    
**Variable description**: Population density of the residential area (number of residents per km2) in 2009.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  

### **Variable label**: Urbanization grade in 2011 
**Variable name**: socenv_urbanization_grade_2011    
**Variable description**: Population density of the residential area (number of residents per km2) in 2011.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  

### **Variable label**: Urbanization grade in 2014
**Variable name**: socenv_urbanization_grade_2014    
**Variable description**: Population density of the residential area (number of residents per km2) in 2014.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written  



# Demographics

### **Variable label**: Proportion of men in 2006  
**Variable name**: socenv_proportion_men_2006    
**Variable description**: Proportion of men in the residential area in 2006.  
**Variable type**: decimal
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of men in 2011  
**Variable name**: socenv_proportion_men_2011    
**Variable description**: Proportion of men in the residential area in 2011.  
**Variable type**: decimal
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of women in 2006  
**Variable name**: socenv_proportion_women_2006    
**Variable description**: Proportion of women in the residential area in 2006.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}  
#This is where the R-script will be written  



### **Variable label**: Proportion of women in 2011    
**Variable name**: socenv_proportion_women_2011    
**Variable description**: Proportion of women in the residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written


### **Variable label**: Proportion of residents aged 65 or older in 2006   
**Variable name**: socenv_proportion_65_older_2006   
**Variable description**: Proportion of residents aged 65 or older in residential area in 2006.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of residents aged 65 or older in 2007   
**Variable name**: socenv_proportion_65_older_2007   
**Variable description**: Proportion of residents aged 65 or older in residential area in 2007.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of residents aged 65 or older in 2011   
**Variable name**: socenv_proportion_65_older_2011   
**Variable description**: Proportion of residents aged 65 or older in residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of unmaried residents in 2008   
**Variable name**: socenv_proportion_unmaried_2008   
**Variable description**: Proportion of unmaried residents in residential area in 2008.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of unmaried residents in 2011   
**Variable name**: socenv_proportion_unmaried_2011   
**Variable description**: Proportion of unmaried residents in residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of maried residents in 2006   
**Variable name**: socenv_proportion_maried_2006   
**Variable description**: Proportion of maried residents in residential area in 2006.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of maried residents in 2008   
**Variable name**: socenv_proportion_maried_2008   
**Variable description**: Proportion of maried residents in residential area in 2008.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of maried residents in 2011   
**Variable name**: socenv_proportion_maried_2011   
**Variable description**: Proportion of maried residents in residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of divorced residents in 2006   
**Variable name**: socenv_proportion_divorced_2006   
**Variable description**: Proportion of divorced residents in residential area in 2006.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of divorced residents in 2008   
**Variable name**: socenv_proportion_divorced_2008   
**Variable description**: Proportion of divorced residents in residential area in 2008.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of divorced residents in 2011   
**Variable name**: socenv_proportion_divorced_2011   
**Variable description**: Proportion of divorced residents in residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of widowed residents in 2006   
**Variable name**: socenv_proportion_widowed_2006   
**Variable description**: Proportion of widowed residents in residential area in 2006.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of widowed residents in 2008     
**Variable name**: socenv_proportion_widowed_2008   
**Variable description**: Proportion of widowed residents in residential area in 2008.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of widowed residents in 2011    
**Variable name**: socenv_proportion_widowed_2011   
**Variable description**: Proportion of widowed residents in residential area in 2011.  
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average household size in 2006   
**Variable name**: socenv_average_household_size_2006   
**Variable description**: Average household size in residential area in 2006.  
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average household size in 2009   
**Variable name**: socenv_average_household_size_2009   
**Variable description**: Average household size in residential area in 2009.  
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average household size in 2011   
**Variable name**: socenv_average_household_size_2011   
**Variable description**: Average household size in residential area in 2011.  
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average household size in 2014   
**Variable name**: socenv_average_household_size_2014   
**Variable description**: Average household size in residential area in 2014.  
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average household size in 2015      
**Variable name**: socenv_average_household_size_2015     
**Variable description**: Average household size in residential area in 2015.    
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average household size in 2016      
**Variable name**: socenv_average_household_size_2016      
**Variable description**: Average household size in residential area in 2016.    
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



# Housing


### **Variable label**: Average value of dwellings in 1000 euros in 2006    
**Variable name**: socenv_average_value_dwellings_2006  
**Variable description**: Average value of dwellings in 1000 euros in residential area in 2006.    
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average value of dwellings in 1000 euros in 2011    
**Variable name**: socenv_average_value_dwellings_2011  
**Variable description**: Average value of dwellings in 1000 euros in residential area in 2011.    
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average value of a plot (m2) in euros in 2006 (detached houses)   
**Variable name**: socenv_average_value_detached_houses_m2_2006  
**Variable description**: Average value of a plot in euros (detached houses) in the residential area in 2006.    
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average value of a plot (m2) in euros in 2006 (row houses)   
**Variable name**: socenv_average_value_row_houses_m2_2006  
**Variable description**: Average value of a plot in euros (row houses) in the residential area in 2006.    
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average value of a plot (m2) in euros in 2006 (multi dwellings)   
**Variable name**: socenv_average_value_multi_dwelling_m2_2006  
**Variable description**: Average value of a plot in euros (multi dwellings) in the residential area in 2006.    
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average value of a plot (m2) in euros in 2007 (dwellings)    
**Variable name**: socenv_average_value_dwelling_m2_2007  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area in 2007.    
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average value of a plot (m2) in euros in 2011 (dwellings)  
**Variable name**: socenv_average_value_dwelling_m2_2011  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area in 2011.    
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average value of a plot (m2) in euros in 2013 (dwellings)  
**Variable name**: socenv_average_value_dwelling_m2_2013  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area in 2013.    
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average value of a plot (m2) in euros in 2014 (dwellings)  
**Variable name**: socenv_average_value_dwelling_m2_2014  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area in 2014.    
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average value of a plot (m2) in euros in 2015 (dwellings)  
**Variable name**: socenv_average_value_dwelling_m2_2015  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area in 2015.    
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average value of a plot (m2) in euros in 2011 (detached houses)   
**Variable name**: socenv_average_value_detached_houses_m2_2011  
**Variable description**: Average value of a plot in euros (detached houses) in the residential area in 2011.    
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average value of a plot (m2) in euros in 2011 (row houses)   
**Variable name**: socenv_average_value_row_houses_m2_2011  
**Variable description**: Average value of a plot in euros (row houses) in the residential area in 2011.    
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average value of a plot (m2) in euros in 2011 (multi dwellings)   
**Variable name**: socenv_average_value_multi_dwelling_m2_2011  
**Variable description**: Average value of a plot in euros (multi dwellings) in the residential area in 2011.    
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written


### **Variable label**: Proportion of unoccupied dwellings in 2011   
**Variable name**: socenv_proportion_unoccupied_dwellings_2011
**Variable description**: Proportion of unoccupied dwellings in residential area in 2011.    
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of unoccupied dwellings in 2012   
**Variable name**: socenv_proportion_unoccupied_dwellings_2012
**Variable description**: Proportion of unoccupied dwellings in residential area in 2012.    
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of unoccupied dwellings in 2014   
**Variable name**: socenv_proportion_unoccupied_dwellings_2012
**Variable description**: Proportion of unoccupied dwellings in residential area in 2012.    
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



# Income


### **Variable label**: Average income in 1000 euros in 2005  
**Variable name**: socenv_average_income_residents_2005  
**Variable description**: Average income in 1000 euros of residents in residential area in 2005.    
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in euros in 2006  
**Variable name**: socenv_average_income_2006  
**Variable description**: Average income in euros of residents in residential area in 2006.    
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in 1000 euros in 2006  
**Variable name**: socenv_average_income_2006_2  
**Variable description**: Average income in 1000 euros of residents in residential area in 2006.    
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in euros in 2007  
**Variable name**: socenv_average_income_2007  
**Variable description**: Average income in euros of residents in residential area in 2007.    
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in euros in 2011  
**Variable name**: socenv_average_income_2011  
**Variable description**: Average income in euros of residents in residential area in 2011.    
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written


### **Variable label**: Average income in 1000 euros in 2011   
**Variable name**: socenv_average_income_2011_2
**Variable description**: Average income in 1000 euros of residents in residential area in 2011.    
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in 1000 euros in 2011   
**Variable name**: socenv_average_income_residents_2011
**Variable description**: Average income in 1000 euros of residents in residential area in 2011.    
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in euros in 2013  
**Variable name**: socenv_average_income_2013  
**Variable description**: Average income in euros of residents in residential area in 2013.    
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in euros in 2014  
**Variable name**: socenv_average_income_2014  
**Variable description**: Average income in euros of residents in residential area in 2014.    
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in euros in 2015  
**Variable name**: socenv_average_income_2015  
**Variable description**: Average income in euros of residents in residential area in 2015.    
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average gross income in euros in 2015  
**Variable name**: socenv_average_gross_income_2015  
**Variable description**: Average gross income in euros of residents in residential area in 2015.    
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average net income in euros in 2015  
**Variable name**: socenv_average_net_income_2015  
**Variable description**: Average net income in euros of residents in residential area in 2015.    
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in euros in 2016  
**Variable name**: socenv_average_income_2016  
**Variable description**: Average income in euros of residents in residential area in 2016.    
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of income recipients in 2005
**Variable name**: socenv_average_income_recipients_2005  
**Variable description**: Proportion of income recipients in residential area in 2005.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of income recipients in 2011  
**Variable name**: socenv_average_income_recipients_2011  
**Variable description**: Proportion of income recipients in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



# Unemployment rate


### **Variable label**: Proportion of unemployed residents in 2006  
**Variable name**: socenv_unemployment_rate_2006  
**Variable description**: Proportion of unemployed residents in residential area in 2006.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of unemployed residents in 2007    
**Variable name**: socenv_proportion_unemployment_2007    
**Variable description**: Proportion of unemployed residents in residential area in 2007.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of unemployed residents in 2011    
**Variable name**: socenv_proportion_unemployment_2011    
**Variable description**: Proportion of unemployed residents in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of unemployed residents in 2011  
**Variable name**: socenv_unemployment_rate_2011  
**Variable description**: Proportion of unemployed residents in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of unemployed residents in 2014  
**Variable name**: socenv_unemployment_rate_2014  
**Variable description**: Proportion of unemployed residents in residential area in 2014.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of unemployed residents in 2015  
**Variable name**: socenv_unemployment_rate_2015  
**Variable description**: Proportion of unemployed residents in residential area in 2015.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



# Social security



### **Variable label**: Proportion of social security beneficiaries in 2006  
**Variable name**: socenv_proportion_socsecben_2006   
**Variable description**: Proportion of social security beneficiaries in residential area in 2006.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of social security beneficiaries in 2007    
**Variable name**: socenv_proportion_socsecben_2007   
**Variable description**: Proportion of social security beneficiaries in residential area in 2007.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of social security beneficiaries in 2010  
**Variable name**: socenv_proportion_socsecben_2010   
**Variable description**: Proportion of social security beneficiaries in residential area in 2010.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of residents with disability benefit in 2010  
**Variable name**: socenv_proportion_disability_benefit_2010   
**Variable description**: Proportion of residents with a disability benefit in residential area in 2010.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of residents with unemployment benefit in 2010  
**Variable name**: socenv_proportion_unemployment_benefit_2010   
**Variable description**: Proportion of residents with a unemployment benefit in residential area in 2010.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of social security beneficiaries in 2011  
**Variable name**: socenv_proportion_socsecben_2011   
**Variable description**: Proportion of social security beneficiaries in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of social security beneficiaries in 2015  
**Variable name**: socenv_proportion_socsecben_2015   
**Variable description**: Proportion of social security beneficiaries in residential area in 2015.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of social security beneficiaries in 2016  
**Variable name**: socenv_proportion_socsecben_2016   
**Variable description**: Proportion of social security beneficiaries in residential area in 2016.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written


### **Variable label**: Proportion of social security beneficiaries in 2016    
**Variable name**: socenv_proportion_social_beneficiaries_2016  
**Variable description**: Proportion of social security beneficiaries in residential area in 2016.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



# Educational level  


### **Variable label**: Proportion of low educated residents in 2011  
**Variable name**: socenv_proportion_low_education_2011  
**Variable description**: Proportion of low educated residents in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of intermediate educated residents in 2011  
**Variable name**: socenv_proportion_intermediate_education_2011  
**Variable description**: Proportion of intermediate educated residents in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of high educated residents in 2011  
**Variable name**: socenv_proportion_high_education_2011  
**Variable description**: Proportion of high educated residents in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of non-educated residents in 2011  
**Variable name**: socenv_proportion_no_education_2011  
**Variable description**: Proportion of non-educated residents in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of residents whose educational level was not indicated in 2011
**Variable name**: socenv_proportion_education_not_indicated_2011  
**Variable description**: Proportion of residents in residential area whose educational level was not indicated in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written




### **Variable label**: Proportion of low educated residents in 2014 
**Variable name**: socenv_proportion_low_education_2014  
**Variable description**: Proportion of low educated residents in residential area in 2014.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of intermediate educated residents in 2014  
**Variable name**: socenv_proportion_intermediate_education_2014  
**Variable description**: Proportion of intermediate educated residents in residential area in 2014.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of high educated residents in 2014  
**Variable name**: socenv_proportion_high_education_2014  
**Variable description**: Proportion of high educated residents in residential area in 2014.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



# Immigrants and ethnic minority groups


### **Variable label**: Proportion of western immigrants in 2006  
**Variable name**: socenv_proportion_western_immigrants_2006  
**Variable description**: Proportion of western immigrants in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of non-western immigrants in 2006  
**Variable name**: socenv_proportion_non_western_immigrants_2006  
**Variable description**: Proportion of non-western immigrants in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of western immigrants in 2011  
**Variable name**: socenv_proportion_western_immigrants_2011  
**Variable description**: Proportion of western immigrants in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of non-western immigrants in 2011  
**Variable name**: socenv_proportion_non_western_immigrants_2011  
**Variable description**: Proportion of non-western immigrants in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written




### **Variable label**: Proportion of immigrants of Moroccan origin in 2006  
**Variable name**: socenv_proportion_ethnicity_moroccan_2006  
**Variable description**: Proportion of immigrants of Moroccan origin in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of immigrants of Antillian and Aruban origin in 2006  
**Variable name**: socenv_proportion_ethnicity_antilles_aruba_2006  
**Variable description**: Proportion of immigrants of Antillian and Aruban origin in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of immigrants of Surinamese origin in 2006  
**Variable name**: socenv_proportion_ethnicity_surinamese_2006  
**Variable description**: Proportion of immigrants of Surinamese origin in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of immigrants of Turkish origin in 2006  
**Variable name**: socenv_proportion_ethnicity_turkey_2006  
**Variable description**: Proportion of immigrants of Turkish origin in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of immigrants of other origin in 2006  
**Variable name**: socenv_proportion_ethnicity_other_2006  
**Variable description**: Proportion of immigrants of other origin in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of immigrants of Moroccan origin in 2011  
**Variable name**: socenv_proportion_ethnicity_moroccan_2011  
**Variable description**: Proportion of immigrants of Moroccan origin in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of immigrants of Antillian and Aruban origin in 2011  
**Variable name**: socenv_proportion_ethnicity_antilles_aruba_2011  
**Variable description**: Proportion of immigrants of Antillian and Aruban origin in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of immigrants of Surinamese origin in 2011  
**Variable name**: socenv_proportion_ethnicity_surinamese_2011  
**Variable description**: Proportion of immigrants of Surinamese origin in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of immigrants of Turkish origin in 2011  
**Variable name**: socenv_proportion_ethnicity_turkey_2011  
**Variable description**: Proportion of immigrants of Turkish origin in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of immigrants of other origin in 2011  
**Variable name**: socenv_proportion_ethnicity_other_2011  
**Variable description**: Proportion of immigrants of other origin in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of foreigners and stateless persons in 2011  
**Variable name**: socenv_proportion_foreigners_stateless_persons_2011  
**Variable description**: Proportion of stateless foreigners in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of foreigners from Europe in 2011  
**Variable name**: socenv_proportion_foreigners_europe_2011  
**Variable description**: Proportion of European foreigners in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of foreigners from Africa in 2011  
**Variable name**: socenv_proportion_foreigners_africa_2011  
**Variable description**: Proportion of African foreigners in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of foreigners from America in 2011  
**Variable name**: socenv_proportion_foreigners_america_2011  
**Variable description**: Proportion of American foreigners in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of foreigners from Asia in 2011  
**Variable name**: socenv_proportion_foreigners_asia_2011  
**Variable description**: Proportion of Asian foreigners in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of foreigners from Oceania in 2011  
**Variable name**: socenv_proportion_foreigners_oceania_2011  
**Variable description**: Proportion of foreigners from Oceania in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of stateless persons in 2011  
**Variable name**: socenv_proportion_stateless_persons_2011  
**Variable description**: Proportion of stateless persons in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written


### **Variable label**: Proportion of foreigners in 2007  
**Variable name**: socenv_proportion_foreigners_2007  
**Variable description**: Proportion of foreigners in residential area in 2007.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of foreigners in 2011  
**Variable name**: socenv_proportion_foreigners_2011  
**Variable description**: Proportion of foreigners in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of residents with a migration background in 2011  
**Variable name**: socenv_proportion_residents_with_migration_background_2011  
**Variable description**: Proportion of residents with a migration background in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of foreigners in 2016  
**Variable name**: socenv_proportion_foreigners_2016  
**Variable description**: Proportion of foreigners in residential area in 2016.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of residents with a migration background in 2016  
**Variable name**: socenv_proportion_residents_with_migration_background_2016    
**Variable description**: Proportion of residents with a migration background in residential area in 2016.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of immigrants and Norwegian-born immigrant parents in 2011  
**Variable name**: socenv_prop_immigrants_norwegian_born_2011_total  
**Variable description**: Proportion of immigrants and Norwegian-born immigrant parents in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of immigrants in 2011  
**Variable name**: socenv_prop_immigrants_2011_total  
**Variable description**: Proportion of immigrants in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of Norwegian-born immigrant parents in 2011  
**Variable name**: socenv_prop_norwegian_born_immigr_parents_total_2011
**Variable description**: Proportion of Norwegian-born immigrant parents in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of Lithuanians in 2011  
**Variable name**: socenv_proportion_ethnicity_lithuanians_2011  
**Variable description**: Proportion of Lithuanians in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of Russians in 2011  
**Variable name**: socenv_proportion_ethnicity_russians_2011  
**Variable description**: Proportion of Russians in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of Poles in 2011  
**Variable name**: socenv_proportion_ethnicity_poles_2011  
**Variable description**: Proportion of Poles in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of Belorussians in 2011  
**Variable name**: socenv_proportion_ethnicity_belorussians_2011  
**Variable description**: Proportion of Belorussians in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of Ukrainians in 2011  
**Variable name**: socenv_proportion_ethnicity_ukrainians_2011  
**Variable description**: Proportion of Ukrainians in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of Jews in 2011  
**Variable name**: socenv_proportion_ethnicity_jews_2011  
**Variable description**: Proportion of Jews in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of Tatars in 2011  
**Variable name**: socenv_proportion_ethnicity_tatars_2011  
**Variable description**: Proportion of Tatars in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of Germans in 2011  
**Variable name**: socenv_proportion_ethnicity_germans_2011  
**Variable description**: Proportion of Germans in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of Romany in 2011  
**Variable name**: socenv_proportion_ethnicity_romany_2011  
**Variable description**: Proportion of Romany in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of Latvians in 2011  
**Variable name**: socenv_proportion_ethnicity_latvians_2011  
**Variable description**: Proportion of Latvians in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of Armenians in 2011  
**Variable name**: socenv_proportion_ethnicity_armenians_2011  
**Variable description**: Proportion of Armenians in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of residents of other origins in 2011  
**Variable name**: socenv_proportion_ethnicity_others_2011
**Variable description**: Proportion of residents of other origins in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of residents whose origin is not indicated in 2011  
**Variable name**: socenv_proportion_ethnicity_not_indicated_2011  
**Variable description**: Proportion of residents whose origin is not indicated in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



# Crime  


### **Variable label**: Number of criminal offenses per 1000 residents in 2007  
**Variable name**: socenv_number_criminal_offenses_per_1000_residents_2007    
**Variable description**: Number of criminal offenses per 1000 residents in residential area in 2007.       
**Variable type**: integer    
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of violent crimes per 1000 residents in 2007  
**Variable name**: socenv_number_violent_crimes_offenses_per_1000_residents_2007    
**Variable description**: Number of violent crimes per 1000 residents in residential area in 2007.       
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of thefts per 1000 residents in 2007  
**Variable name**: socenv_number_thefts_per_1000_residents_2007    
**Variable description**: Number of thefts per 1000 residents in residential area in 2007.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of criminal offenses per 1000 residents in 2011  
**Variable name**: socenv_number_criminal_offenses_per_1000_residents_2011    
**Variable description**: Number of criminal offenses per 1000 residents in residential area in 2011.       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of vandalism and public disorder per 1000 residents in 2011  
**Variable name**: socenv_number_vandalism_public_order_per_1000_residents_2011   
**Variable description**: Number of vandalism and public disorder per 1000 residents in residential area in 2011.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of violent crimes and sexual offenses per 1000 residents in 2011    
**Variable name**: socenv_number_violent_crimes_sexual_offenses_per_1000_residents_2011    
**Variable description**: Number of violent crimes and sexual offenses per 1000 residents in residential area in 2011.         
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of violent crimes per 1000 residents in 2011    
**Variable name**: socenv_number_violent_crimes_per_1000_residents_2011    
**Variable description**: Number of violent crimes per 1000 residents in residential area in 2011.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of thefts per 1000 residents in 2011    
**Variable name**: socenv_number_thefts_per_1000_residents_2011    
**Variable description**: Number of thefts per 1000 residents in residential area in 2011.       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of vandalism per 1000 residents in 2011   
**Variable name**: socenv_number_vandalism_per_1000_residents_2011    
**Variable description**: Number of vandalism per 1000 residents in residential area in 2011.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of public disorder per 1000 residents in 2011    
**Variable name**: socenv_number_public_order_per_1000_residents_2011    
**Variable description**: Number of public disorder per 1000 residents in residential area in 2011.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of criminal offenses per 1000 residents in 2014    
**Variable name**: socenv_number_criminal_offenses_per_1000_residents_2014    
**Variable description**: Number of criminal offenses per 1000 residents in residential area in 2014.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of criminal offenses per 1000 residents in 2015    
**Variable name**: socenv_number_criminal_offenses_per_1000_residents_2015    
**Variable description**: Number of criminal offenses per 1000 residents in residential area in 2015.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of criminal offenses per 1000 residents in 2016    
**Variable name**: socenv_number_criminal_offenses_per_1000_residents_2016    
**Variable description**: Number of criminal offenses per 1000 residents in residential area in 2016.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of vandalism and public disorder per 1000 residents in 2016    
**Variable name**: socenv_number_vandalism_public_order_per_1000_residents_2016   
**Variable description**: Number of vandalism and public disorder per 1000 residents in residential area in 2016.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of violent crimes and sexual offenses per 1000 residents in 2016  
**Variable name**: socenv_number_violent_crimes_sexual_offenses_per_1000_residents_2016   
**Variable description**: Number of violent crimes and sexual offenses per 1000 residents in residential area in 2016.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of violent crimes per 1000 residents in 2016    
**Variable name**: socenv_number_violent_crimes_per_1000_residents_2016   
**Variable description**: Number of violent crimes per 1000 residents in residential area in 2016.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of thefts per 1000 residents in 2016  
**Variable name**: socenv_number_thefts_per_1000_residents_2016    
**Variable description**: Number of thefts per 1000 residents in residential area in 2016.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of vandalism per 1000 residents in 2016    
**Variable name**: socenv_number_vandalism_per_1000_residents_2016    
**Variable description**: Number of vandalism per 1000 residents in residential area in 2016.          
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of public disorder per 1000 residents in 2016    
**Variable name**: socenv_number_public_order_per_1000_residents_2016    
**Variable description**: Number of public disorder per 1000 residents in residential area in 2016.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written
