---
title: "Social environmental (i.e. geospatial) RECORD"
output: html_document
---
# Connecting with Opal data server
## Login to server and assign study data
```{r, echo=FALSE}
#Load Opal R library
library(opal)
library(dplyr)
# Create an opal object with the login information
erasmus_opal <- opal.login()
#Login to Opal server and assign the content of the RECORD table(s) to your RStudio environment
# RECORD wave 1, part 1
opal.assign.table.tibble(erasmus_opal, 'RECORD_w1_1', 'RECORD.RECORD_w1_1', variables = list("Inc_St500", "Inc_St1000", "Inc_St2000"))
RECORD_w1_1a <- opal.execute(erasmus_opal,'RECORD_w1_1')
opal.assign.table.tibble(erasmus_opal, 'RECORD_W1_SocioEnviro', 'RECORD.RECORD_W1_SocioEnviro', variables = list ("URBANIZATION_GRADE_2009"))
RECORD_w1_1b <- opal.execute(erasmus_opal,'RECORD_W1_SocioEnviro')
opal.assign.table.tibble(erasmus_opal, 'MINDMAP_Area_identifiers_in_RECORD_W1_190521', 'RECORD.MINDMAP_Area_identifiers_in_RECORD_W1_190521', variables = list ("city", "neighbourhood","pc5"))
RECORD_w1_1c <- opal.execute(erasmus_opal,'MINDMAP_Area_identifiers_in_RECORD_W1_190521')

# RECORD wave 2
opal.assign.table.tibble(erasmus_opal, 'RECORD_W2_SocioEnviro', 'RECORD.RECORD_W2_SocioEnviro', variables = list ("URBANIZATION_GRADE_2009","AVERAGE_HOUSEHOLD_SIZE_2014","PROPORTION_UNOCCUPIED_DWELLINGS_2014","UNEMPLOYMENT_RATE_2014"))
RECORD_w2a <- opal.execute(erasmus_opal,'RECORD_W2_SocioEnviro')
opal.assign.table.tibble(erasmus_opal, 'MINDMAP_Area_identifiers_in_RECORD_W2_190521', 'RECORD.MINDMAP_Area_identifiers_in_RECORD_W2_190521', variables = list ("neighbourhood", "pc5"))
RECORD_w2b <- opal.execute(erasmus_opal,'MINDMAP_Area_identifiers_in_RECORD_W2_190521')

```
## Assign participant id as first column of your harmonized dataframes
```{r, echo=FALSE}
RECORD_w1_1<-merge(RECORD_w1_1a, RECORD_w1_1b, by="id")
RECORD_w1_1<-merge(RECORD_w1_1, RECORD_w1_1c, by="id")

RECORD_w2<-merge(RECORD_w2a, RECORD_w2b, by="id", all=TRUE)

socenv_RECORD_0 <- data.frame(id = RECORD_w1_1$id)
socenv_RECORD_1 <- data.frame(id = RECORD_w2$id)
```

## When you are done with your work, logout of Opal server
```{r, echo=FALSE}
opal.logout(erasmus_opal) 
```
---
# Table of Contents
1. [Urbanization grade](#Urbanization grade)  
2. [Demographics](#Demographics)  
3. [Housing](#Housing)  
4. [Income](#Income)  
5. [Unemployment](#Unemployment)  
6. [Social security](#Social security)  
7. [Educational level](#Educational level)  
8. [Immigrants and ethnic minority groups](#Immigrants and ethnic minority groups)
9. [Crime](#Crime)  
10. [Area indicators] (#Area indicators)  

# Urbanization grade

### **Variable label**: Urbanization grade in 2006  
**Variable name**: socenv_urbanization_grade_2006    
**Variable description**: Population density of the residential area (number of residents per km2) in 2006.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:
For RECORD, these data are available for neighbourhoods in 2009 and 2014, not in 2006.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  

### **Variable label**: Urbanization grade in 2007 
**Variable name**: socenv_urbanization_grade_0    
**Variable description**: Population density of the residential area (number of residents per km2) in 2007.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
For RECORD, this variable is available for neighbourhoods in 2009. This variable was calculated by: number of residents in area / area size. This variable has been linked to cohort respondents at wave 2007 and 2011 using their 5-digit postal code. References to the original data sources are listed in the WP7 deliverable report. 
**R script**:  
```{r, echo=TRUE}

socenv_RECORD_0$socenv_urbanization_grade_0 <-as.integer(round(RECORD_w1_1$URBANIZATION_GRADE_2009)) 

```  

### **Variable label**: Urbanization grade in 2009 
**Variable name**: socenv_urbanization_grade_2009    
**Variable description**: Population density of the residential area (number of residents per km2) in 2009.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}

```  

### **Variable label**: Urbanization grade in 2011 
**Variable name**: socenv_urbanization_grade_1    
**Variable description**: Population density of the residential area (number of residents per km2) in 2011.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete
**Harmonization comment**: 
For RECORD, this variable is available for neighbourhoods in 2009. This variable was calculated by: number of residents in area / area size. This variable has been linked to cohort respondents at wave 2007 and 2011 using their 5-digit postal code. References to the original data sources are listed in the WP7 deliverable report. 
**R script**:  
```{r, echo=TRUE}

socenv_RECORD_1$socenv_urbanization_grade_1 <-as.integer(round(RECORD_w2$URBANIZATION_GRADE_2009))

```  

### **Variable label**: Urbanization grade in 2014
**Variable name**: socenv_urbanization_grade_2014    
**Variable description**: Population density of the residential area (number of residents per km2) in 2014.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**: 
**R script**:  
```{r, echo=TRUE}

```    



# Demographics

### **Variable label**: Percentage of men in 2006  
**Variable name**: socenv_percentage_men_2006    
**Variable description**: Percentage of men in the residential area in 2006.  
**Variable type**: decimal
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of men in 2011  
**Variable name**: socenv_percentage_men_2011    
**Variable description**: Percentage of men in the residential area in 2011.  
**Variable type**: decimal
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of women in 2006  
**Variable name**: socenv_percentage_women_2006    
**Variable description**: Percentage of women in the residential area in 2006.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of women in 2011    
**Variable name**: socenv_percentage_women_2011    
**Variable description**: Percentage of women in the residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of residents aged 65 or older in 2006   
**Variable name**: socenv_percentage_65_older_2006   
**Variable description**: Percentage of residents aged 65 or older in residential area in 2006.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of residents aged 65 or older in 2007   
**Variable name**: socenv_percentage_65_older_2007   
**Variable description**: Percentage of residents aged 65 or older in residential area in 2007.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:   
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of residents aged 65 or older in 2011   
**Variable name**: socenv_percentage_65_older_2011   
**Variable description**: Percentage of residents aged 65 or older in residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of unmarried residents in 2008   
**Variable name**: socenv_percentage_unmarried_2008   
**Variable description**: Percentage of unmarried residents in residential area in 2008.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of unmarried residents in 2011   
**Variable name**: socenv_percentage_unmarried_2011   
**Variable description**: Percentage of unmarried residents in residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of married residents in 2006   
**Variable name**: socenv_percentage_married_2006   
**Variable description**: Percentage of married residents in residential area in 2006.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of married residents in 2008   
**Variable name**: socenv_percentage_married_2008   
**Variable description**: Percentage of married residents in residential area in 2008.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of married residents in 2011   
**Variable name**: socenv_percentage_married_2011   
**Variable description**: Percentage of married residents in residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of divorced residents in 2006   
**Variable name**: socenv_percentage_divorced_2006   
**Variable description**: Percentage of divorced residents in residential area in 2006.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of divorced residents in 2008   
**Variable name**: socenv_percentage_divorced_2008   
**Variable description**: Percentage of divorced residents in residential area in 2008.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of divorced residents in 2011   
**Variable name**: socenv_percentage_divorced_2011   
**Variable description**: Percentage of divorced residents in residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of widowed residents in 2006   
**Variable name**: socenv_percentage_widowed_2006   
**Variable description**: Percentage of widowed residents in residential area in 2006.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of widowed residents in 2008     
**Variable name**: socenv_percentage_widowed_2008   
**Variable description**: Percentage of widowed residents in residential area in 2008.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of widowed residents in 2011    
**Variable name**: socenv_percentage_widowed_2011   
**Variable description**: Percentage of widowed residents in residential area in 2011.  
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:   
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average household size in 2006   
**Variable name**: socenv_average_hh_size_2006   
**Variable description**: Average household size in residential area in 2006.  
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**: 
For RECORD, these data are available for neighbourhoods in 2014, not in 2006.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average household size in 2009   
**Variable name**: socenv_average_hh_size_2009   
**Variable description**: Average household size in residential area in 2009.  
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**: 
For RECORD, these data are available for neighbourhoodsin 2014, not in 2009. 
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average household size in 2011   
**Variable name**: socenv_average_hh_size_2011   
**Variable description**: Average household size in residential area in 2011.  
**Variable type**: integer       
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**: 
For RECORD, these data are available for neighbourhoods in 2014, not in 2011. 
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average household size in 2014   
**Variable name**: socenv_average_hh_size_1   
**Variable description**: Average household size in residential area in 2014.  
**Variable type**: integer       
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  complete
**Harmonization comment**: 
For RECORD, these data are available for neighbourhoods in 2014. This variable was calculated by: total number of residents in area / total number of households in area * 100. For harmonization purposes, this variable has been made integer and has been rounded. This variable has been linked cohort respondents using their 5-digit postal code.References of all data sources are listed in the WP7 deliverable report.
**R script**:  
```{r, echo=TRUE}  
socenv_RECORD_1$socenv_average_hh_size_1 <-as.integer(round(as.numeric(RECORD_w2$AVERAGE_HOUSEHOLD_SIZE_2014)))

```    

### **Variable label**: Average household size in 2015      
**Variable name**: socenv_average_hh_size_2015     
**Variable description**: Average household size in residential area in 2015.    
**Variable type**: integer    
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**: 
For RECORD, these data are available for neighbourhoods in 2014, not in 2015.  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average household size in 2016      
**Variable name**: socenv_average_hh_size_2016      
**Variable description**: Average household size in residential area in 2016.    
**Variable type**: integer       
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**: 
For RECORD, these data are available for neighbourhoods in 2014, not in 2016.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    


# Housing

### **Variable label**: Average value of dwellings in 1000 euros in 2006    
**Variable name**: socenv_avv_dwellings_2006  
**Variable description**: Average value of dwellings in 1000 euros in residential area in 2006.    
**Variable type**: integer   
**Variable unit**: 1000 euros   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**: 
Related data is available in RECORD (mean rank of price of sold dwellings in different street network buffers in 2002-2007), but these data cannot be harmonized into average value of dwellings in 1000 euros.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average value of dwellings in 1000 euros in 2011    
**Variable name**: socenv_avv_dwellings_2011  
**Variable description**: Average value of dwellings in 1000 euros in residential area in 2011.    
**Variable type**: integer   
**Variable unit**: 1000 euros   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average value of a plot (m2) in euros in 2007 (dwellings)    
**Variable name**: socenv_avv_dwelling_m2_2007  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area in 2007. 
**Variable type**: integer   
**Variable unit**: euros   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
For RECORD, these data are not available.  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average value of a plot (m2) in euros in 2011 (dwellings)  
**Variable name**: socenv_avv_dwelling_m2_2011  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area in 2011. 
**Variable type**: integer   
**Variable unit**: euros   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average value of a plot (m2) in euros in 2013 (dwellings)  
**Variable name**: socenv_avv_dwelling_m2_2013  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area in 2013. 
**Variable type**: integer   
**Variable unit**: euros   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average value of a plot (m2) in euros in 2014 (dwellings)  
**Variable name**: socenv_avv_dwelling_m2_2014  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area in 2014.    
**Variable type**: integer   
**Variable unit**: euros   
**Category coding**:   
**Harmonization status**: impossible 
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average value of a plot (m2) in euros in 2015 (dwellings)  
**Variable name**: socenv_avv_dwelling_m2_2015   
**Variable description**: Average value of a plot in euros (dwellings) in the residential area in 2015.
**Variable type**: integer   
**Variable unit**: euros    
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
For RECORD, these data are not available. 
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of unoccupied dwellings in 2011   
**Variable name**: socenv_perc_unocc_dwellings_2011
**Variable description**: Percentage of unoccupied dwellings in residential area in 2011.    
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible  
**Harmonization comment**:  
For RECORD, these data are available for neighbourhoods in 2014, not in 2011. 
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of unoccupied dwellings in 2012   
**Variable name**: socenv_perc_unocc_dwellings_2012
**Variable description**: Percentage of unoccupied dwellings in residential area in 2012.    
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible  
**Harmonization comment**:  
For RECORD, these data are available for neighbourhoods in 2014, not in 2011.  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of unoccupied dwellings in 2014   
**Variable name**: socenv_perc_unocc_dwellings_1
**Variable description**: Percentage of unoccupied dwellings in residential area in 2014.    
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete 
**Harmonization comment**:  
For RECORD, these data are available for neighbourhoods in 2014. This variable was caluclated by: total number of unoccupied dwellings in the area / total number of dwellings in the area * 100. This variable has been linked to cohort respondents at wave 2011 using their 5-digit postal code. References of all data sources are listed in the WP7 deliverable report.
**R script**:  
```{r, echo=TRUE}  
socenv_RECORD_1$socenv_perc_unocc_dwellings_1 <-as.numeric(RECORD_w2$PROPORTION_UNOCCUPIED_DWELLINGS_2014)

```    

# Income

### **Variable label**: Average income in 1000 euros in 2005  
**Variable name**: socenv_av_inc1000_2005  
**Variable description**: Average income in 1000 euros of residents in residential area in 2005.    
**Variable type**: integer       
**Variable unit**: 1000 euros   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in 1000 euros in 2006  
**Variable name**: socenv_av_inc1000_2006 
**Variable description**: Average income in 1000 euros of residents in residential area in 2006.    
**Variable type**: integer       
**Variable unit**: 1000 euros    
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in 1000 euros in 2011   
**Variable name**: socenv_av_inc1000_2011 
**Variable description**: Average income in 1000 euros of residents in residential area in 2011.    
**Variable type**: integer       
**Variable unit**: 1000 euros    
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2006  
**Variable name**: socenv_av_inc_2006  
**Variable description**: Average income in euros of residents in residential area in 2006.    
**Variable type**: integer         
**Variable unit**: euros    
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2007  
**Variable name**: socenv_av_inc_2007
**Variable description**: Average income in euros of residents in residential area in 2007.    
**Variable type**: integer        
**Variable unit**: euros    
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2011  
**Variable name**: socenv_av_inc_2011  
**Variable description**: Average income in euros of residents in residential area in 2011.    
**Variable type**: integer         
**Variable unit**: euros    
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2013  
**Variable name**: socenv_av_inc_2013  
**Variable description**: Average income in euros of residents in residential area in 2013.    
**Variable type**: integer         
**Variable unit**: euros    
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2014  
**Variable name**: socenv_av_inc_2014  
**Variable description**: Average income in euros of residents in residential area in 2014.    
**Variable type**: integer         
**Variable unit**: euros    
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2015  
**Variable name**: socenv_av_inc_2015  
**Variable description**: Average income in euros of residents in residential area in 2015.    
**Variable type**: integer          
**Variable unit**: euros     
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2016  
**Variable name**: socenv_av_inc_2016  
**Variable description**: Average income in euros of residents in residential area in 2016.    
**Variable type**: integer         
**Variable unit**: euros    
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in 1000 euros in 2005 (dichotomized)  
**Variable name**: socenv_av_inc1000dich_2005  
**Variable description**: Average income in 1000 euros of residents in residential area in 2005 (dichotomized: below/above country-specific net mean household income (OECD)).      
**Variable type**: integer     
**Variable unit**:   
**Category coding**: 

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  


```    

### **Variable label**: Average income in 1000 euros in 2006 (dichotomized)  
**Variable name**: socenv_av_inc1000dich_2006 
**Variable description**: Average income in 1000 euros of residents in residential area in 2006 (dichotomized: below/above country-specific net mean household income (OECD)).       
**Variable type**: integer     
**Variable unit**:    
**Category coding**:

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in 1000 euros in 2011 (dichotomized)   
**Variable name**: socenv_av_inc1000dich_2011 
**Variable description**: Average income in 1000 euros of residents in residential area in 2011 (dichotomized: below/above country-specific net mean household income (OECD)).      
**Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  


```    

### **Variable label**: Average income in euros in 2006 (dichotomized)  
**Variable name**: socenv_av_incdich_2006  
**Variable description**: Average income in euros of residents in residential area in 2006 (dichotomized: below/above country-specific net mean household income (OECD)).      
**Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2007 (dichotomized) 
**Variable name**: socenv_av_incdich_2007
**Variable description**: Average income in euros of residents in residential area in 2007 (dichotomized: below/above country-specific net mean household income (OECD)).       
**Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2011 (dichotomized)  
**Variable name**: socenv_av_incdich_2011  
**Variable description**: Average income in euros of residents in residential area in 2011 (dichotomized: below/above country-specific net mean household income (OECD)).       
**Variable type**: integer     
**Variable unit**:      
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2013 (dichotomized)  
**Variable name**: socenv_av_incdich_2013
**Variable description**: Average income in euros of residents in residential area in 2013 (dichotomized: below/above country-specific net mean household income (OECD)).      
**Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2014 (dichotomized) 
**Variable name**: socenv_av_incdich_2014  
**Variable description**: Average income in euros of residents in residential area in 2014 (dichotomized: below/above country-specific net mean household income (OECD)).      
**Variable type**: integer     
**Variable unit**:  
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2015 (dichotomized) 
**Variable name**: socenv_av_incdich_2015  
**Variable description**: Average income in euros of residents in residential area in 2015 (dichotomized: below/above country-specific net mean household income (OECD)).     
**Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2016 (dichotomized)  
**Variable name**: socenv_av_incdich_2016  
**Variable description**: Average income in euros of residents in residential area in 2016 (dichotomized: below/above country-specific net mean household income (OECD)).     
**Variable type**: integer     
**Variable unit**:     
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```   


 ### **Variable label**: Average household income in euros in 2006
**Variable name**: socenv_av_hhinc_500m_0  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address in 2006. 
**Variable type**: integer     
**Variable unit**: euros   
**Category coding**:   

**Harmonization status**: complete
**Harmonization comment**: In RECORD, these data were already available.
**R script**:  
```{r, echo=TRUE}
socenv_RECORD_0$socenv_av_hhinc_500m_0 <-as.integer(round(as.numeric(RECORD_w1_1$Inc_St500)))

```     

### **Variable label**: Average household income in euros in 2006
**Variable name**: socenv_av_hhinc_1000m_0  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address in 2006. 
**Variable type**: integer       
**Variable unit**: euros   
**Category coding**:   

**Harmonization status**: complete
**Harmonization comment**: In RECORD, these data were already available.
**R script**:  
```{r, echo=TRUE}
socenv_RECORD_0$socenv_av_hhinc_1000m_0 <-as.integer(round(as.numeric(RECORD_w1_1$Inc_St1000)))

```     

### **Variable label**: Average household income in euros in 2006
**Variable name**: socenv_av_hhinc_2000m_0  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address in 2006. 
**Variable type**: integer       
**Variable unit**: euros   
**Category coding**:   

**Harmonization status**: complete
**Harmonization comment**: In RECORD, these data were already available.
**R script**:  
```{r, echo=TRUE}
socenv_RECORD_0$socenv_av_hhinc_2000m_0 <-as.integer(round(as.numeric(RECORD_w1_1$Inc_St2000)))

```     


### **Variable label**: Average household income in euros in 2006 (dichotomized)
**Variable name**: socenv_av_hhincdich_500m_0  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address in 2006 (dichotomized: below/above country-specific net mean household income (OECD)).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**: complete
**Harmonization comment**: We dichotomized average household income in 500 meter street network buffer around participants by comparing it with the country-specific net mean household income (OECD) in 2008 (€24197).
**R script**:   
```{r, echo=TRUE}  
socenv_RECORD_0$socenv_av_hhincdich_500m_0 <- ifelse(as.numeric(RECORD_w1_1$Inc_St500) > 24197, 1, 0)

```  



### **Variable label**: Average household income in euros in 2006 (dichotomized)
**Variable name**: socenv_av_hhincdich_1000m_0  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address in 2006 (dichotomized: below/above country-specific net mean household income (OECD)).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**: complete
**Harmonization comment**: We dichotomized average household income in 1000 meter street network buffer around participants by comparing it with the country-specific net mean household income (OECD) in 2008 (€24197).
**R script**:   
```{r, echo=TRUE}  
socenv_RECORD_0$socenv_av_hhincdich_1000m_0 <- ifelse(as.numeric(RECORD_w1_1$Inc_St1000) > 24197, 1, 0)

```     

### **Variable label**: Average household income in euros in 2006 (dichotomized)
**Variable name**: socenv_av_hhincdich_2000m_0  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address in 2006 (dichotomized: below/above country-specific net mean household income (OECD)).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**: complete
**Harmonization comment**: We dichotomized average household income in 2000 meter street network buffer around participants by comparing it with the country-specific net mean household income (OECD) in 2008 (€24197).
**R script**:   
```{r, echo=TRUE}  
socenv_RECORD_0$socenv_av_hhincdich_2000m_0 <- ifelse(as.numeric(RECORD_w1_1$Inc_St2000) > 24197, 1, 0)

```    


### **Variable label**: Average income in 1000 euros in 2005 (Z standardised)  
**Variable name**: socenv_av_inc1000Z_2005  
**Variable description**: Average income in 1000 euros of residents in residential area in 2005 (standardized: mean=0 and sd=1).
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible  
**Harmonization comment**: 
These data are not available for RECORD.
**R script**:  
```{r, echo=TRUE} 



```       

### **Variable label**: Average income in 1000 euros in 2006 (Z standardized)  
**Variable name**: socenv_av_inc1000Z_2006 
**Variable description**: Average income in 1000 euros of residents in residential area in 2006 (standardized: mean=0 and sd=1).      
**Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Harmonization status**: impossible  
**Harmonization comment**: 
These data are not available for RECORD.
**R script**:  
```{r, echo=TRUE} 



```    

### **Variable label**: Average income in 1000 euros in 2011 (Z standardized)   
**Variable name**: socenv_av_inc1000Z_2011 
**Variable description**: Average income in 1000 euros of residents in residential area in 2011 (standardized: mean=0 and sd=1).   
**Variable type**: integer       
**Variable unit**:    
**Category coding**:   

**Harmonization status**: impossible  
**Harmonization comment**: 
These data are not available for RECORD.
**R script**:  
```{r, echo=TRUE} 



```      



### **Variable label**: Average income in euros in 2006 (Z standardized)  
**Variable name**: socenv_av_incZ_2006  
**Variable description**: Average income in euros of residents in residential area in 2006 (standardized: mean=0 and sd=1). 
**Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Harmonization status**: impossible  
**Harmonization comment**: 
These data are not available for RECORD.
**R script**:  
```{r, echo=TRUE} 



```     

### **Variable label**: Average income in euros in 2007 (Z standardized) 
**Variable name**: socenv_av_incZ_2007
**Variable description**: Average income in euros of residents in residential area in 2007 (standardized: mean=0 and sd=1).        
**Variable type**: integer       
**Variable unit**:    
**Category coding**:   

**Harmonization status**: impossible  
**Harmonization comment**: 
These data are not available for RECORD.
**R script**:  
```{r, echo=TRUE} 


```       

### **Variable label**: Average income in euros in 2011 (Z standardized)  
**Variable name**: socenv_av_incZ_2011  
**Variable description**: Average income in euros of residents in residential area in 2011 (standardized: mean=0 and sd=1).        
**Variable type**: integer       
**Variable unit**:     
**Category coding**:   

**Harmonization status**: impossible  
**Harmonization comment**: 
These data are not available for RECORD.
**R script**:  
```{r, echo=TRUE} 


```     

### **Variable label**: Average income in euros in 2013 (Z standardized)  
**Variable name**: socenv_av_incZ_2013
**Variable description**: Average income in euros of residents in residential area in 2013 (standardized: mean=0 and sd=1).      
**Variable type**: integer       
**Variable unit**:    
**Category coding**:   

**Harmonization status**: impossible  
**Harmonization comment**: 
These data are not available for RECORD.
**R script**:  
```{r, echo=TRUE} 


```    

### **Variable label**: Average income in euros in 2014 (Z standardized) 
**Variable name**: socenv_av_incZ_2014  
**Variable description**: Average income in euros of residents in residential area in 2014 (standardized: mean=0 and sd=1).       
**Variable type**: integer       
**Variable unit**:  
**Category coding**:   

**Harmonization status**: impossible  
**Harmonization comment**: 
These data are not available for RECORD.
**R script**:  
```{r, echo=TRUE} 


```     

### **Variable label**: Average income in euros in 2015 (Z standardized) 
**Variable name**: socenv_av_incZ_2015  
**Variable description**: Average income in euros of residents in residential area in 2015 (standardized: mean=0 and sd=1).    
**Variable type**: integer       
**Variable unit**:    
**Category coding**:   

**Harmonization status**: impossible  
**Harmonization comment**: 
These data are not available for RECORD.
**R script**:  
```{r, echo=TRUE} 


```     

### **Variable label**: Average income in euros in 2016 (Z standardized)  
**Variable name**: socenv_av_incZ_2016  
**Variable description**: Average income in euros of residents in residential area in 2016 (standardized: mean=0 and sd=1).    
**Variable type**: integer       
**Variable unit**:     
**Category coding**:   

**Harmonization status**: impossible  
**Harmonization comment**: 
These data are not available for RECORD.
**R script**:  
```{r, echo=TRUE} 


```   

### **Variable label**: Average household income in euros in 2006 (Z standardized)
**Variable name**: socenv_av_hhincZ_500m_2006  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address in 2006 (standardized: mean=0 and sd=1).    .       
**Variable type**: integer       
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**: Data on average household income in euros in 500 meter street network buffer zone around participants address are available in RECORD, but y and o are not available for France and therefore we cannot apply the formula Z=(x-y)/o (Z=standardized income variable with mean=0, sd=1; x=area-level average income from respondent; y=area-level average income in entire country; o=standard deviation of area-level income in entire country).
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    


### **Variable label**: Average household income in euros in 2006 (Z standardized)
**Variable name**: socenv_av_hhincZ_1000m_2006  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address in 2006 (standardized: mean=0 and sd=1).       
**Variable type**: integer       
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**: Data on average household income in euros in 1000 meter street network buffer zone around participants address are available in RECORD, but y and o are not available for France and therefore we cannot apply the formula Z=(x-y)/o (Z=standardized income variable with mean=0, sd=1; x=area-level average income from respondent; y=area-level average income in entire country; o=standard deviation of area-level income in entire country).
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average household income in euros in 2006 (Z standardized)
**Variable name**: socenv_av_hhincZ_2000m_2006  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address in 2006 (standardized: mean=0 and sd=1).       
**Variable type**: integer       
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**: Data on average household income in euros in 2000 meter street network buffer zone around participants address are available in RECORD, but y and o are not available for France and therefore we cannot apply the formula Z=(x-y)/o (Z=standardized income variable with mean=0, sd=1; x=area-level average income from respondent; y=area-level average income in entire country; o=standard deviation of area-level income in entire country).
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Percentage of income recipients in 2005
**Variable name**: socenv_perc_inc_recipients_2005  
**Variable description**: Percentage of income recipients in residential area in 2005.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:   
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of income recipients in 2011  
**Variable name**: socenv_perc_inc_recipients_2011  
**Variable description**: Percentage of income recipients in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

# Unemployment

### **Variable label**: Percentage of unemployed residents in 2006  
**Variable name**: socenv_perc_unemployment_2006  
**Variable description**: Percentage of unemployed residents in residential area in 2006.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are available for neighbourhoods in 2014, not in 2006.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of unemployed residents in 2007    
**Variable name**: socenv_perc_unemployment_2007    
**Variable description**: Percentage of unemployed residents in residential area in 2007.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are available for neighbourhoods in 2014, not in 2007.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of unemployed residents in 2011    
**Variable name**: socenv_perc_unemployment_2011    
**Variable description**: Percentage of unemployed residents in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are available for neighbourhoods in 2014, not in 2011.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of unemployed residents in 2014  
**Variable name**: socenv_perc_unemployment_1  
**Variable description**: Percentage of unemployed residents in residential area in 2014.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  complete
**Harmonization comment**:
For RECORD, these data are available for neighbourhoods in 2014. This variable includes the percentage of unemployed residents aged 15-64 years in the neighbourhood. This variable was calculated by: total number of unemployed residents aged 15-64 years old in the area / total number of residents aged 15-64 years old in the area * 100. This variable has been linked to cohort respondents at wave 2011 using their 5-digit postal code. References of the original data sources are listed in WP7 deliverable report.
**R script**:  
```{r, echo=TRUE}  
socenv_RECORD_1$socenv_perc_unemployment_1 <-as.numeric(RECORD_w2$UNEMPLOYMENT_RATE_2014)
 
```    

### **Variable label**: Percentage of unemployed residents in 2015  
**Variable name**: socenv_perc_unemployment_2015  
**Variable description**: Percentage of unemployed residents in residential area in 2015.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are available for neighbourhoods in 2014, not in 2015.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

# Social security

### **Variable label**: Percentage of social security beneficiaries in 2006  
**Variable name**: socenv_percentage_socsecben_2006   
**Variable description**: Percentage of social security beneficiaries in residential area in 2006.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of social security beneficiaries in 2007    
**Variable name**: socenv_percentage_socsecben_2007   
**Variable description**: Percentage of social security beneficiaries in residential area in 2007.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of social security beneficiaries in 2010  
**Variable name**: socenv_percentage_socsecben_2010   
**Variable description**: Percentage of social security beneficiaries in residential area in 2010.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of social security beneficiaries in 2011  
**Variable name**: socenv_percentage_socsecben_2011   
**Variable description**: Percentage of social security beneficiaries in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of social security beneficiaries in 2015  
**Variable name**: socenv_percentage_socsecben_2015   
**Variable description**: Percentage of social security beneficiaries in residential area in 2015.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of social security beneficiaries in 2016  
**Variable name**: socenv_percentage_socsecben_2016   
**Variable description**: Percentage of social security beneficiaries in residential area in 2016.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of residents with disability benefit in 2006  
**Variable name**: socenv_percentage_disben_2006   
**Variable description**: Percentage of residents with a disability benefit in residential area in 2006.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Percentage of residents with disability benefit in 2010  
**Variable name**: socenv_percentage_disben_2010   
**Variable description**: Percentage of residents with a disability benefit in residential area in 2010.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    


### **Variable label**: Percentage of residents with unemployment benefit in 2006  
**Variable name**: socenv_percentage_unemplben_2006   
**Variable description**: Percentage of residents with a unemployment benefit in residential area in 2006.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    


### **Variable label**: Percentage of residents with unemployment benefit in 2010  
**Variable name**: socenv_percentage_unemplben_2010   
**Variable description**: Percentage of residents with a unemployment benefit in residential area in 2010.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

# Educational level  

### **Variable label**: Percentage of low educated residents in 2011  
**Variable name**: socenv_perc_low_education_2011  
**Variable description**: Percentage of low educated residents in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of low educated residents in 2014 
**Variable name**: socenv_perc_low_education_2014  
**Variable description**: Percentage of low educated residents in residential area in 2014.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of intermediate educated residents in 2011  
**Variable name**: socenv_perc_itm_education_2011  
**Variable description**: Percentage of intermediate educated residents in residential area in 2011.
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of intermediate educated residents in 2014  
**Variable name**: socenv_perc_itm_education_2014  
**Variable description**: Percentage of intermediate educated residents in residential area in 2014.  
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of high educated residents in 2011  
**Variable name**: socenv_perc_high_education_2011  
**Variable description**: Percentage of high educated residents in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of high educated residents in 2014  
**Variable name**: socenv_perc_high_education_2014  
**Variable description**: Percentage of high educated residents in residential area in 2014.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

# Immigrants and ethnic minority groups

### **Variable label**: Percentage of immigrants in 2011  
**Variable name**: socenv_perc_immigrants_2011
**Variable description**: Percentage of immigrants in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of western immigrants in 2006  
**Variable name**: socenv_perc_west_imgs_2006  
**Variable description**: Percentage of western immigrants in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of western immigrants in 2011  
**Variable name**: socenv_perc_west_imgs_2011  
**Variable description**: Percentage of western immigrants in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of non-western immigrants in 2006  
**Variable name**: socenv_perc_nonwest_imgs_2006  
**Variable description**: Percentage of non-western immigrants in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of non-western immigrants in 2011  
**Variable name**: socenv_perc_nonwest_imgs_2011  
**Variable description**: Percentage of non-western immigrants in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of immigrants of Moroccan origin in 2006  
**Variable name**: socenv_perc_moroccan_2006  
**Variable description**: Percentage of immigrants of Moroccan origin in residential area in 2006.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of immigrants of Moroccan origin in 2011  
**Variable name**: socenv_perc_moroccan_2011  
**Variable description**: Percentage of immigrants of Moroccan origin in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of immigrants of Antillian and Aruban origin in 2006  
**Variable name**: socenv_perc_antaru_2006  
**Variable description**: Percentage of immigrants of Antillian and Aruban origin in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts. 
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of immigrants of Antillian and Aruban origin in 2011  
**Variable name**: socenv_perc_antaru_2011  
**Variable description**: Percentage of immigrants of Antillian and Aruban origin in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts. 
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of immigrants of Surinamese origin in 2006  
**Variable name**: socenv_perc_surinamese_2006  
**Variable description**: Percentage of immigrants of Surinamese origin in residential area in 2006.   
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of immigrants of Surinamese origin in 2011  
**Variable name**: socenv_perc_surinamese_2011  
**Variable description**: Percentage of immigrants of Surinamese origin in residential area in 2011.   
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of immigrants of Turkish origin in 2006  
**Variable name**: socenv_perc_turkey_2006  
**Variable description**: Percentage of immigrants of Turkish origin in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of immigrants of Turkish origin in 2011  
**Variable name**: socenv_perc_turkey_2011  
**Variable description**: Percentage of immigrants of Turkish origin in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of immigrants of other origin in 2006  
**Variable name**: socenv_perc_other_2006  
**Variable description**: Percentage of immigrants of other origin in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of immigrants of other origin in 2011  
**Variable name**: socenv_perc_other_2011  
**Variable description**: Percentage of immigrants of other origin in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of foreigners in 2007  
**Variable name**: socenv_perc_foreigners_2007  
**Variable description**: Percentage of foreigners in residential area in 2007.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Percentage of foreigners in 2011  
**Variable name**: socenv_perc_foreigners_2011  
**Variable description**: Percentage of foreigners in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**: 
Because the collected data on migrants / ethnic minority groups are all related to different groups, these data cannot be harmonized across countries / cohorts.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

# Crime  

### **Variable label**: Number of criminal offenses per 1000 residents in 2007  
**Variable name**: socenv_crimoff_2007    
**Variable description**: Number of criminal offenses per 1000 residents in residential area in 2007.  
**Variable type**: integer    
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of criminal offenses per 1000 residents in 2011  
**Variable name**: socenv_crimoff_2011    
**Variable description**: Number of criminal offenses per 1000 residents in residential area in 2011. 
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of criminal offenses per 1000 residents in 2014    
**Variable name**: socenv_crimoff_2014    
**Variable description**: Number of criminal offenses per 1000 residents in residential area in 2014.  
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of criminal offenses per 1000 residents in 2015    
**Variable name**: socenv_crimoff_2015    
**Variable description**: Number of criminal offenses per 1000 residents in residential area in 2015. 
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of criminal offenses per 1000 residents in 2016    
**Variable name**: socenv_crimoff_2016    
**Variable description**: Number of criminal offenses per 1000 residents in residential area in 2016. 
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of violent crimes per 1000 residents in 2007  
**Variable name**: socenv_violentcrim_2007    
**Variable description**: Number of violent crimes per 1000 residents in residential area in 2007.    
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of violent crimes per 1000 residents in 2011    
**Variable name**: socenv_violentcrim_2011    
**Variable description**: Number of violent crimes per 1000 residents in residential area in 2011.    
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of violent crimes per 1000 residents in 2016    
**Variable name**: socenv_violentcrim_2016   
**Variable description**: Number of violent crimes per 1000 residents in residential area in 2016.    
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of thefts per 1000 residents in 2007  
**Variable name**: socenv_thefts_2007    
**Variable description**: Number of thefts per 1000 residents in residential area in 2007.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of thefts per 1000 residents in 2011    
**Variable name**: socenv_thefts_2011    
**Variable description**: Number of thefts per 1000 residents in residential area in 2011.       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of thefts per 1000 residents in 2016  
**Variable name**: socenv_thefts_2016    
**Variable description**: Number of thefts per 1000 residents in residential area in 2016.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of vandalism and public disorder per 1000 residents in 2011  
**Variable name**: socenv_vandalism_po_2011   
**Variable description**: Number of vandalism and public disorder per 1000 residents in residential area in 2011.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of vandalism and public disorder per 1000 residents in 2016    
**Variable name**: socenv_vandalism_po_2016   
**Variable description**: Number of vandalism and public disorder per 1000 residents in residential area in 2016.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of violent crimes and sexual offenses per 1000 residents in 2011    
**Variable name**: socenv_violentcrim_sexoff_2011    
**Variable description**: Number of violent crimes and sexual offenses per 1000 residents in residential area in 2011.         
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of violent crimes and sexual offenses per 1000 residents in 2016  
**Variable name**: socenv_violentcrim_sexoff_2016   
**Variable description**: Number of violent crimes and sexual offenses per 1000 residents in residential area in 2016.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of vandalism per 1000 residents in 2011   
**Variable name**: socenv_vandalism_2011    
**Variable description**: Number of vandalism per 1000 residents in residential area in 2011.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of vandalism per 1000 residents in 2016    
**Variable name**: socenv_vandalism_2016    
**Variable description**: Number of vandalism per 1000 residents in residential area in 2016.          
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of public disorder per 1000 residents in 2011    
**Variable name**: socenv_po_2011    
**Variable description**: Number of public disorder per 1000 residents in residential area in 2011.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**: 
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of public disorder per 1000 residents in 2016    
**Variable name**: socenv_po_2016    
**Variable description**: Number of public disorder per 1000 residents in residential area in 2016.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
For RECORD, these data are not available.
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

#Area indicators

### **Variable label**: Area indicator: city  
**Variable name**: socenv_city_2004   
**Variable description**: City indicator in 2004.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


```  


### **Variable label**: Area indicator: city  
**Variable name**: socenv_city_2006   
**Variable description**: City indicator in 2006.       
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


```  

### **Variable label**: Area indicator: city  
**Variable name**: socenv_city_0  
**Variable description**: City indicator in 2007.       
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete
**Harmonization comment**: For RECORD, the indicator variables start with 33.  
**R script**:  
```{r, echo=TRUE}  
socenv_RECORD_0$socenv_city_0 <-as.integer(RECORD_w1_1$city) 

```  



### **Variable label**: Area indicator: city  
**Variable name**: socenv_city_2009   
**Variable description**: City indicator in 2009.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


```


### **Variable label**: Area indicator: city  
**Variable name**: socenv_city_2011   
**Variable description**: City indicator in 2011.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


```  


### **Variable label**: Area indicator: city  
**Variable name**: socenv_city_2014   
**Variable description**: City indicator in 2014.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


```  

### **Variable label**: Area indicator: municipality  
**Variable name**: socenv_municipality_2004   
**Variable description**: Municipality indicator in 2004.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}  

``` 

### **Variable label**: Area indicator: municipality  
**Variable name**: socenv_municipality_2006   
**Variable description**: Municipality indicator in 2006.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


```  



### **Variable label**: Area indicator: municipality  
**Variable name**: socenv_municipality_2007   
**Variable description**: Municipality indicator in 2007.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


```  



### **Variable label**: Area indicator: municipality  
**Variable name**: socenv_municipality_2011   
**Variable description**: Municipality indicator in 2011.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


```  

### **Variable label**: Area indicator: municipality  
**Variable name**: socenv_municipality_2014   
**Variable description**: Municipality indicator in 2014.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:   
**R script**:  
```{r, echo=TRUE}  

``` 

### **Variable label**: Area indicator: municipality  
**Variable name**: socenv_municipality_2016   
**Variable description**: Municipality indicator in 2016.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


```  


### **Variable label**: Area indicator: neighbourhood 
**Variable name**: socenv_neighbourhood_2004
**Variable description**: Neighbourhood indicator in 2004.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:     

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  

```  


### **Variable label**: Area indicator: neighbourhood 
**Variable name**: socenv_neighbourhood_2006
**Variable description**: Neighbourhood indicator in 2006.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:     

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


``` 


### **Variable label**: Area indicator: neighbourhood 
**Variable name**: socenv_neighbourhood_0
**Variable description**: Neighbourhood indicator in 2007.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:     

**Harmonization status**: complete
**Harmonization comment**: For RECORD, the indicator variables start with 33.  
**R script**:  
```{r, echo=TRUE}  

socenv_RECORD_0$socenv_neighbourhood_0 <-as.integer(RECORD_w1_1$neighbourhood) 

``` 

### **Variable label**: Area indicator: neighbourhood  
**Variable name**: socenv_neighbourhood_2009   
**Variable description**: Neighbourhood indicator in 2009.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


```


### **Variable label**: Area indicator: neighbourhood 
**Variable name**: socenv_neighbourhood_1
**Variable description**: Neighbourhood indicator in 2011.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:     

**Harmonization status**: complete
**Harmonization comment**: For RECORD, the indicator variables start with 33.  
**R script**:  
```{r, echo=TRUE}  

socenv_RECORD_1$socenv_neighbourhood_1 <-as.integer(RECORD_w2$neighbourhood) 

``` 


### **Variable label**: Area indicator: neighbourhood 
**Variable name**: socenv_neighbourhood_2014
**Variable description**: Neighbourhood indicator in 2014.       
**Variable type**: integer      
**Variable unit**:   
**Category coding**:     

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


``` 


### **Variable label**: Area indicator: 4-digit postal code 
**Variable name**: socenv_PC4_2004
**Variable description**: 4-digit postal code (PC4) indicator in 2004.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:     

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


```  



### **Variable label**: Area indicator: 4-digit postal code 
**Variable name**: socenv_PC4_2006
**Variable description**: 4-digit postal code (PC4) indicator in 2006.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:     

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


```  

### **Variable label**: Area indicator: 4-digit postal code 
**Variable name**: socenv_PC4_2011
**Variable description**: 4-digit postal code (PC4) indicator in 2011.      
**Variable type**: integer      
**Variable unit**:   
**Category coding**:     

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


``` 



### **Variable label**: Area indicator: 4-digit postal code 
**Variable name**: socenv_PC4_2011
**Variable description**: 4-digit postal code (PC4) indicator in 2014.     
**Variable type**: integer      
**Variable unit**:   
**Category coding**:     

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


``` 



### **Variable label**: Area indicator: 6-digit postal code
**Variable name**: socenv_PC6_2004
**Variable description**: 6-digit postal code (PC6) indicator in 2004.       
**Variable type**: integer      
**Variable unit**:   
**Category coding**:     

**Harmonization status**: impossible
**Harmonization comment**:
**R script**:  
```{r, echo=TRUE}  


```  



### **Variable label**: Area indicator: 6-digit postal code
**Variable name**: socenv_PC6_2006
**Variable description**: 6-digit postal code (PC6) indicator in 2006.       
**Variable type**: integer      
**Variable unit**:   
**Category coding**:     

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


``` 


### **Variable label**: Area indicator: 6-digit postal code
**Variable name**: socenv_PC6_2011
**Variable description**: 6-digit postal code (PC6) indicator in 2011.      
**Variable type**: integer      
**Variable unit**:   
**Category coding**:     

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


```  


### **Variable label**: Area indicator: 6-digit postal code
**Variable name**: socenv_PC6_2014
**Variable description**: 6-digit postal code (PC6) indicator in 2014.      
**Variable type**: integer      
**Variable unit**:   
**Category coding**:     

**Harmonization status**: impossible
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  


```  

### **Variable label**: Area indicator: 5-digit postal code 
**Variable name**: socenv_PC5_0 
**Variable description**: 5-digit postal code (PC5) indicator in 2007.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete
**Harmonization comment**:  
For RECORD, the indicator variables start with 33.
**R script**:  
```{r, echo=TRUE}  
socenv_RECORD_0$socenv_pc5_0 <-as.integer(RECORD_w1_1$pc5)


```



### **Variable label**: Area indicator: 5-digit postal code 
**Variable name**: socenv_PC5_1 
**Variable description**: 5-digit postal code (PC5) indicator in 2011.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete
**Harmonization comment**:  
For RECORD, the indicator variables start with 33.
**R script**:  
```{r, echo=TRUE}  
socenv_RECORD_1$socenv_pc5_1 <-as.integer(RECORD_w2$pc5) 


```


