---
title: "Social environmental (i.e. geospatial) RECORD"
output: html_document
---
# Connecting with Opal data server
## Login to server and assign study data
```{r, echo=FALSE}
#Load Opal R library
library(opal)
library(dplyr)
# Create an opal object with the login information
erasmus_opal <- opal.login()
#Login to Opal server and assign the content of the RECORD table(s) to your RStudio environment
# RECORD wave 1, part 1
opal.assign.table.tibble(erasmus_opal, 'RECORD_w1_1', 'RECORD.RECORD_w1_1', variables = list("Inc_St500", "Inc_St1000", "Inc_St2000"))
RECORD_w1_1a <- opal.execute(erasmus_opal,'RECORD_w1_1')
opal.assign.table.tibble(erasmus_opal, 'RECORD_W1_SocioEnviro', 'RECORD.RECORD_W1_SocioEnviro', variables = list ("URBANIZATION_GRADE_2009"))
RECORD_w1_1b <- opal.execute(erasmus_opal,'RECORD_W1_SocioEnviro')
opal.assign.table.tibble(erasmus_opal, 'MINDMAP_Area_identifiers_in_RECORD_W1_190521', 'RECORD.MINDMAP_Area_identifiers_in_RECORD_W1_190521', variables = list ("city", "neighbourhood","pc5"))
RECORD_w1_1c <- opal.execute(erasmus_opal,'MINDMAP_Area_identifiers_in_RECORD_W1_190521')

# RECORD wave 2
opal.assign.table.tibble(erasmus_opal, 'RECORD_W2_SocioEnviro', 'RECORD.RECORD_W2_SocioEnviro', variables = list ("URBANIZATION_GRADE_2009","AVERAGE_HOUSEHOLD_SIZE_2014","PROPORTION_UNOCCUPIED_DWELLINGS_2014","UNEMPLOYMENT_RATE_2014"))
RECORD_w2a <- opal.execute(erasmus_opal,'RECORD_W2_SocioEnviro')
opal.assign.table.tibble(erasmus_opal, 'MINDMAP_Area_identifiers_in_RECORD_W2_190521', 'RECORD.MINDMAP_Area_identifiers_in_RECORD_W2_190521', variables = list ("neighbourhood", "pc5"))
RECORD_w2b <- opal.execute(erasmus_opal,'MINDMAP_Area_identifiers_in_RECORD_W2_190521')

```
## Assign participant id as first column of your harmonized dataframes
```{r, echo=FALSE}
RECORD_w1_1<-merge(RECORD_w1_1a, RECORD_w1_1b, by="id")
RECORD_w1_1<-merge(RECORD_w1_1, RECORD_w1_1c, by="id")

RECORD_w2<-merge(RECORD_w2a, RECORD_w2b, by="id", all=TRUE)

socenv_RECORD_0 <- data.frame(id = RECORD_w1_1$id)
socenv_RECORD_1 <- data.frame(id = RECORD_w2$id)
```

## When you are done with your work, logout of Opal server
```{r, echo=FALSE}
opal.logout(erasmus_opal) 
```


---
# Table of Contents
1. [Urbanization grade](#Urbanzation grade)  
2. [Demographics](#Demographics)  
3. [Housing](#Housing)  
4. [Income](#Income)  
5. [Unemployment](#Unemployment)  
6. [Social security](#Social security)  
7. [Educational level](#Educational level)  
8. [Immigrants and ethnic minority groups](#Immigrants and ethnic minority groups)  
9. [Crime](#Crime)
10. [Area indicators] (#Area indicators)
  

# Urbanization grade

### **Variable label**: Urbanization grade  
**Variable name**: socenv_urbanization_grade_0    
**Variable description**: Population density of the residential area (number of residents per km2). 
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete 
**Harmonization comment**:  
For RECORD, this variable is available for neighbourhoods in 2009. This variable was calculated by: number of residents in area / area size. This variable has been linked to cohort respondents at wave 2007 and 2011 using their 5-digit postal code. References to the original data sources are listed in the WP7 deliverable report. 
**R script**:  
```{r, echo=TRUE}

socenv_RECORD_0$socenv_urbanization_grade_0 <-as.integer(round(RECORD_w1_1$URBANIZATION_GRADE_2009)) 

```  
 



### **Variable label**: Urbanization grade  
**Variable name**: socenv_urbanization_grade_1   
**Variable description**: Population density of the residential area (number of residents per km2). 
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete
**Harmonization comment**: 
For RECORD, this variable is available for neighbourhoods in 2009. This variable was calculated by: number of residents in area / area size. This variable has been linked to cohort respondents at wave 2007 and 2011 using their 5-digit postal code. References to the original data sources are listed in the WP7 deliverable report. 
**R script**:  
```{r, echo=TRUE}

socenv_RECORD_1$socenv_urbanization_grade_1 <-as.integer(round(RECORD_w2$URBANIZATION_GRADE_2009))

```  
 



### **Variable label**: Urbanization grade  
**Variable name**: socenv_urbanization_grade_2    
**Variable description**: Population density of the residential area (number of residents per km2). 
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Urbanization grade  
**Variable name**: socenv_urbanization_grade_3    
**Variable description**: Population density of the residential area (number of residents per km2). 
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Urbanization grade  
**Variable name**: socenv_urbanization_grade_4    
**Variable description**: Population density of the residential area (number of residents per km2). 
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Urbanization grade  
**Variable name**: socenv_urbanization_grade_5    
**Variable description**: Population density of the residential area (number of residents per km2). 
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Urbanization grade  
**Variable name**: socenv_urbanization_grade_6    
**Variable description**: Population density of the residential area (number of residents per km2). 
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



# Demographics

### **Variable label**: Percentage of men 
**Variable name**: socenv_percentage_men_0    
**Variable description**: Percentage of men in the residential area.  
**Variable type**: decimal
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Percentage of men 
**Variable name**: socenv_percentage_men_1    
**Variable description**: Percentage of men in the residential area.  
**Variable type**: decimal
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Percentage of men 
**Variable name**: socenv_percentage_men_2    
**Variable description**: Percentage of men in the residential area.  
**Variable type**: decimal
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Percentage of men 
**Variable name**: socenv_percentage_men_3    
**Variable description**: Percentage of men in the residential area.  
**Variable type**: decimal
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Percentage of men 
**Variable name**: socenv_percentage_men_4    
**Variable description**: Percentage of men in the residential area.  
**Variable type**: decimal
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Percentage of men 
**Variable name**: socenv_percentage_men_5    
**Variable description**: Percentage of men in the residential area.  
**Variable type**: decimal
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Percentage of men 
**Variable name**: socenv_percentage_men_6    
**Variable description**: Percentage of men in the residential area.  
**Variable type**: decimal
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Percentage of women  
**Variable name**: socenv_percentage_women_0    
**Variable description**: Percentage of women in the residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Percentage of women  
**Variable name**: socenv_percentage_women_1   
**Variable description**: Percentage of women in the residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Percentage of women  
**Variable name**: socenv_percentage_women_2   
**Variable description**: Percentage of women in the residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of women  
**Variable name**: socenv_percentage_women_3   
**Variable description**: Percentage of women in the residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of women  
**Variable name**: socenv_percentage_women_4   
**Variable description**: Percentage of women in the residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of women  
**Variable name**: socenv_percentage_women_5   
**Variable description**: Percentage of women in the residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of women  
**Variable name**: socenv_percentage_women_6   
**Variable description**: Percentage of women in the residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents aged 65 or older   
**Variable name**: socenv_percentage_65_older_0   
**Variable description**: Percentage of residents aged 65 or older in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents aged 65 or older   
**Variable name**: socenv_percentage_65_older_1   
**Variable description**: Percentage of residents aged 65 or older in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents aged 65 or older   
**Variable name**: socenv_percentage_65_older_2   
**Variable description**: Percentage of residents aged 65 or older in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents aged 65 or older   
**Variable name**: socenv_percentage_65_older_3   
**Variable description**: Percentage of residents aged 65 or older in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents aged 65 or older   
**Variable name**: socenv_percentage_65_older_4   
**Variable description**: Percentage of residents aged 65 or older in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents aged 65 or older   
**Variable name**: socenv_percentage_65_older_5   
**Variable description**: Percentage of residents aged 65 or older in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents aged 65 or older   
**Variable name**: socenv_percentage_65_older_6   
**Variable description**: Percentage of residents aged 65 or older in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of unmarried residents  
**Variable name**: socenv_percentage_unmarried_0   
**Variable description**: Percentage of unmarried residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of unmarried residents  
**Variable name**: socenv_percentage_unmarried_1   
**Variable description**: Percentage of unmarried residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of unmarried residents  
**Variable name**: socenv_percentage_unmarried_2   
**Variable description**: Percentage of unmarried residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of unmarried residents  
**Variable name**: socenv_percentage_unmarried_3   
**Variable description**: Percentage of unmarried residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of unmarried residents  
**Variable name**: socenv_percentage_unmarried_4   
**Variable description**: Percentage of unmarried residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of unmarried residents  
**Variable name**: socenv_percentage_unmarried_5   
**Variable description**: Percentage of unmarried residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of unmarried residents  
**Variable name**: socenv_percentage_unmarried_6   
**Variable description**: Percentage of unmarried residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of married residents  
**Variable name**: socenv_percentage_married_0   
**Variable description**: Percentage of married residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of married residents  
**Variable name**: socenv_percentage_married_1    
**Variable description**: Percentage of married residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of married residents  
**Variable name**: socenv_percentage_married_2   
**Variable description**: Percentage of married residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of married residents  
**Variable name**: socenv_percentage_married_3   
**Variable description**: Percentage of married residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of married residents  
**Variable name**: socenv_percentage_married_4   
**Variable description**: Percentage of married residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of married residents  
**Variable name**: socenv_percentage_married_5   
**Variable description**: Percentage of married residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of married residents  
**Variable name**: socenv_percentage_married_6   
**Variable description**: Percentage of married residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of divorced residents   
**Variable name**: socenv_percentage_divorced_0   
**Variable description**: Percentage of divorced residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of divorced residents   
**Variable name**: socenv_percentage_divorced_1   
**Variable description**: Percentage of divorced residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of divorced residents   
**Variable name**: socenv_percentage_divorced_2   
**Variable description**: Percentage of divorced residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of divorced residents   
**Variable name**: socenv_percentage_divorced_3   
**Variable description**: Percentage of divorced residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of divorced residents   
**Variable name**: socenv_percentage_divorced_4   
**Variable description**: Percentage of divorced residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of divorced residents   
**Variable name**: socenv_percentage_divorced_5   
**Variable description**: Percentage of divorced residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of divorced residents   
**Variable name**: socenv_percentage_divorced_6   
**Variable description**: Percentage of divorced residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of widowed residents   
**Variable name**: socenv_percentage_widowed_0   
**Variable description**: Percentage of widowed residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of widowed residents   
**Variable name**: socenv_percentage_widowed_1   
**Variable description**: Percentage of widowed residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of widowed residents   
**Variable name**: socenv_percentage_widowed_2   
**Variable description**: Percentage of widowed residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of widowed residents   
**Variable name**: socenv_percentage_widowed_3   
**Variable description**: Percentage of widowed residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of widowed residents   
**Variable name**: socenv_percentage_widowed_4   
**Variable description**: Percentage of widowed residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of widowed residents   
**Variable name**: socenv_percentage_widowed_5   
**Variable description**: Percentage of widowed residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of widowed residents   
**Variable name**: socenv_percentage_widowed_6   
**Variable description**: Percentage of widowed residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household size  
**Variable name**: socenv_average_hh_size_0
**Variable description**: Average household size in residential area.  
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household size  
**Variable name**: socenv_average_hh_size_1
**Variable description**: Average household size in residential area.  
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  complete
**Harmonization comment**: 
For RECORD, these data are available for neighbourhoods in 2014. This variable was calculated by: total number of residents in area / total number of households in area * 100. For harmonization purposes, this variable has been made integer and has been rounded. This variable has been linked cohort respondents using their 5-digit postal code.References of all data sources are listed in the WP7 deliverable report.
**R script**:  
```{r, echo=TRUE}

socenv_RECORD_1$socenv_average_hh_size_1 <-as.integer(round(as.numeric(RECORD_w2$AVERAGE_HOUSEHOLD_SIZE_2014)))

```


### **Variable label**: Average household size  
**Variable name**: socenv_average_hh_size_2
**Variable description**: Average household size in residential area.  
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household size  
**Variable name**: socenv_average_hh_size_3
**Variable description**: Average household size in residential area.  
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household size  
**Variable name**: socenv_average_hh_size_4
**Variable description**: Average household size in residential area.  
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household size  
**Variable name**: socenv_average_hh_size_5
**Variable description**: Average household size in residential area.  
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household size  
**Variable name**: socenv_average_hh_size_6
**Variable description**: Average household size in residential area.  
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



# Housing

### **Variable label**: Average value of dwellings in 1000 euros    
**Variable name**: socenv_avv_dwellings_0 
**Variable description**: Average value of dwellings in 1000 euros in residential area.    
**Variable type**: integer   
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average value of dwellings in 1000 euros    
**Variable name**: socenv_avv_dwellings_1 
**Variable description**: Average value of dwellings in 1000 euros in residential area.    
**Variable type**: integer   
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average value of dwellings in 1000 euros    
**Variable name**: socenv_avv_dwellings_2 
**Variable description**: Average value of dwellings in 1000 euros in residential area.    
**Variable type**: integer   
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average value of dwellings in 1000 euros    
**Variable name**: socenv_avv_dwellings_3 
**Variable description**: Average value of dwellings in 1000 euros in residential area.    
**Variable type**: integer   
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average value of dwellings in 1000 euros    
**Variable name**: socenv_avv_dwellings_4 
**Variable description**: Average value of dwellings in 1000 euros in residential area.    
**Variable type**: integer   
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average value of dwellings in 1000 euros    
**Variable name**: socenv_avv_dwellings_5 
**Variable description**: Average value of dwellings in 1000 euros in residential area.    
**Variable type**: integer   
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average value of dwellings in 1000 euros    
**Variable name**: socenv_avv_dwellings_6 
**Variable description**: Average value of dwellings in 1000 euros in residential area.    
**Variable type**: integer   
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average value of a plot (m2) in euros (dwellings)    
**Variable name**: socenv_avv_dwelling_m2_0  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area.    
**Variable type**: integer   
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average value of a plot (m2) in euros (dwellings)    
**Variable name**: socenv_avv_dwelling_m2_1  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area.    
**Variable type**: integer   
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average value of a plot (m2) in euros (dwellings)    
**Variable name**: socenv_avv_dwelling_m2_2  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area.    
**Variable type**: integer   
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average value of a plot (m2) in euros (dwellings)    
**Variable name**: socenv_avv_dwelling_m2_3  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area.    
**Variable type**: integer   
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average value of a plot (m2) in euros (dwellings)    
**Variable name**: socenv_avv_dwelling_m2_4  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area.    
**Variable type**: integer   
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average value of a plot (m2) in euros (dwellings)    
**Variable name**: socenv_avv_dwelling_m2_5  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area.    
**Variable type**: integer   
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average value of a plot (m2) in euros (dwellings)    
**Variable name**: socenv_avv_dwelling_m2_6  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area.    
**Variable type**: integer   
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of unoccupied dwellings   
**Variable name**: socenv_perc_unocc_dwellings_0
**Variable description**: Percentage of unoccupied dwellings in residential area.    
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of unoccupied dwellings   
**Variable name**: socenv_perc_unocc_dwellings_1
**Variable description**: Percentage of unoccupied dwellings in residential area.    
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete 
**Harmonization comment**:  
For RECORD, these data are available for neighbourhoods in 2014. This variable was caluclated by: total number of unoccupied dwellings in the area / total number of dwellings in the area * 100. This variable has been linked to cohort respondents at wave 2011 using their 5-digit postal code. References of all data sources are listed in the WP7 deliverable report.
**R script**:  
```{r, echo=TRUE}

socenv_RECORD_1$socenv_perc_unocc_dwellings_1 <-as.numeric(RECORD_w2$PROPORTION_UNOCCUPIED_DWELLINGS_2014)

```    




### **Variable label**: Percentage of unoccupied dwellings   
**Variable name**: socenv_perc_unocc_dwellings_2
**Variable description**: Percentage of unoccupied dwellings in residential area.    
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of unoccupied dwellings   
**Variable name**: socenv_perc_unocc_dwellings_3
**Variable description**: Percentage of unoccupied dwellings in residential area.    
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of unoccupied dwellings   
**Variable name**: socenv_perc_unocc_dwellings_4
**Variable description**: Percentage of unoccupied dwellings in residential area.    
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of unoccupied dwellings   
**Variable name**: socenv_perc_unocc_dwellings_5
**Variable description**: Percentage of unoccupied dwellings in residential area.    
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of unoccupied dwellings   
**Variable name**: socenv_perc_unocc_dwellings_6
**Variable description**: Percentage of unoccupied dwellings in residential area.    
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



# Income

### **Variable label**: Average income in 1000 euros 
**Variable name**: socenv_av_inc1000_0  
**Variable description**: Average income in 1000 euros of residents in residential area.    
**Variable type**: integer     
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros 
**Variable name**: socenv_av_inc1000_1  
**Variable description**: Average income in 1000 euros of residents in residential area.    
**Variable type**: integer     
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros 
**Variable name**: socenv_av_inc1000_2  
**Variable description**: Average income in 1000 euros of residents in residential area.    
**Variable type**: integer     
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros 
**Variable name**: socenv_av_inc1000_3  
**Variable description**: Average income in 1000 euros of residents in residential area.    
**Variable type**: integer     
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros 
**Variable name**: socenv_av_inc1000_4  
**Variable description**: Average income in 1000 euros of residents in residential area.    
**Variable type**: integer     
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros 
**Variable name**: socenv_av_inc1000_5  
**Variable description**: Average income in 1000 euros of residents in residential area.    
**Variable type**: integer     
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros 
**Variable name**: socenv_av_inc1000_6  
**Variable description**: Average income in 1000 euros of residents in residential area.    
**Variable type**: integer     
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in euros 
**Variable name**: socenv_av_inc_0  
**Variable description**: Average income in euros of residents in residential area.    
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in euros 
**Variable name**: socenv_av_inc_1  
**Variable description**: Average income in euros of residents in residential area.    
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in euros 
**Variable name**: socenv_av_inc_2  
**Variable description**: Average income in euros of residents in residential area.    
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in euros 
**Variable name**: socenv_av_inc_3  
**Variable description**: Average income in euros of residents in residential area.    
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in euros 
**Variable name**: socenv_av_inc_4 
**Variable description**: Average income in euros of residents in residential area.    
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in euros 
**Variable name**: socenv_av_inc_5  
**Variable description**: Average income in euros of residents in residential area.    
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in euros 
**Variable name**: socenv_av_inc_6  
**Variable description**: Average income in euros of residents in residential area.    
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros (dichotomized)  
**Variable name**: socenv_av_incdich1000_0 
**Variable description**: Average income in 1000 euros of residents in residential area (dichotomized: below/above country-specific mean household income).    
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros (dichotomized)  
**Variable name**: socenv_av_incdich1000_1 
**Variable description**: Average income in 1000 euros of residents in residential area (dichotomized: below/above country-specific mean household income).    
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros (dichotomized)  
**Variable name**: socenv_av_incdich1000_2 
**Variable description**: Average income in 1000 euros of residents in residential area (dichotomized: below/above country-specific mean household income).    
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros (dichotomized)  
**Variable name**: socenv_av_incdich1000_3 
**Variable description**: Average income in 1000 euros of residents in residential area (dichotomized: below/above country-specific mean household income).    
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros (dichotomized)  
**Variable name**: socenv_av_incdich1000_4 
**Variable description**: Average income in 1000 euros of residents in residential area (dichotomized: below/above country-specific mean household income).    
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros (dichotomized)  
**Variable name**: socenv_av_incdich1000_5 
**Variable description**: Average income in 1000 euros of residents in residential area (dichotomized: below/above country-specific mean household income).    
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros (dichotomized)  
**Variable name**: socenv_av_incdich1000_6 
**Variable description**: Average income in 1000 euros of residents in residential area (dichotomized: below/above country-specific mean household income).    
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in euros (dichotomized) 
**Variable name**: socenv_av_incdich_0  
**Variable description**: Average income in euros of residents in residential area (dichotomized: below/above country-specific  mean household income).     
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in euros (dichotomized) 
**Variable name**: socenv_av_incdich_1  
**Variable description**: Average income in euros of residents in residential area (dichotomized: below/above country-specific  mean household income).     
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in euros (dichotomized) 
**Variable name**: socenv_av_incdich_2  
**Variable description**: Average income in euros of residents in residential area (dichotomized: below/above country-specific  mean household income).     
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in euros (dichotomized) 
**Variable name**: socenv_av_incdich_3  
**Variable description**: Average income in euros of residents in residential area (dichotomized: below/above country-specific  mean household income).     
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in euros (dichotomized) 
**Variable name**: socenv_av_incdich_4  
**Variable description**: Average income in euros of residents in residential area (dichotomized: below/above country-specific  mean household income).     
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in euros (dichotomized) 
**Variable name**: socenv_av_incdich_5  
**Variable description**: Average income in euros of residents in residential area (dichotomized: below/above country-specific  mean household income).     
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in euros (dichotomized) 
**Variable name**: socenv_av_incdich_6  
**Variable description**: Average income in euros of residents in residential area (dichotomized: below/above country-specific  mean household income).     
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_500m_0  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: complete
**Harmonization comment**: In RECORD, these data were already available for 2006.
**R script**:  
```{r, echo=TRUE}

socenv_RECORD_0$socenv_av_hhinc_500m_0 <-as.integer(round(as.numeric(RECORD_w1_1$Inc_St500)))

```     




### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_500m_1  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_500m_2  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_500m_3  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_500m_4  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_500m_5  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_500m_6  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_1000m_0  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: complete
**Harmonization comment**: In RECORD, these data were already available for 2006.
**R script**:  
```{r, echo=TRUE}
socenv_RECORD_0$socenv_av_hhinc_1000m_0 <-as.integer(round(as.numeric(RECORD_w1_1$Inc_St1000)))

```     




### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_1000m_1  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_1000m_2  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_1000m_3  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_1000m_4  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_1000m_5  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_1000m_6  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_2000m_0  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: complete
**Harmonization comment**: In RECORD, these data were already available for 2006.
**R script**:  
```{r, echo=TRUE}

socenv_RECORD_0$socenv_av_hhinc_2000m_0 <-as.integer(round(as.numeric(RECORD_w1_1$Inc_St2000)))

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_2000m_1  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address.
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_2000m_2  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_2000m_3  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_2000m_4  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address.
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_2000m_5  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_2000m_6  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_500m_0  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: complete
**Harmonization comment**: We dichotomized average net household income in 500 meter street network buffer around participants address in 2006 by comparing it with the country-specific net mean household income (OECD) in 2008 (24197).
**R script**:   
```{r, echo=TRUE}  

socenv_RECORD_0$socenv_av_hhincdich_500m_0 <- ifelse(as.numeric(RECORD_w1_1$Inc_St500) > 24197, 1, 0)

```


### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_500m_1  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_500m_2  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_500m_3  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_500m_4  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_500m_5  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_500m_6  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_1000m_0  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: complete
**Harmonization comment**: We dichotomized average net household income in 1000 meter street network buffer around participants address in 2006 by comparing it with the country-specific net mean household income (OECD) in 2008 (24197).
**R script**:   
```{r, echo=TRUE}

socenv_RECORD_0$socenv_av_hhincdich_1000m_0 <- ifelse(as.numeric(RECORD_w1_1$Inc_St1000) > 24197, 1, 0)

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_1000m_1  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_1000m_2  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_1000m_3  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_1000m_4  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_1000m_5  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_1000m_6  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_2000m_0  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: complete
**Harmonization comment**: We dichotomized average net household income in 2000 meter street network buffer around participants address in 2006 by comparing it with the country-specific net mean household income (OECD) in 2008 (24197).
**R script**:   
```{r, echo=TRUE} 

socenv_RECORD_0$socenv_av_hhincdich_2000m_0 <- ifelse(as.numeric(RECORD_w1_1$Inc_St2000) > 24197, 1, 0)

```


### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_2000m_1  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_2000m_2  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_2000m_3  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_2000m_4  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_2000m_5  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_2000m_6  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros (Z standardised)  
**Variable name**: socenv_av_inc1000Z_0  
**Variable description**: Average income in 1000 euros of residents in residential area (standardized: mean=0 and sd=1).
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros (Z standardised)  
**Variable name**: socenv_av_inc1000Z_1  
**Variable description**: Average income in 1000 euros of residents in residential area (standardized: mean=0 and sd=1).
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros (Z standardised)  
**Variable name**: socenv_av_inc1000Z_2  
**Variable description**: Average income in 1000 euros of residents in residential area (standardized: mean=0 and sd=1).
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros (Z standardised)  
**Variable name**: socenv_av_inc1000Z_3  
**Variable description**: Average income in 1000 euros of residents in residential area (standardized: mean=0 and sd=1).
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros (Z standardised)  
**Variable name**: socenv_av_inc1000Z_4  
**Variable description**: Average income in 1000 euros of residents in residential area (standardized: mean=0 and sd=1).
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros (Z standardised)  
**Variable name**: socenv_av_inc1000Z_5  
**Variable description**: Average income in 1000 euros of residents in residential area (standardized: mean=0 and sd=1).
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros (Z standardised)  
**Variable name**: socenv_av_inc1000Z_6  
**Variable description**: Average income in 1000 euros of residents in residential area (standardized: mean=0 and sd=1).
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in euros (Z standardized)  
**Variable name**: socenv_av_incZ_0  
**Variable description**: Average income in euros of residents in residential area (standardized: mean=0 and sd=1). **Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```   



### **Variable label**: Average income in euros (Z standardized)  
**Variable name**: socenv_av_incZ_1  
**Variable description**: Average income in euros of residents in residential area (standardized: mean=0 and sd=1). **Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```   



### **Variable label**: Average income in euros (Z standardized)  
**Variable name**: socenv_av_incZ_2  
**Variable description**: Average income in euros of residents in residential area (standardized: mean=0 and sd=1). **Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Average income in euros (Z standardized)  
**Variable name**: socenv_av_incZ_3  
**Variable description**: Average income in euros of residents in residential area (standardized: mean=0 and sd=1). **Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Average income in euros (Z standardized)  
**Variable name**: socenv_av_incZ_4  
**Variable description**: Average income in euros of residents in residential area (standardized: mean=0 and sd=1). **Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Average income in euros (Z standardized)  
**Variable name**: socenv_av_incZ_5  
**Variable description**: Average income in euros of residents in residential area (standardized: mean=0 and sd=1). **Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Average income in euros (Z standardized)  
**Variable name**: socenv_av_incZ_6  
**Variable description**: Average income in euros of residents in residential area (standardized: mean=0 and sd=1). **Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Average household income in euros (Z standardized)
**Variable name**: socenv_av_hhincZ_500m_0  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address (standardized: mean=0 and sd=1).    .       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   


**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Average household income in euros (Z standardized)
**Variable name**: socenv_av_hhincZ_500m_1  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address (standardized: mean=0 and sd=1).    .       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   


**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Average household income in euros (Z standardized)
**Variable name**: socenv_av_hhincZ_500m_2 
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address (standardized: mean=0 and sd=1).    .       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   


**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Average household income in euros (Z standardized)
**Variable name**: socenv_av_hhincZ_500m_3  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address (standardized: mean=0 and sd=1).    .       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   


**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Average household income in euros (Z standardized)
**Variable name**: socenv_av_hhincZ_500m_4  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address (standardized: mean=0 and sd=1).    .       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   


**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Average household income in euros (Z standardized)
**Variable name**: socenv_av_hhincZ_500m_5  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address (standardized: mean=0 and sd=1).    .       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   


**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Average household income in euros (Z standardized)
**Variable name**: socenv_av_hhincZ_500m_6  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address (standardized: mean=0 and sd=1).    .       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Average household income in euros (Z standardized)
**Variable name**: socenv_av_hhincZ_1000m_0  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address (standardized: mean=0 and sd=1).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Average household income in euros (Z standardized)
**Variable name**: socenv_av_hhincZ_1000m_1  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address (standardized: mean=0 and sd=1).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Average household income in euros (Z standardized)
**Variable name**: socenv_av_hhincZ_1000m_2  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address (standardized: mean=0 and sd=1).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Average household income in euros (Z standardized)
**Variable name**: socenv_av_hhincZ_1000m_3  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address (standardized: mean=0 and sd=1).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Average household income in euros (Z standardized)
**Variable name**: socenv_av_hhincZ_1000m_4  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address (standardized: mean=0 and sd=1).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Average household income in euros (Z standardized)
**Variable name**: socenv_av_hhincZ_1000m_5  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address (standardized: mean=0 and sd=1).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Average household income in euros (Z standardized)
**Variable name**: socenv_av_hhincZ_1000m_6  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address (standardized: mean=0 and sd=1).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Average household income in euros (Z standardized)
**Variable name**: socenv_av_hhincZ_2000m_0  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address (standardized: mean=0 and sd=1).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Average household income in euros (Z standardized)
**Variable name**: socenv_av_hhincZ_2000m_1  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address (standardized: mean=0 and sd=1).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Average household income in euros (Z standardized)
**Variable name**: socenv_av_hhincZ_2000m_2  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address (standardized: mean=0 and sd=1).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Average household income in euros (Z standardized)
**Variable name**: socenv_av_hhincZ_2000m_3  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address (standardized: mean=0 and sd=1).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Average household income in euros (Z standardized)
**Variable name**: socenv_av_hhincZ_2000m_4  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address (standardized: mean=0 and sd=1).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Average household income in euros (Z standardized)
**Variable name**: socenv_av_hhincZ_2000m_5  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address (standardized: mean=0 and sd=1).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Average household income in euros (Z standardized)
**Variable name**: socenv_av_hhincZ_2000m_6  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address (standardized: mean=0 and sd=1).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of income recipients
**Variable name**: socenv_perc_inc_recipients_0  
**Variable description**: Percentage of income recipients in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 

### **Variable label**: Percentage of income recipients
**Variable name**: socenv_perc_inc_recipients_1  
**Variable description**: Percentage of income recipients in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of income recipients
**Variable name**: socenv_perc_inc_recipients_2 
**Variable description**: Percentage of income recipients in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of income recipients
**Variable name**: socenv_perc_inc_recipients_3  
**Variable description**: Percentage of income recipients in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of income recipients
**Variable name**: socenv_perc_inc_recipients_4  
**Variable description**: Percentage of income recipients in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of income recipients
**Variable name**: socenv_perc_inc_recipients_5  
**Variable description**: Percentage of income recipients in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of income recipients
**Variable name**: socenv_perc_inc_recipients_6  
**Variable description**: Percentage of income recipients in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



# Unemployment

### **Variable label**: Percentage of unemployed residents  
**Variable name**: socenv_perc_unemployment_0  
**Variable description**: Percentage of unemployed residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of unemployed residents  
**Variable name**: socenv_perc_unemployment_1  
**Variable description**: Percentage of unemployed residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  complete
**Harmonization comment**:
For RECORD, these data are available for neighbourhoods in 2014. This variable includes the percentage of unemployed residents aged 15-64 years in the neighbourhood. This variable was calculated by: total number of unemployed residents aged 15-64 years old in the area / total number of residents aged 15-64 years old in the area * 100. This variable has been linked to cohort respondents at wave 2011 using their 5-digit postal code. References of the original data sources are listed in WP7 deliverable report.
**R script**:  
```{r, echo=TRUE} 

socenv_RECORD_1$socenv_perc_unemployment_1 <-as.numeric(RECORD_w2$UNEMPLOYMENT_RATE_2014)
 
```    




### **Variable label**: Percentage of unemployed residents  
**Variable name**: socenv_perc_unemployment_2  
**Variable description**: Percentage of unemployed residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of unemployed residents  
**Variable name**: socenv_perc_unemployment_3  
**Variable description**: Percentage of unemployed residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of unemployed residents  
**Variable name**: socenv_perc_unemployment_4  
**Variable description**: Percentage of unemployed residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of unemployed residents  
**Variable name**: socenv_perc_unemployment_5  
**Variable description**: Percentage of unemployed residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of unemployed residents  
**Variable name**: socenv_perc_unemployment_6  
**Variable description**: Percentage of unemployed residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



# Social security

### **Variable label**: Percentage of social security beneficiaries  
**Variable name**: socenv_percentage_socsecben_0  
**Variable description**: Percentage of social security beneficiaries in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of social security beneficiaries  
**Variable name**: socenv_percentage_socsecben_1  
**Variable description**: Percentage of social security beneficiaries in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of social security beneficiaries  
**Variable name**: socenv_percentage_socsecben_2  
**Variable description**: Percentage of social security beneficiaries in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of social security beneficiaries  
**Variable name**: socenv_percentage_socsecben_3  
**Variable description**: Percentage of social security beneficiaries in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of social security beneficiaries  
**Variable name**: socenv_percentage_socsecben_4  
**Variable description**: Percentage of social security beneficiaries in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of social security beneficiaries  
**Variable name**: socenv_percentage_socsecben_5  
**Variable description**: Percentage of social security beneficiaries in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of social security beneficiaries  
**Variable name**: socenv_percentage_socsecben_6  
**Variable description**: Percentage of social security beneficiaries in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of residents with disability benefit  
**Variable name**: socenv_percentage_disben_0   
**Variable description**: Percentage of residents with a disability benefit in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of residents with disability benefit  
**Variable name**: socenv_percentage_disben_1   
**Variable description**: Percentage of residents with a disability benefit in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents with disability benefit  
**Variable name**: socenv_percentage_disben_2   
**Variable description**: Percentage of residents with a disability benefit in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents with disability benefit  
**Variable name**: socenv_percentage_disben_3   
**Variable description**: Percentage of residents with a disability benefit in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents with disability benefit  
**Variable name**: socenv_percentage_disben_4   
**Variable description**: Percentage of residents with a disability benefit in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents with disability benefit  
**Variable name**: socenv_percentage_disben_5   
**Variable description**: Percentage of residents with a disability benefit in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents with disability benefit  
**Variable name**: socenv_percentage_disben_6   
**Variable description**: Percentage of residents with a disability benefit in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents with unemployment benefit  
**Variable name**: socenv_percentage_unemplben_0   
**Variable description**: Percentage of residents with a unemployment benefit in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents with unemployment benefit  
**Variable name**: socenv_percentage_unemplben_1   
**Variable description**: Percentage of residents with a unemployment benefit in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents with unemployment benefit  
**Variable name**: socenv_percentage_unemplben_2   
**Variable description**: Percentage of residents with a unemployment benefit in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents with unemployment benefit  
**Variable name**: socenv_percentage_unemplben_3   
**Variable description**: Percentage of residents with a unemployment benefit in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents with unemployment benefit  
**Variable name**: socenv_percentage_unemplben_4   
**Variable description**: Percentage of residents with a unemployment benefit in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents with unemployment benefit  
**Variable name**: socenv_percentage_unemplben_5   
**Variable description**: Percentage of residents with a unemployment benefit in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents with unemployment benefit  
**Variable name**: socenv_percentage_unemplben_6   
**Variable description**: Percentage of residents with a unemployment benefit in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



# Educational level  

### **Variable label**: Percentage of low educated residents  
**Variable name**: socenv_perc_low_education_0  
**Variable description**: Percentage of low educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of low educated residents  
**Variable name**: socenv_perc_low_education_1  
**Variable description**: Percentage of low educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of low educated residents  
**Variable name**: socenv_perc_low_education_2  
**Variable description**: Percentage of low educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of low educated residents  
**Variable name**: socenv_perc_low_education_3  
**Variable description**: Percentage of low educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of low educated residents  
**Variable name**: socenv_perc_low_education_4  
**Variable description**: Percentage of low educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of low educated residents  
**Variable name**: socenv_perc_low_education_5  
**Variable description**: Percentage of low educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of low educated residents  
**Variable name**: socenv_perc_low_education_6  
**Variable description**: Percentage of low educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of intermediate educated residents  
**Variable name**: socenv_perc_itm_education_0  
**Variable description**: Percentage of intermediate educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of intermediate educated residents  
**Variable name**: socenv_perc_itm_education_1  
**Variable description**: Percentage of intermediate educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of intermediate educated residents  
**Variable name**: socenv_perc_itm_education_2  
**Variable description**: Percentage of intermediate educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of intermediate educated residents  
**Variable name**: socenv_perc_itm_education_3  
**Variable description**: Percentage of intermediate educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of intermediate educated residents  
**Variable name**: socenv_perc_itm_education_4  
**Variable description**: Percentage of intermediate educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of intermediate educated residents  
**Variable name**: socenv_perc_itm_education_5  
**Variable description**: Percentage of intermediate educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of intermediate educated residents  
**Variable name**: socenv_perc_itm_education_6  
**Variable description**: Percentage of intermediate educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of high educated residents  
**Variable name**: socenv_perc_high_education_0  
**Variable description**: Percentage of high educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of high educated residents  
**Variable name**: socenv_perc_high_education_1  
**Variable description**: Percentage of high educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of high educated residents  
**Variable name**: socenv_perc_high_education_2  
**Variable description**: Percentage of high educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of high educated residents  
**Variable name**: socenv_perc_high_education_3  
**Variable description**: Percentage of high educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of high educated residents  
**Variable name**: socenv_perc_high_education_4  
**Variable description**: Percentage of high educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of high educated residents  
**Variable name**: socenv_perc_high_education_5  
**Variable description**: Percentage of high educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of high educated residents  
**Variable name**: socenv_perc_high_education_6  
**Variable description**: Percentage of high educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



# Immigrants and ethnic minority groups

### **Variable label**: Percentage of immigrants  
**Variable name**: socenv_perc_immigrants_0
**Variable description**: Percentage of immigrants in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants  
**Variable name**: socenv_perc_immigrants_1
**Variable description**: Percentage of immigrants in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants  
**Variable name**: socenv_perc_immigrants_2
**Variable description**: Percentage of immigrants in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants  
**Variable name**: socenv_perc_immigrants_3
**Variable description**: Percentage of immigrants in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants  
**Variable name**: socenv_perc_immigrants_4
**Variable description**: Percentage of immigrants in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants  
**Variable name**: socenv_perc_immigrants_5
**Variable description**: Percentage of immigrants in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants  
**Variable name**: socenv_perc_immigrants_6
**Variable description**: Percentage of immigrants in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of western immigrants  
**Variable name**: socenv_perc_west_imgs_0  
**Variable description**: Percentage of western immigrants in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of western immigrants  
**Variable name**: socenv_perc_west_imgs_1  
**Variable description**: Percentage of western immigrants in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of western immigrants  
**Variable name**: socenv_perc_west_imgs_2  
**Variable description**: Percentage of western immigrants in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of western immigrants  
**Variable name**: socenv_perc_west_imgs_3  
**Variable description**: Percentage of western immigrants in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of western immigrants  
**Variable name**: socenv_perc_west_imgs_4  
**Variable description**: Percentage of western immigrants in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of western immigrants  
**Variable name**: socenv_perc_west_imgs_5  
**Variable description**: Percentage of western immigrants in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of western immigrants  
**Variable name**: socenv_perc_west_imgs_6  
**Variable description**: Percentage of western immigrants in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of non-western immigrants
**Variable name**: socenv_perc_nonwest_imgs_0  
**Variable description**: Percentage of non-western immigrants in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of non-western immigrants
**Variable name**: socenv_perc_nonwest_imgs_1  
**Variable description**: Percentage of non-western immigrants in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of non-western immigrants
**Variable name**: socenv_perc_nonwest_imgs_2  
**Variable description**: Percentage of non-western immigrants in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of non-western immigrants
**Variable name**: socenv_perc_nonwest_imgs_3  
**Variable description**: Percentage of non-western immigrants in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of non-western immigrants
**Variable name**: socenv_perc_nonwest_imgs_4  
**Variable description**: Percentage of non-western immigrants in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of non-western immigrants
**Variable name**: socenv_perc_nonwest_imgs_5  
**Variable description**: Percentage of non-western immigrants in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of non-western immigrants
**Variable name**: socenv_perc_nonwest_imgs_6  
**Variable description**: Percentage of non-western immigrants in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of Moroccan origin  
**Variable name**: socenv_perc_moroccan_0  
**Variable description**: Percentage of immigrants of Moroccan origin in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of Moroccan origin  
**Variable name**: socenv_perc_moroccan_1  
**Variable description**: Percentage of immigrants of Moroccan origin in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of Moroccan origin  
**Variable name**: socenv_perc_moroccan_2  
**Variable description**: Percentage of immigrants of Moroccan origin in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of Moroccan origin  
**Variable name**: socenv_perc_moroccan_3  
**Variable description**: Percentage of immigrants of Moroccan origin in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of Moroccan origin  
**Variable name**: socenv_perc_moroccan_4  
**Variable description**: Percentage of immigrants of Moroccan origin in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of Moroccan origin  
**Variable name**: socenv_perc_moroccan_5  
**Variable description**: Percentage of immigrants of Moroccan origin in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of Moroccan origin  
**Variable name**: socenv_perc_moroccan_6  
**Variable description**: Percentage of immigrants of Moroccan origin in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of Antillian and Aruban origin 
**Variable name**: socenv_perc_antaru_0  
**Variable description**: Percentage of immigrants of Antillian and Aruban origin in residential area.    **Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of Antillian and Aruban origin 
**Variable name**: socenv_perc_antaru_1  
**Variable description**: Percentage of immigrants of Antillian and Aruban origin in residential area.    **Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of Antillian and Aruban origin 
**Variable name**: socenv_perc_antaru_2  
**Variable description**: Percentage of immigrants of Antillian and Aruban origin in residential area.    **Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of Antillian and Aruban origin 
**Variable name**: socenv_perc_antaru_3  
**Variable description**: Percentage of immigrants of Antillian and Aruban origin in residential area.    **Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of Antillian and Aruban origin 
**Variable name**: socenv_perc_antaru_4  
**Variable description**: Percentage of immigrants of Antillian and Aruban origin in residential area.    **Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of Antillian and Aruban origin 
**Variable name**: socenv_perc_antaru_5  
**Variable description**: Percentage of immigrants of Antillian and Aruban origin in residential area.    **Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of Antillian and Aruban origin 
**Variable name**: socenv_perc_antaru_6  
**Variable description**: Percentage of immigrants of Antillian and Aruban origin in residential area.    **Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of Surinamese origin  
**Variable name**: socenv_perc_surinamese_0  
**Variable description**: Percentage of immigrants of Surinamese origin in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of Surinamese origin  
**Variable name**: socenv_perc_surinamese_1  
**Variable description**: Percentage of immigrants of Surinamese origin in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of Surinamese origin  
**Variable name**: socenv_perc_surinamese_2  
**Variable description**: Percentage of immigrants of Surinamese origin in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of Surinamese origin  
**Variable name**: socenv_perc_surinamese_3  
**Variable description**: Percentage of immigrants of Surinamese origin in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of Surinamese origin  
**Variable name**: socenv_perc_surinamese_4  
**Variable description**: Percentage of immigrants of Surinamese origin in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of Surinamese origin  
**Variable name**: socenv_perc_surinamese_5  
**Variable description**: Percentage of immigrants of Surinamese origin in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of Surinamese origin  
**Variable name**: socenv_perc_surinamese_6  
**Variable description**: Percentage of immigrants of Surinamese origin in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of Turkish origin  
**Variable name**: socenv_perc_turkey_0  
**Variable description**: Percentage of immigrants of Turkish origin in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of Turkish origin  
**Variable name**: socenv_perc_turkey_1  
**Variable description**: Percentage of immigrants of Turkish origin in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of Turkish origin  
**Variable name**: socenv_perc_turkey_2  
**Variable description**: Percentage of immigrants of Turkish origin in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of Turkish origin  
**Variable name**: socenv_perc_turkey_3  
**Variable description**: Percentage of immigrants of Turkish origin in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of Turkish origin  
**Variable name**: socenv_perc_turkey_4  
**Variable description**: Percentage of immigrants of Turkish origin in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of Turkish origin  
**Variable name**: socenv_perc_turkey_5  
**Variable description**: Percentage of immigrants of Turkish origin in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of Turkish origin  
**Variable name**: socenv_perc_turkey_6  
**Variable description**: Percentage of immigrants of Turkish origin in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of other origin  
**Variable name**: socenv_perc_other_0  
**Variable description**: Percentage of immigrants of other origin in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of other origin  
**Variable name**: socenv_perc_other_1  
**Variable description**: Percentage of immigrants of other origin in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of other origin  
**Variable name**: socenv_perc_other_2  
**Variable description**: Percentage of immigrants of other origin in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of other origin  
**Variable name**: socenv_perc_other_3  
**Variable description**: Percentage of immigrants of other origin in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of other origin  
**Variable name**: socenv_perc_other_4  
**Variable description**: Percentage of immigrants of other origin in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of other origin  
**Variable name**: socenv_perc_other_5  
**Variable description**: Percentage of immigrants of other origin in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of immigrants of other origin  
**Variable name**: socenv_perc_other_6  
**Variable description**: Percentage of immigrants of other origin in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of foreigners 
**Variable name**: socenv_perc_foreigners_0  
**Variable description**: Percentage of foreigners in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of foreigners 
**Variable name**: socenv_perc_foreigners_1  
**Variable description**: Percentage of foreigners in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of foreigners 
**Variable name**: socenv_perc_foreigners_2  
**Variable description**: Percentage of foreigners in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of foreigners 
**Variable name**: socenv_perc_foreigners_3  
**Variable description**: Percentage of foreigners in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of foreigners 
**Variable name**: socenv_perc_foreigners_4  
**Variable description**: Percentage of foreigners in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of foreigners 
**Variable name**: socenv_perc_foreigners_5  
**Variable description**: Percentage of foreigners in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of foreigners 
**Variable name**: socenv_perc_foreigners_6  
**Variable description**: Percentage of foreigners in residential area.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



# Crime  

### **Variable label**: Number of criminal offenses per 1000 residents  
**Variable name**: socenv_crimoff_0    
**Variable description**: Number of criminal offenses per 1000 residents in residential area.       
**Variable type**: integer    
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of criminal offenses per 1000 residents  
**Variable name**: socenv_crimoff_1    
**Variable description**: Number of criminal offenses per 1000 residents in residential area.       
**Variable type**: integer    
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of criminal offenses per 1000 residents  
**Variable name**: socenv_crimoff_2    
**Variable description**: Number of criminal offenses per 1000 residents in residential area.       
**Variable type**: integer    
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of criminal offenses per 1000 residents  
**Variable name**: socenv_crimoff_3    
**Variable description**: Number of criminal offenses per 1000 residents in residential area.       
**Variable type**: integer    
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of criminal offenses per 1000 residents  
**Variable name**: socenv_crimoff_4    
**Variable description**: Number of criminal offenses per 1000 residents in residential area.       
**Variable type**: integer    
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of criminal offenses per 1000 residents  
**Variable name**: socenv_crimoff_5    
**Variable description**: Number of criminal offenses per 1000 residents in residential area.       
**Variable type**: integer    
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of criminal offenses per 1000 residents  
**Variable name**: socenv_crimoff_6    
**Variable description**: Number of criminal offenses per 1000 residents in residential area.       
**Variable type**: integer    
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of violent crimes per 1000 residents  
**Variable name**: socenv_violentcrim_0    
**Variable description**: Number of violent crimes per 1000 residents in residential area.       
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of violent crimes per 1000 residents  
**Variable name**: socenv_violentcrim_1    
**Variable description**: Number of violent crimes per 1000 residents in residential area.       
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of violent crimes per 1000 residents  
**Variable name**: socenv_violentcrim_2    
**Variable description**: Number of violent crimes per 1000 residents in residential area.       
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of violent crimes per 1000 residents  
**Variable name**: socenv_violentcrim_3    
**Variable description**: Number of violent crimes per 1000 residents in residential area.       
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of violent crimes per 1000 residents  
**Variable name**: socenv_violentcrim_4    
**Variable description**: Number of violent crimes per 1000 residents in residential area.       
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of violent crimes per 1000 residents  
**Variable name**: socenv_violentcrim_5    
**Variable description**: Number of violent crimes per 1000 residents in residential area.       
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of violent crimes per 1000 residents  
**Variable name**: socenv_violentcrim_6    
**Variable description**: Number of violent crimes per 1000 residents in residential area.       
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of thefts per 1000 residents 
**Variable name**: socenv_thefts_0    
**Variable description**: Number of thefts per 1000 residents in residential area.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of thefts per 1000 residents 
**Variable name**: socenv_thefts_1    
**Variable description**: Number of thefts per 1000 residents in residential area.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of thefts per 1000 residents 
**Variable name**: socenv_thefts_2    
**Variable description**: Number of thefts per 1000 residents in residential area.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of thefts per 1000 residents 
**Variable name**: socenv_thefts_3    
**Variable description**: Number of thefts per 1000 residents in residential area.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of thefts per 1000 residents 
**Variable name**: socenv_thefts_4    
**Variable description**: Number of thefts per 1000 residents in residential area.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of thefts per 1000 residents 
**Variable name**: socenv_thefts_5    
**Variable description**: Number of thefts per 1000 residents in residential area.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of thefts per 1000 residents 
**Variable name**: socenv_thefts_6    
**Variable description**: Number of thefts per 1000 residents in residential area.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of vandalism and public disorder per 1000 residents  
**Variable name**: socenv_vandalism_po_0   
**Variable description**: Number of vandalism and public disorder per 1000 residents in residential area.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of vandalism and public disorder per 1000 residents  
**Variable name**: socenv_vandalism_po_1   
**Variable description**: Number of vandalism and public disorder per 1000 residents in residential area.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of vandalism and public disorder per 1000 residents  
**Variable name**: socenv_vandalism_po_2   
**Variable description**: Number of vandalism and public disorder per 1000 residents in residential area.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of vandalism and public disorder per 1000 residents  
**Variable name**: socenv_vandalism_po_3   
**Variable description**: Number of vandalism and public disorder per 1000 residents in residential area.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of vandalism and public disorder per 1000 residents  
**Variable name**: socenv_vandalism_po_4   
**Variable description**: Number of vandalism and public disorder per 1000 residents in residential area.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of vandalism and public disorder per 1000 residents  
**Variable name**: socenv_vandalism_po_5   
**Variable description**: Number of vandalism and public disorder per 1000 residents in residential area.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of vandalism and public disorder per 1000 residents  
**Variable name**: socenv_vandalism_po_6   
**Variable description**: Number of vandalism and public disorder per 1000 residents in residential area.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of violent crimes and sexual offenses per 1000 residents   
**Variable name**: socenv_violentcrim_sexoff_0    
**Variable description**: Number of violent crimes and sexual offenses per 1000 residents in residential area.         
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of violent crimes and sexual offenses per 1000 residents   
**Variable name**: socenv_violentcrim_sexoff_1    
**Variable description**: Number of violent crimes and sexual offenses per 1000 residents in residential area.         
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of violent crimes and sexual offenses per 1000 residents   
**Variable name**: socenv_violentcrim_sexoff_2    
**Variable description**: Number of violent crimes and sexual offenses per 1000 residents in residential area.         
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of violent crimes and sexual offenses per 1000 residents   
**Variable name**: socenv_violentcrim_sexoff_3    
**Variable description**: Number of violent crimes and sexual offenses per 1000 residents in residential area.         
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of violent crimes and sexual offenses per 1000 residents   
**Variable name**: socenv_violentcrim_sexoff_4    
**Variable description**: Number of violent crimes and sexual offenses per 1000 residents in residential area.         
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of violent crimes and sexual offenses per 1000 residents   
**Variable name**: socenv_violentcrim_sexoff_5    
**Variable description**: Number of violent crimes and sexual offenses per 1000 residents in residential area.         
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of violent crimes and sexual offenses per 1000 residents   
**Variable name**: socenv_violentcrim_sexoff_6    
**Variable description**: Number of violent crimes and sexual offenses per 1000 residents in residential area.         
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of vandalism per 1000 residents   
**Variable name**: socenv_vandalism_0    
**Variable description**: Number of vandalism per 1000 residents in residential area.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of vandalism per 1000 residents   
**Variable name**: socenv_vandalism_1    
**Variable description**: Number of vandalism per 1000 residents in residential area.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of vandalism per 1000 residents   
**Variable name**: socenv_vandalism_2    
**Variable description**: Number of vandalism per 1000 residents in residential area.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of vandalism per 1000 residents   
**Variable name**: socenv_vandalism_3    
**Variable description**: Number of vandalism per 1000 residents in residential area.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of vandalism per 1000 residents   
**Variable name**: socenv_vandalism_4    
**Variable description**: Number of vandalism per 1000 residents in residential area.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of vandalism per 1000 residents   
**Variable name**: socenv_vandalism_5    
**Variable description**: Number of vandalism per 1000 residents in residential area.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of vandalism per 1000 residents   
**Variable name**: socenv_vandalism_6    
**Variable description**: Number of vandalism per 1000 residents in residential area.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of public disorder per 1000 residents    
**Variable name**: socenv_po_0    
**Variable description**: Number of public disorder per 1000 residents in residential area.       
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of public disorder per 1000 residents    
**Variable name**: socenv_po_1    
**Variable description**: Number of public disorder per 1000 residents in residential area.       
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of public disorder per 1000 residents    
**Variable name**: socenv_po_2    
**Variable description**: Number of public disorder per 1000 residents in residential area.       
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of public disorder per 1000 residents    
**Variable name**: socenv_po_3    
**Variable description**: Number of public disorder per 1000 residents in residential area.       
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of public disorder per 1000 residents    
**Variable name**: socenv_po_4    
**Variable description**: Number of public disorder per 1000 residents in residential area.       
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of public disorder per 1000 residents    
**Variable name**: socenv_po_5    
**Variable description**: Number of public disorder per 1000 residents in residential area.       
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of public disorder per 1000 residents    
**Variable name**: socenv_po_6    
**Variable description**: Number of public disorder per 1000 residents in residential area.       
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



#Area indicators

### **Variable label**: Area indicator: city 
**Variable name**: socenv_city_0    
**Variable description**: City indicator.    
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete
**Harmonization comment**: For RECORD, the indicator variables start with 33.  
**R script**:  
```{r, echo=TRUE}  
socenv_RECORD_0$socenv_city_0 <-as.integer(RECORD_w1_1$city) 

```  



### **Variable label**: Area indicator: city 
**Variable name**: socenv_city_1    
**Variable description**: City indicator.    
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: city 
**Variable name**: socenv_city_2    
**Variable description**: City indicator.    
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: city 
**Variable name**: socenv_city_3    
**Variable description**: City indicator.    
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: city 
**Variable name**: socenv_city_4    
**Variable description**: City indicator.    
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: city 
**Variable name**: socenv_city_5    
**Variable description**: City indicator.    
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: city 
**Variable name**: socenv_city_6    
**Variable description**: City indicator.    
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: municipality
**Variable name**: socenv_municipality_0    
**Variable description**: Municipality indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: municipality
**Variable name**: socenv_municipality_1    
**Variable description**: Municipality indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: municipality
**Variable name**: socenv_municipality_2    
**Variable description**: Municipality indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: municipality
**Variable name**: socenv_municipality_3    
**Variable description**: Municipality indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: municipality
**Variable name**: socenv_municipality_4     
**Variable description**: Municipality indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: municipality
**Variable name**: socenv_municipality_5    
**Variable description**: Municipality indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: municipality
**Variable name**: socenv_municipality_6    
**Variable description**: Municipality indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: neighbourhood
**Variable name**: socenv_neighbourhood_0    
**Variable description**: Neighbourhood indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete
**Harmonization comment**: For RECORD, the indicator variables start with 33.  
**R script**:  
```{r, echo=TRUE}  

socenv_RECORD_0$socenv_neighbourhood_0 <-as.integer(RECORD_w1_1$neighbourhood) 

``` 



### **Variable label**: Area indicator: neighbourhood
**Variable name**: socenv_neighbourhood_1    
**Variable description**: Neighbourhood indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete
**Harmonization comment**: For RECORD, the indicator variables start with 33.  
**R script**:  
```{r, echo=TRUE}  

socenv_RECORD_1$socenv_neighbourhood_1 <-as.integer(RECORD_w2$neighbourhood) 

``` 




### **Variable label**: Area indicator: neighbourhood
**Variable name**: socenv_neighbourhood_2    
**Variable description**: Neighbourhood indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: neighbourhood
**Variable name**: socenv_neighbourhood_3    
**Variable description**: Neighbourhood indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: neighbourhood
**Variable name**: socenv_neighbourhood_4    
**Variable description**: Neighbourhood indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: neighbourhood
**Variable name**: socenv_neighbourhood_5    
**Variable description**: Neighbourhood indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: neighbourhood
**Variable name**: socenv_neighbourhood_6    
**Variable description**: Neighbourhood indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 4-digit postal code
**Variable name**: socenv_pc4_0    
**Variable description**:  4-digit postal code (PC4) indicator. 
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 4-digit postal code
**Variable name**: socenv_pc4_1    
**Variable description**:  4-digit postal code (PC4) indicator. 
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 4-digit postal code
**Variable name**: socenv_pc4_2    
**Variable description**:  4-digit postal code (PC4) indicator. 
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 4-digit postal code
**Variable name**: socenv_pc4_3    
**Variable description**:  4-digit postal code (PC4) indicator. 
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 4-digit postal code
**Variable name**: socenv_pc4_4    
**Variable description**:  4-digit postal code (PC4) indicator. 
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 4-digit postal code
**Variable name**: socenv_pc4_5    
**Variable description**:  4-digit postal code (PC4) indicator. 
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 4-digit postal code
**Variable name**: socenv_pc4_6    
**Variable description**:  4-digit postal code (PC4) indicator. 
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 6-digit postal code
**Variable name**: socenv_pc6_0    
**Variable description**:  6-digit postal code (PC6) indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 6-digit postal code
**Variable name**: socenv_pc6_1    
**Variable description**:  6-digit postal code (PC6) indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 6-digit postal code
**Variable name**: socenv_pc6_2    
**Variable description**:  6-digit postal code (PC6) indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 6-digit postal code
**Variable name**: socenv_pc6_3    
**Variable description**:  6-digit postal code (PC6) indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 6-digit postal code
**Variable name**: socenv_pc6_4    
**Variable description**:  6-digit postal code (PC6) indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 6-digit postal code
**Variable name**: socenv_pc6_5    
**Variable description**:  6-digit postal code (PC6) indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 6-digit postal code
**Variable name**: socenv_pc6_6    
**Variable description**:  6-digit postal code (PC6) indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 5-digit postal code
**Variable name**: socenv_pc5_0    
**Variable description**:  5-digit postal code (PC5) indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete
**Harmonization comment**:  
For RECORD, the indicator variables start with 33.
**R script**:  
```{r, echo=TRUE}  

socenv_RECORD_0$socenv_pc5_0 <-as.integer(RECORD_w1_1$pc5)

```



### **Variable label**: Area indicator: 5-digit postal code
**Variable name**: socenv_pc5_1    
**Variable description**:  5-digit postal code (PC5) indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete
**Harmonization comment**:  
For RECORD, the indicator variables start with 33.
**R script**:  
```{r, echo=TRUE}  
socenv_RECORD_1$socenv_pc5_1 <-as.integer(RECORD_w2$pc5) 

```



### **Variable label**: Area indicator: 5-digit postal code
**Variable name**: socenv_pc5_2    
**Variable description**:  5-digit postal code (PC5) indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 5-digit postal code
**Variable name**: socenv_pc5_3    
**Variable description**:  5-digit postal code (PC5) indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 5-digit postal code
**Variable name**: socenv_pc5_4    
**Variable description**:  5-digit postal code (PC5) indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 5-digit postal code
**Variable name**: socenv_pc5_5    
**Variable description**:  5-digit postal code (PC5) indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 5-digit postal code
**Variable name**: socenv_pc5_6    
**Variable description**:  5-digit postal code (PC5) indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```
