---
title: "Social environmental (i.e. geospatial) HUNT"
output: html_document
---
# Connecting with Opal data server
## Login to server and assign study data
```{r, echo=FALSE}
#Load Opal R library
library(opal)
library(dplyr)
# Create an opal object with the login information
erasmus_opal <- opal.login()
#Login to Opal server and assign the content of the HUNT table(s) to your RStudio environment
# HUNT1
opal.assign.table.tibble(erasmus_opal, 'HUNT1', 'HUNT.HUNT1',variables = list())
HUNT1 <- opal.execute(erasmus_opal,'HUNT1')
# HUNT2
opal.assign.table.tibble(erasmus_opal, 'HUNT2', 'HUNT.HUNT2', variables=list('')) 
HUNT2<- opal.execute(erasmus_opal,'HUNT2')

# HUNT3
opal.assign.table.tibble(erasmus_opal, 'HUNT3_socioenviro_april2019', 'HUNT.HUNT3_socioenviro_april2019',variables = list("URBANIZATON_GRADE_2006","PROPORTION_MEN_2006","PROPORTION_WOMEN_2006","PROPORTION_65_OLDER_2006","PROPORTION_MARIED_2006","PROPORTION_DIVORCED_2006","PROPORTION_WIDOWED_2006","AVERAGE_HOUSEHOLD_SIZE_2006","AVERAGE_INCOME_2006","UNEMPLOYMENT_RATE_2006","PROPORTION_SOCSECBEN_2006","PROPORTION_UNOCCUPIED_DWELLINGS_2011","PROPORTION_LOW_EDUCATION_2011","PROPORTION_INTERMEDIATE_EDUCATION_2011","PROPORTION_HIGH_EDUCATION_2011","municipality"))
HUNT3 <- opal.execute(erasmus_opal,'HUNT3_socioenviro_april2019')

```
## Assign participant id as first column of your harmonized dataframes
```{r, echo=FALSE}
socenv_HUNT_2 <- data.frame(id = HUNT3$id)
```
## When you are done with your work, logout of Opal server
```{r, echo=FALSE}
opal.logout(erasmus_opal) 
```


---
# Table of Contents
1. [Urbanization grade](#Urbanzation grade)  
2. [Demographics](#Demographics)  
3. [Housing](#Housing)  
4. [Income](#Income)  
5. [Unemployment](#Unemployment)  
6. [Social security](#Social security)  
7. [Educational level](#Educational level)  
8. [Crime](#Crime)
9. [Area indicators] (#Area indicators)
  

# Urbanization grade

### **Variable label**: Urbanization grade  
**Variable name**: socenv_urbanization_grade_0    
**Variable description**: Population density of the residential area (number of residents per km2). 
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Urbanization grade  
**Variable name**: socenv_urbanization_grade_1   
**Variable description**: Population density of the residential area (number of residents per km2). 
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Urbanization grade  
**Variable name**: socenv_urbanization_grade_2    
**Variable description**: Population density of the residential area (number of residents per km2). 
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete  
**Harmonization comment**: 
For HUNT, urbanization grade data are available for municipalities in 2006. These data were already available in the original data source. This variable has been linked to cohort respondents in 2006 using their municipality code. References to the original data sources are listed in the WP7 deliverable report."

**R script**:  
```{r, echo=TRUE}  
socenv_HUNT_2$socenv_urbanization_grade_2 <-as.integer(round(HUNT3$URBANIZATON_GRADE_2006))
```  



### **Variable label**: Urbanization grade  
**Variable name**: socenv_urbanization_grade_3    
**Variable description**: Population density of the residential area (number of residents per km2). 
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Urbanization grade  
**Variable name**: socenv_urbanization_grade_4    
**Variable description**: Population density of the residential area (number of residents per km2). 
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Urbanization grade  
**Variable name**: socenv_urbanization_grade_5    
**Variable description**: Population density of the residential area (number of residents per km2). 
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Urbanization grade  
**Variable name**: socenv_urbanization_grade_6    
**Variable description**: Population density of the residential area (number of residents per km2). 
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



# Demographics

### **Variable label**: Percentage of men 
**Variable name**: socenv_percentage_men_0    
**Variable description**: Percentage of men in the residential area.  
**Variable type**: decimal
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Percentage of men 
**Variable name**: socenv_percentage_men_1    
**Variable description**: Percentage of men in the residential area.  
**Variable type**: decimal
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Percentage of men 
**Variable name**: socenv_percentage_men_2    
**Variable description**: Percentage of men in the residential area.  
**Variable type**: decimal
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete 
**Harmonization comment**:
For HUNT, these data are available for municipalities in 2006. This variable was calculated by: total number of men in area / total number of residents in area * 100. This variable has been linked to cohort respondents in 2006 using their municipality code. References to the original data sources are listed in the WP7 deliverable report.
**R script**:  
```{r, echo=TRUE}  
socenv_HUNT_2$socenv_percentage_men_2<-as.numeric(HUNT3$PROPORTION_MEN_2006)

```    
 



### **Variable label**: Percentage of men 
**Variable name**: socenv_percentage_men_3    
**Variable description**: Percentage of men in the residential area.  
**Variable type**: decimal
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Percentage of men 
**Variable name**: socenv_percentage_men_4    
**Variable description**: Percentage of men in the residential area.  
**Variable type**: decimal
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Percentage of men 
**Variable name**: socenv_percentage_men_5    
**Variable description**: Percentage of men in the residential area.  
**Variable type**: decimal
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Percentage of men 
**Variable name**: socenv_percentage_men_6    
**Variable description**: Percentage of men in the residential area.  
**Variable type**: decimal
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Percentage of women  
**Variable name**: socenv_percentage_women_0    
**Variable description**: Percentage of women in the residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  


### **Variable label**: Percentage of women  
**Variable name**: socenv_percentage_women_1   
**Variable description**: Percentage of women in the residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  



### **Variable label**: Percentage of women  
**Variable name**: socenv_percentage_women_2   
**Variable description**: Percentage of women in the residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete 
**Harmonization comment**:
For HUNT, these data are available for municipalities in 2006. This variable was calculated by: total number of women in area / total number of residents in area * 100. This variable has been linked to cohort respondents in 2006 using their municipality code. References to the original data sources are listed in the WP7 deliverable report.
**R script**:  
```{r, echo=TRUE}  
socenv_HUNT_2$socenv_percentage_women_2<-as.numeric(HUNT3$PROPORTION_WOMEN_2006) 

```  



### **Variable label**: Percentage of women  
**Variable name**: socenv_percentage_women_3   
**Variable description**: Percentage of women in the residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of women  
**Variable name**: socenv_percentage_women_4   
**Variable description**: Percentage of women in the residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of women  
**Variable name**: socenv_percentage_women_5   
**Variable description**: Percentage of women in the residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of women  
**Variable name**: socenv_percentage_women_6   
**Variable description**: Percentage of women in the residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents aged 65 or older   
**Variable name**: socenv_percentage_65_older_0   
**Variable description**: Percentage of residents aged 65 or older in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents aged 65 or older   
**Variable name**: socenv_percentage_65_older_1   
**Variable description**: Percentage of residents aged 65 or older in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents aged 65 or older   
**Variable name**: socenv_percentage_65_older_2   
**Variable description**: Percentage of residents aged 65 or older in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete 
**Harmonization comment**: 
For HUNT, these data are available for municipalities in 2006. This variable was calculated by: summing age groups ≥ 65 years in the area / total number of residents in area * 100. This variable has been linked to cohort respondents in 2006 using their municipality code. References to the original data sources are listed in the WP7 deliverable report.
**R script**:  
```{r, echo=TRUE}  
socenv_HUNT_2$socenv_percentage_65_older_2<-as.numeric(HUNT3$PROPORTION_65_OLDER_2006) 

```    



### **Variable label**: Percentage of residents aged 65 or older   
**Variable name**: socenv_percentage_65_older_3   
**Variable description**: Percentage of residents aged 65 or older in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents aged 65 or older   
**Variable name**: socenv_percentage_65_older_4   
**Variable description**: Percentage of residents aged 65 or older in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents aged 65 or older   
**Variable name**: socenv_percentage_65_older_5   
**Variable description**: Percentage of residents aged 65 or older in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents aged 65 or older   
**Variable name**: socenv_percentage_65_older_6   
**Variable description**: Percentage of residents aged 65 or older in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of unmarried residents  
**Variable name**: socenv_percentage_unmarried_0   
**Variable description**: Percentage of unmarried residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of unmarried residents  
**Variable name**: socenv_percentage_unmarried_1   
**Variable description**: Percentage of unmarried residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of unmarried residents  
**Variable name**: socenv_percentage_unmarried_2   
**Variable description**: Percentage of unmarried residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of unmarried residents  
**Variable name**: socenv_percentage_unmarried_3   
**Variable description**: Percentage of unmarried residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of unmarried residents  
**Variable name**: socenv_percentage_unmarried_4   
**Variable description**: Percentage of unmarried residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of unmarried residents  
**Variable name**: socenv_percentage_unmarried_5   
**Variable description**: Percentage of unmarried residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of unmarried residents  
**Variable name**: socenv_percentage_unmarried_6   
**Variable description**: Percentage of unmarried residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of married residents  
**Variable name**: socenv_percentage_married_0   
**Variable description**: Percentage of married residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of married residents  
**Variable name**: socenv_percentage_married_1    
**Variable description**: Percentage of married residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of married residents  
**Variable name**: socenv_percentage_married_2   
**Variable description**: Percentage of married residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete 
**Harmonization comment**: 
For HUNT, these data are available for municipalties in 2006. This variable was calculated by: number of married residents in the area / total number of residents in area * 100. This variable has been linked to cohort respondents in 2006 using their municipality code. References to the original data sources are listed in the WP7 deliverable report.
**R script**:  
```{r, echo=TRUE}  
socenv_HUNT_2$socenv_percentage_married_2<-as.numeric(HUNT3$PROPORTION_MARIED_2006) 
```    




### **Variable label**: Percentage of married residents  
**Variable name**: socenv_percentage_married_3   
**Variable description**: Percentage of married residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of married residents  
**Variable name**: socenv_percentage_married_4   
**Variable description**: Percentage of married residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of married residents  
**Variable name**: socenv_percentage_married_5   
**Variable description**: Percentage of married residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of married residents  
**Variable name**: socenv_percentage_married_6   
**Variable description**: Percentage of married residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of divorced residents   
**Variable name**: socenv_percentage_divorced_0   
**Variable description**: Percentage of divorced residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of divorced residents   
**Variable name**: socenv_percentage_divorced_1   
**Variable description**: Percentage of divorced residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of divorced residents   
**Variable name**: socenv_percentage_divorced_2   
**Variable description**: Percentage of divorced residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete   
**Harmonization comment**: 
For HUNT, these data are available for municipalties in 2006. This variable was calculated by: number of divorced residents in the area / total number of residents in area * 100. This variable has been linked to cohort respondents in 2006 using their municipality code. References to the original data sources are listed in the WP7 deliverable report.
**R script**:  
```{r, echo=TRUE}  
socenv_HUNT_2$socenv_percentage_divorced_2<-as.numeric(HUNT3$PROPORTION_DIVORCED_2006) 
```    




### **Variable label**: Percentage of divorced residents   
**Variable name**: socenv_percentage_divorced_3   
**Variable description**: Percentage of divorced residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of divorced residents   
**Variable name**: socenv_percentage_divorced_4   
**Variable description**: Percentage of divorced residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of divorced residents   
**Variable name**: socenv_percentage_divorced_5   
**Variable description**: Percentage of divorced residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of divorced residents   
**Variable name**: socenv_percentage_divorced_6   
**Variable description**: Percentage of divorced residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of widowed residents   
**Variable name**: socenv_percentage_widowed_0   
**Variable description**: Percentage of widowed residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of widowed residents   
**Variable name**: socenv_percentage_widowed_1   
**Variable description**: Percentage of widowed residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of widowed residents   
**Variable name**: socenv_percentage_widowed_2   
**Variable description**: Percentage of widowed residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete  
**Harmonization comment**: 
For HUNT, these data are available for municipalties in 2006. This variable was calculated by: number of widowed residents in the area / total number of residents in area * 100. This variable has been linked to cohort respondents in 2006 using their municipality code. References to the original data sources are listed in the WP7 deliverable report.
**R script**:  
```{r, echo=TRUE}  
socenv_HUNT_2$socenv_percentage_widowed_2<-as.numeric(HUNT3$PROPORTION_WIDOWED_2006) 
```




### **Variable label**: Percentage of widowed residents   
**Variable name**: socenv_percentage_widowed_3   
**Variable description**: Percentage of widowed residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of widowed residents   
**Variable name**: socenv_percentage_widowed_4   
**Variable description**: Percentage of widowed residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of widowed residents   
**Variable name**: socenv_percentage_widowed_5   
**Variable description**: Percentage of widowed residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of widowed residents   
**Variable name**: socenv_percentage_widowed_6   
**Variable description**: Percentage of widowed residents in residential area.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household size  
**Variable name**: socenv_average_hh_size_0
**Variable description**: Average household size in residential area.  
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household size  
**Variable name**: socenv_average_hh_size_1
**Variable description**: Average household size in residential area.  
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household size  
**Variable name**: socenv_average_hh_size_2
**Variable description**: Average household size in residential area.  
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete 
**Harmonization comment**: 
For HUNT, these data are available for municipalties in 2006. For harmonization purposes, this variable has been made integer and has been rounded. This variable has been linked to cohort respondents in 2006 using their municipality code. References to the original data sources are listed in the WP7 deliverable report. 
**R script**:  
```{r, echo=TRUE}  
socenv_HUNT_2$socenv_average_hh_size_2<-as.integer(round(as.numeric(HUNT3$AVERAGE_HOUSEHOLD_SIZE_2006))) 
```    



### **Variable label**: Average household size  
**Variable name**: socenv_average_hh_size_3
**Variable description**: Average household size in residential area.  
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household size  
**Variable name**: socenv_average_hh_size_4
**Variable description**: Average household size in residential area.  
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household size  
**Variable name**: socenv_average_hh_size_5
**Variable description**: Average household size in residential area.  
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household size  
**Variable name**: socenv_average_hh_size_6
**Variable description**: Average household size in residential area.  
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



# Housing

### **Variable label**: Average value of dwellings in 1000 euros    
**Variable name**: socenv_avv_dwellings_0 
**Variable description**: Average value of dwellings in 1000 euros in residential area.    
**Variable type**: integer   
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average value of dwellings in 1000 euros    
**Variable name**: socenv_avv_dwellings_1 
**Variable description**: Average value of dwellings in 1000 euros in residential area.    
**Variable type**: integer   
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average value of dwellings in 1000 euros    
**Variable name**: socenv_avv_dwellings_2 
**Variable description**: Average value of dwellings in 1000 euros in residential area.    
**Variable type**: integer   
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average value of dwellings in 1000 euros    
**Variable name**: socenv_avv_dwellings_3 
**Variable description**: Average value of dwellings in 1000 euros in residential area.    
**Variable type**: integer   
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average value of dwellings in 1000 euros    
**Variable name**: socenv_avv_dwellings_4 
**Variable description**: Average value of dwellings in 1000 euros in residential area.    
**Variable type**: integer   
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average value of dwellings in 1000 euros    
**Variable name**: socenv_avv_dwellings_5 
**Variable description**: Average value of dwellings in 1000 euros in residential area.    
**Variable type**: integer   
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average value of dwellings in 1000 euros    
**Variable name**: socenv_avv_dwellings_6 
**Variable description**: Average value of dwellings in 1000 euros in residential area.    
**Variable type**: integer   
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average value of a plot (m2) in euros (dwellings)    
**Variable name**: socenv_avv_dwelling_m2_0  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area.    
**Variable type**: integer   
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average value of a plot (m2) in euros (dwellings)    
**Variable name**: socenv_avv_dwelling_m2_1  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area.    
**Variable type**: integer   
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average value of a plot (m2) in euros (dwellings)    
**Variable name**: socenv_avv_dwelling_m2_2  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area.    
**Variable type**: integer   
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average value of a plot (m2) in euros (dwellings)    
**Variable name**: socenv_avv_dwelling_m2_3  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area.    
**Variable type**: integer   
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average value of a plot (m2) in euros (dwellings)    
**Variable name**: socenv_avv_dwelling_m2_4  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area.    
**Variable type**: integer   
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average value of a plot (m2) in euros (dwellings)    
**Variable name**: socenv_avv_dwelling_m2_5  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area.    
**Variable type**: integer   
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average value of a plot (m2) in euros (dwellings)    
**Variable name**: socenv_avv_dwelling_m2_6  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area.    
**Variable type**: integer   
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of unoccupied dwellings   
**Variable name**: socenv_perc_unocc_dwellings_0
**Variable description**: Percentage of unoccupied dwellings in residential area.    
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of unoccupied dwellings   
**Variable name**: socenv_perc_unocc_dwellings_1
**Variable description**: Percentage of unoccupied dwellings in residential area.    
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of unoccupied dwellings   
**Variable name**: socenv_perc_unocc_dwellings_2
**Variable description**: Percentage of unoccupied dwellings in residential area.    
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete 
**Harmonization comment**:  
For HUNT, these data are available for municipalities in 2011. This variable was calculated  by: 100 - (number of occupied dwellings in the area / total number of dwellings in the area). This variable has been linked to cohort respondents in 2006 using their municipality code. References to the original data sources are listed in the WP7 deliverable report.
**R script**: 
```{r, echo=TRUE}  
socenv_HUNT_2$socenv_perc_unocc_dwellings_2<-as.numeric(HUNT3$PROPORTION_UNOCCUPIED_DWELLINGS_2011) 

```



### **Variable label**: Percentage of unoccupied dwellings   
**Variable name**: socenv_perc_unocc_dwellings_3
**Variable description**: Percentage of unoccupied dwellings in residential area.    
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of unoccupied dwellings   
**Variable name**: socenv_perc_unocc_dwellings_4
**Variable description**: Percentage of unoccupied dwellings in residential area.    
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of unoccupied dwellings   
**Variable name**: socenv_perc_unocc_dwellings_5
**Variable description**: Percentage of unoccupied dwellings in residential area.    
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of unoccupied dwellings   
**Variable name**: socenv_perc_unocc_dwellings_6
**Variable description**: Percentage of unoccupied dwellings in residential area.    
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



# Income

### **Variable label**: Average income in 1000 euros 
**Variable name**: socenv_av_inc1000_0  
**Variable description**: Average income in 1000 euros of residents in residential area.    
**Variable type**: integer     
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros 
**Variable name**: socenv_av_inc1000_1  
**Variable description**: Average income in 1000 euros of residents in residential area.    
**Variable type**: integer     
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros 
**Variable name**: socenv_av_inc1000_2  
**Variable description**: Average income in 1000 euros of residents in residential area.    
**Variable type**: integer     
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**: complete 
**Harmonization comment**:  
For HUNT, these data are available for municipalities in 2006. This variable includes the average gross year income in 1000 euros of residents aged 17 years and older in municipalities. This variable was already converted using a currency conversion of 1.00NOK=€0.0961356. However, this exchange rate was incorrect and therefore this variable should be recalculated using the correct currency conversion of ECB in 2006, which is 1.00NOK=€0.12433. The final variable has been linked to cohort respondents in 2006 using their municipality code. For harmonization purposes, this variable has been made integer and has been rounded. References to the original data sources are listed in the WP7 deliverable report.  
**R script**:  
```{r, echo=TRUE}  
socenv_HUNT_2$socenv_av_inc1000_2<-as.integer(round(as.numeric(HUNT3$AVERAGE_INCOME_2006/0.0961356)*0.12433)/1000) 

```    



### **Variable label**: Average income in 1000 euros 
**Variable name**: socenv_av_inc1000_3  
**Variable description**: Average income in 1000 euros of residents in residential area.    
**Variable type**: integer     
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros 
**Variable name**: socenv_av_inc1000_4  
**Variable description**: Average income in 1000 euros of residents in residential area.    
**Variable type**: integer     
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros 
**Variable name**: socenv_av_inc1000_5  
**Variable description**: Average income in 1000 euros of residents in residential area.    
**Variable type**: integer     
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros 
**Variable name**: socenv_av_inc1000_6  
**Variable description**: Average income in 1000 euros of residents in residential area.    
**Variable type**: integer     
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in euros 
**Variable name**: socenv_av_inc_0  
**Variable description**: Average income in euros of residents in residential area.    
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in euros 
**Variable name**: socenv_av_inc_1  
**Variable description**: Average income in euros of residents in residential area.    
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in euros 
**Variable name**: socenv_av_inc_2  
**Variable description**: Average income in euros of residents in residential area.    
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: complete  
**Harmonization comment**: 
For HUNT, these data are available for municipalities in 2006. This variable includes the average gross year income in euros of residents aged 17 years and older in municipalities. This variable was already converted using a currency conversion of 1.00NOK=€0.0961356. However, this exchange rate was incorrect and therefore this variable should be recalculated using the correct currency conversion of ECB in 2006, which is 1.00NOK=€0.12433. The final variable has been linked to cohort respondents in 2006 using their municipality code. For harmonization purposes, this variable has been made integer and has been rounded. References to the original data sources are listed in the WP7 deliverable report. 
**R script**:  
```{r, echo=TRUE}  
socenv_HUNT_2$socenv_av_inc_2<-as.integer(round(as.numeric(HUNT3$AVERAGE_INCOME_2006/0.0961356)*0.12433)) 

```       



### **Variable label**: Average income in euros 
**Variable name**: socenv_av_inc_3  
**Variable description**: Average income in euros of residents in residential area.    
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in euros 
**Variable name**: socenv_av_inc_4 
**Variable description**: Average income in euros of residents in residential area.    
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in euros 
**Variable name**: socenv_av_inc_5  
**Variable description**: Average income in euros of residents in residential area.    
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in euros 
**Variable name**: socenv_av_inc_6  
**Variable description**: Average income in euros of residents in residential area.    
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros (dichotomized)  
**Variable name**: socenv_av_incdich1000_0 
**Variable description**: Average income in 1000 euros of residents in residential area (dichotomized: below/above country-specific mean household income).    
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros (dichotomized)  
**Variable name**: socenv_av_incdich1000_1 
**Variable description**: Average income in 1000 euros of residents in residential area (dichotomized: below/above country-specific mean household income).    
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros (dichotomized)  
**Variable name**: socenv_av_incdich1000_2 
**Variable description**: Average income in 1000 euros of residents in residential area (dichotomized: below/above country-specific mean household income).    
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: complete  
**Harmonization comment**: 
We dichotomized average gross yearly income in 1000 euros of residents aged 17 years or older in the municipality in 2006 by comparing it with the country-specific gross mean household income (data from Norway Statistics) in 2006. The country-specific mean gross household income in 2006 was €65608 (527700 NOK; ECB currency conversion in 2006: 1.00NOK=€0.12433). The original variable on average gross yearly income was calculated using an incorrect exchange rate (1NOK=€0.0961356). This has been corrected here. 
Furthermore, we make the assumption that when the average household size is 2 or above, there are 2 income earners in the household. The income variable has been calculated as follows: 
if hh_size<2, income_correction= income*hh_size
if hh_size>=2, income_correction= income*2
Subsequently, the income variable has been compared with the country-specific mean gross household income.
The final variable has been linked to cohort respondents in 2006 using their municipality code. References to the original data sources are listed in the WP7 deliverable report. 
**R script**:  
```{r, echo=TRUE} 

socenv_HUNT_2$socenv_av_incdich1000_2 <-
ifelse((as.numeric(HUNT3$AVERAGE_HOUSEHOLD_SIZE_2006))<2,
as.numeric(((HUNT3$AVERAGE_INCOME_2006/0.0961356)*0.12433)/1000)*as.numeric(HUNT3$AVERAGE_HOUSEHOLD_SIZE_2006),
as.numeric(((HUNT3$AVERAGE_INCOME_2006/0.0961356)*0.12433)/1000)*2)

socenv_HUNT_2$socenv_av_incdich1000_2 <-
ifelse(as.numeric(socenv_HUNT_2$socenv_av_incdich1000_2) > 65.508, 1, 0)

```   




### **Variable label**: Average income in 1000 euros (dichotomized)  
**Variable name**: socenv_av_incdich1000_3 
**Variable description**: Average income in 1000 euros of residents in residential area (dichotomized: below/above country-specific mean household income).    
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros (dichotomized)  
**Variable name**: socenv_av_incdich1000_4 
**Variable description**: Average income in 1000 euros of residents in residential area (dichotomized: below/above country-specific mean household income).    
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros (dichotomized)  
**Variable name**: socenv_av_incdich1000_5 
**Variable description**: Average income in 1000 euros of residents in residential area (dichotomized: below/above country-specific mean household income).    
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros (dichotomized)  
**Variable name**: socenv_av_incdich1000_6 
**Variable description**: Average income in 1000 euros of residents in residential area (dichotomized: below/above country-specific mean household income).    
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in euros (dichotomized) 
**Variable name**: socenv_av_incdich_0  
**Variable description**: Average income in euros of residents in residential area (dichotomized: below/above country-specific  mean household income).     
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in euros (dichotomized) 
**Variable name**: socenv_av_incdich_1  
**Variable description**: Average income in euros of residents in residential area (dichotomized: below/above country-specific  mean household income).     
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in euros (dichotomized) 
**Variable name**: socenv_av_incdich_2  
**Variable description**: Average income in euros of residents in residential area (dichotomized: below/above country-specific  mean household income).     
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: complete  
**Harmonization comment**:
We dichotomized average gross yearly income in 1000 euros of residents aged 17 years or older in the municipality in 2006 by comparing it with the country-specific gross mean household income (data from Norway Statistics) in 2006. The country-specific mean gross household income in 2006 was €65608 (527700 NOK; ECB currency conversion in 2006: 1.00NOK=€0.12433). The original variable on average gross yearly income was calculated using an incorrect exchange rate (1NOK=€0.0961356). This has been corrected here. 
Furthermore, we make the assumption that when the average household size is 2 or above, there are 2 income earners in the household. The income variable has been calculated as follows: 
if hh_size<2, income_correction= income*hh_size
if hh_size>=2, income_correction= income*2
Subsequently, the income variable has been compared with the country-specific mean gross household income.
The final variable has been linked to cohort respondents in 2006 using their municipality code. References to the original data sources are listed in the WP7 deliverable report. 
**R script**:  
```{r, echo=TRUE} 

socenv_HUNT_2$socenv_av_incdich_2 <-
ifelse((as.numeric(HUNT3$AVERAGE_HOUSEHOLD_SIZE_2006))<2,
as.numeric(((HUNT3$AVERAGE_INCOME_2006/0.0961356)*0.12433))*as.numeric(HUNT3$AVERAGE_HOUSEHOLD_SIZE_2006),
as.numeric(((HUNT3$AVERAGE_INCOME_2006/0.0961356)*0.12433))*2)

socenv_HUNT_2$socenv_av_incdich_2 <-
ifelse(as.numeric(socenv_HUNT_2$socenv_av_incdich_2) > 65508, 1, 0)
  
```     




### **Variable label**: Average income in euros (dichotomized) 
**Variable name**: socenv_av_incdich_3  
**Variable description**: Average income in euros of residents in residential area (dichotomized: below/above country-specific  mean household income).     
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in euros (dichotomized) 
**Variable name**: socenv_av_incdich_4  
**Variable description**: Average income in euros of residents in residential area (dichotomized: below/above country-specific  mean household income).     
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in euros (dichotomized) 
**Variable name**: socenv_av_incdich_5  
**Variable description**: Average income in euros of residents in residential area (dichotomized: below/above country-specific  mean household income).     
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in euros (dichotomized) 
**Variable name**: socenv_av_incdich_6  
**Variable description**: Average income in euros of residents in residential area (dichotomized: below/above country-specific  mean household income).     
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_500m_0  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_500m_1  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_500m_2  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_500m_3  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_500m_4  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_500m_5  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_500m_6  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_1000m_0  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_1000m_1  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_1000m_2  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_1000m_3  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_1000m_4  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_1000m_5  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_1000m_6  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_2000m_0  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_2000m_1  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address.
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_2000m_2  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_2000m_3  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_2000m_4  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address.
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_2000m_5  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros
**Variable name**: socenv_av_hhinc_2000m_6  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address. 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_500m_0  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_500m_1  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_500m_2  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_500m_3  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_500m_4  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_500m_5  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_500m_6  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_1000m_0  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_1000m_1  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_1000m_2  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_1000m_3  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_1000m_4  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_1000m_5  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_1000m_6  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_2000m_0  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_2000m_1  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_2000m_2  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_2000m_3  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_2000m_4  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_2000m_5  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average household income in euros (dichotomized)
**Variable name**: socenv_av_hhincdich_2000m_6  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address (dichotomized: below/above country-specific mean household income).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific mean household income
1 | Greater than country-specific mean household income   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros (Z standardised)  
**Variable name**: socenv_av_inc1000Z_0  
**Variable description**: Average income in 1000 euros of residents in residential area (standardized: mean=0 and sd=1).
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros (Z standardised)  
**Variable name**: socenv_av_inc1000Z_1  
**Variable description**: Average income in 1000 euros of residents in residential area (standardized: mean=0 and sd=1).
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros (Z standardised)  
**Variable name**: socenv_av_inc1000Z_2  
**Variable description**: Average income in 1000 euros of residents in residential area (standardized: mean=0 and sd=1).
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete
**Harmonization comment**: 
We standardized average gross year income in 1000 euros of residents in the neighbourhood by using the formula: Z=(x-y)/o (Z=standardized income variable with mean=0, sd=1; x=area-level average income from respondent; y=area-level average income in entire country; o=standard deviation of area-level income in entire country). Based on municipality-level data from Statistics Norway, we calculated y and o in 2006 in Norway: y=21.3724 and o=2.346074.
**R script**:  
```{r, echo=TRUE}  

socenv_HUNT_2$socenv_av_inc1000Z_2 <- as.numeric(((((HUNT3$AVERAGE_INCOME_2006/0.0961356)*0.080472)/1000)-21.3724)/2.346074)

```    



### **Variable label**: Average income in 1000 euros (Z standardised)  
**Variable name**: socenv_av_inc1000Z_3  
**Variable description**: Average income in 1000 euros of residents in residential area (standardized: mean=0 and sd=1).
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros (Z standardised)  
**Variable name**: socenv_av_inc1000Z_4  
**Variable description**: Average income in 1000 euros of residents in residential area (standardized: mean=0 and sd=1).
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros (Z standardised)  
**Variable name**: socenv_av_inc1000Z_5  
**Variable description**: Average income in 1000 euros of residents in residential area (standardized: mean=0 and sd=1).
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in 1000 euros (Z standardised)  
**Variable name**: socenv_av_inc1000Z_6  
**Variable description**: Average income in 1000 euros of residents in residential area (standardized: mean=0 and sd=1).
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Average income in euros (Z standardized)  
**Variable name**: socenv_av_incZ_0  
**Variable description**: Average income in euros of residents in residential area (standardized: mean=0 and sd=1). **Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```   



### **Variable label**: Average income in euros (Z standardized)  
**Variable name**: socenv_av_incZ_1  
**Variable description**: Average income in euros of residents in residential area (standardized: mean=0 and sd=1). **Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```   



### **Variable label**: Average income in euros (Z standardized)  
**Variable name**: socenv_av_incZ_2  
**Variable description**: Average income in euros of residents in residential area (standardized: mean=0 and sd=1). **Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Harmonization status**: complete
**Harmonization comment**: 
We standardized average gross year income of residents in the neighbourhood by using the formula: Z=(x-y)/o (Z=standardized income variable with mean=0, sd=1; x=area-level average income from respondent; y=area-level average income in entire country; o=standard deviation of area-level income in entire country). Based on municipality-level data from Statistics Norway, we calculated y and o in 2006 in Norway: y=21372.40 and o=2346.074.
**R script**:  
 
```{r, echo=TRUE}  

socenv_HUNT_2$socenv_av_incZ_2 <- as.numeric((((HUNT3$AVERAGE_INCOME_2006/0.0961356)*0.080472)-21372.40)/2346.074)

```    




### **Variable label**: Average income in euros (Z standardized)  
**Variable name**: socenv_av_incZ_3  
**Variable description**: Average income in euros of residents in residential area (standardized: mean=0 and sd=1). **Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Average income in euros (Z standardized)  
**Variable name**: socenv_av_incZ_4  
**Variable description**: Average income in euros of residents in residential area (standardized: mean=0 and sd=1). **Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Average income in euros (Z standardized)  
**Variable name**: socenv_av_incZ_5  
**Variable description**: Average income in euros of residents in residential area (standardized: mean=0 and sd=1). **Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Average income in euros (Z standardized)  
**Variable name**: socenv_av_incZ_6  
**Variable description**: Average income in euros of residents in residential area (standardized: mean=0 and sd=1). **Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 

### **Variable label**: Percentage of income recipients
**Variable name**: socenv_perc_inc_recipients_0  
**Variable description**: Percentage of income recipients in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 

### **Variable label**: Percentage of income recipients
**Variable name**: socenv_perc_inc_recipients_1  
**Variable description**: Percentage of income recipients in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of income recipients
**Variable name**: socenv_perc_inc_recipients_2 
**Variable description**: Percentage of income recipients in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of income recipients
**Variable name**: socenv_perc_inc_recipients_3  
**Variable description**: Percentage of income recipients in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of income recipients
**Variable name**: socenv_perc_inc_recipients_4  
**Variable description**: Percentage of income recipients in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of income recipients
**Variable name**: socenv_perc_inc_recipients_5  
**Variable description**: Percentage of income recipients in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of income recipients
**Variable name**: socenv_perc_inc_recipients_6  
**Variable description**: Percentage of income recipients in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



# Unemployment

### **Variable label**: Percentage of unemployed residents  
**Variable name**: socenv_perc_unemployment_0  
**Variable description**: Percentage of unemployed residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of unemployed residents  
**Variable name**: socenv_perc_unemployment_1  
**Variable description**: Percentage of unemployed residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of unemployed residents  
**Variable name**: socenv_perc_unemployment_2  
**Variable description**: Percentage of unemployed residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete 
**Harmonization comment**: 
For HUNT, these data are available for municipalities in 2006. This variable includes the percentage of unemployed residents aged 15-74 years in the municipality. This variable was already available in the original data source. This variable has been linked to cohort respondents in 2006 using their municipality code. References to the original data sources are listed in the WP7 deliverable report.
**R script**:  
```{r, echo=TRUE} 

socenv_HUNT_2$socenv_perc_unemployment_2<-as.numeric(HUNT3$UNEMPLOYMENT_RATE_2006) 

```    



### **Variable label**: Percentage of unemployed residents  
**Variable name**: socenv_perc_unemployment_3  
**Variable description**: Percentage of unemployed residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of unemployed residents  
**Variable name**: socenv_perc_unemployment_4  
**Variable description**: Percentage of unemployed residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of unemployed residents  
**Variable name**: socenv_perc_unemployment_5  
**Variable description**: Percentage of unemployed residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of unemployed residents  
**Variable name**: socenv_perc_unemployment_6  
**Variable description**: Percentage of unemployed residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



# Social security

### **Variable label**: Percentage of social security beneficiaries  
**Variable name**: socenv_percentage_socsecben_0  
**Variable description**: Percentage of social security beneficiaries in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of social security beneficiaries  
**Variable name**: socenv_percentage_socsecben_1  
**Variable description**: Percentage of social security beneficiaries in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of social security beneficiaries  
**Variable name**: socenv_percentage_socsecben_2  
**Variable description**: Percentage of social security beneficiaries in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete 
**Harmonization comment**: 
For HUNT, these data are available for municipalities in 2006. This variable was calculated by: total number of recipients of social assistance in the municipality / total number of residents in the municipality * 100. This variable has been linked to cohort respondents in 2006 using their municipality code. References to the original data sources are listed in the WP7 deliverable report.
**R script**:  
```{r, echo=TRUE}  
socenv_HUNT_2$socenv_percentage_socsecben_2<-as.numeric(HUNT3$PROPORTION_SOCSECBEN_2006) 
```   




### **Variable label**: Percentage of social security beneficiaries  
**Variable name**: socenv_percentage_socsecben_3  
**Variable description**: Percentage of social security beneficiaries in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of social security beneficiaries  
**Variable name**: socenv_percentage_socsecben_4  
**Variable description**: Percentage of social security beneficiaries in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of social security beneficiaries  
**Variable name**: socenv_percentage_socsecben_5  
**Variable description**: Percentage of social security beneficiaries in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of social security beneficiaries  
**Variable name**: socenv_percentage_socsecben_6  
**Variable description**: Percentage of social security beneficiaries in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of residents with disability benefit  
**Variable name**: socenv_percentage_disben_0   
**Variable description**: Percentage of residents with a disability benefit in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

``` 



### **Variable label**: Percentage of residents with disability benefit  
**Variable name**: socenv_percentage_disben_1   
**Variable description**: Percentage of residents with a disability benefit in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents with disability benefit  
**Variable name**: socenv_percentage_disben_2   
**Variable description**: Percentage of residents with a disability benefit in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents with disability benefit  
**Variable name**: socenv_percentage_disben_3   
**Variable description**: Percentage of residents with a disability benefit in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents with disability benefit  
**Variable name**: socenv_percentage_disben_4   
**Variable description**: Percentage of residents with a disability benefit in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents with disability benefit  
**Variable name**: socenv_percentage_disben_5   
**Variable description**: Percentage of residents with a disability benefit in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents with disability benefit  
**Variable name**: socenv_percentage_disben_6   
**Variable description**: Percentage of residents with a disability benefit in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents with unemployment benefit  
**Variable name**: socenv_percentage_unemplben_0   
**Variable description**: Percentage of residents with a unemployment benefit in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents with unemployment benefit  
**Variable name**: socenv_percentage_unemplben_1   
**Variable description**: Percentage of residents with a unemployment benefit in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents with unemployment benefit  
**Variable name**: socenv_percentage_unemplben_2   
**Variable description**: Percentage of residents with a unemployment benefit in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents with unemployment benefit  
**Variable name**: socenv_percentage_unemplben_3   
**Variable description**: Percentage of residents with a unemployment benefit in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents with unemployment benefit  
**Variable name**: socenv_percentage_unemplben_4   
**Variable description**: Percentage of residents with a unemployment benefit in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents with unemployment benefit  
**Variable name**: socenv_percentage_unemplben_5   
**Variable description**: Percentage of residents with a unemployment benefit in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of residents with unemployment benefit  
**Variable name**: socenv_percentage_unemplben_6   
**Variable description**: Percentage of residents with a unemployment benefit in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



# Educational level  

### **Variable label**: Percentage of low educated residents  
**Variable name**: socenv_perc_low_education_0  
**Variable description**: Percentage of low educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of low educated residents  
**Variable name**: socenv_perc_low_education_1  
**Variable description**: Percentage of low educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of low educated residents  
**Variable name**: socenv_perc_low_education_2  
**Variable description**: Percentage of low educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete  
**Harmonization comment**:
For HUNT, these data are available for municipalities in 2011. This variable includes the percentage of residents aged 16 years or older with low educational level (primary education) in the municipality. This variable has been linked to cohort respondents in 2006 using their municipality code. References to the original data sources are listed in the WP7 deliverable report.
**R script**:  
```{r, echo=TRUE} 

socenv_HUNT_2$socenv_perc_low_education_2<-as.numeric(HUNT3$PROPORTION_LOW_EDUCATION_2011) 

```   



### **Variable label**: Percentage of low educated residents  
**Variable name**: socenv_perc_low_education_3  
**Variable description**: Percentage of low educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of low educated residents  
**Variable name**: socenv_perc_low_education_4  
**Variable description**: Percentage of low educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of low educated residents  
**Variable name**: socenv_perc_low_education_5  
**Variable description**: Percentage of low educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of low educated residents  
**Variable name**: socenv_perc_low_education_6  
**Variable description**: Percentage of low educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of intermediate educated residents  
**Variable name**: socenv_perc_itm_education_0  
**Variable description**: Percentage of intermediate educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of intermediate educated residents  
**Variable name**: socenv_perc_itm_education_1  
**Variable description**: Percentage of intermediate educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of intermediate educated residents  
**Variable name**: socenv_perc_itm_education_2  
**Variable description**: Percentage of intermediate educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete 
**Harmonization comment**:
For HUNT, these data are available for municipalities in 2011. This variable includes the percentage of residents aged 16 years or older with intermediate educational level (upper secondary education) in the municipality. This variable has been linked to cohort respondents in 2006 using their municipality code. References to the original data sources are listed in the WP7 deliverable report.
**R script**:  
```{r, echo=TRUE}  
socenv_HUNT_2$socenv_perc_itm_education_2<-as.numeric(HUNT3$PROPORTION_INTERMEDIATE_EDUCATION_2011) 
```    



### **Variable label**: Percentage of intermediate educated residents  
**Variable name**: socenv_perc_itm_education_3  
**Variable description**: Percentage of intermediate educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of intermediate educated residents  
**Variable name**: socenv_perc_itm_education_4  
**Variable description**: Percentage of intermediate educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of intermediate educated residents  
**Variable name**: socenv_perc_itm_education_5  
**Variable description**: Percentage of intermediate educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of intermediate educated residents  
**Variable name**: socenv_perc_itm_education_6  
**Variable description**: Percentage of intermediate educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of high educated residents  
**Variable name**: socenv_perc_high_education_0  
**Variable description**: Percentage of high educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of high educated residents  
**Variable name**: socenv_perc_high_education_1  
**Variable description**: Percentage of high educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of high educated residents  
**Variable name**: socenv_perc_high_education_2  
**Variable description**: Percentage of high educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete    
**Harmonization comment**:
For HUNT, these data are available for municipalities in 2011. This variable includes the percentage of residents aged 16 years or older with high educational level (tertiary education + tertiary vocational education) in the municipality. This variable has been linked to cohort respondents in 2006 using their municipality code. References to the original data sources are listed in the WP7 deliverable report.
**R script**:  
```{r, echo=TRUE}

socenv_HUNT_2$socenv_perc_high_education_2<-as.numeric(HUNT3$PROPORTION_HIGH_EDUCATION_2011) 

```    




### **Variable label**: Percentage of high educated residents  
**Variable name**: socenv_perc_high_education_3  
**Variable description**: Percentage of high educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of high educated residents  
**Variable name**: socenv_perc_high_education_4  
**Variable description**: Percentage of high educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of high educated residents  
**Variable name**: socenv_perc_high_education_5  
**Variable description**: Percentage of high educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Percentage of high educated residents  
**Variable name**: socenv_perc_high_education_6  
**Variable description**: Percentage of high educated residents in residential area.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```

# Crime  

### **Variable label**: Number of criminal offenses per 1000 residents  
**Variable name**: socenv_crimoff_0    
**Variable description**: Number of criminal offenses per 1000 residents in residential area.       
**Variable type**: integer    
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of criminal offenses per 1000 residents  
**Variable name**: socenv_crimoff_1    
**Variable description**: Number of criminal offenses per 1000 residents in residential area.       
**Variable type**: integer    
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of criminal offenses per 1000 residents  
**Variable name**: socenv_crimoff_2    
**Variable description**: Number of criminal offenses per 1000 residents in residential area.       
**Variable type**: integer    
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of criminal offenses per 1000 residents  
**Variable name**: socenv_crimoff_3    
**Variable description**: Number of criminal offenses per 1000 residents in residential area.       
**Variable type**: integer    
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of criminal offenses per 1000 residents  
**Variable name**: socenv_crimoff_4    
**Variable description**: Number of criminal offenses per 1000 residents in residential area.       
**Variable type**: integer    
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of criminal offenses per 1000 residents  
**Variable name**: socenv_crimoff_5    
**Variable description**: Number of criminal offenses per 1000 residents in residential area.       
**Variable type**: integer    
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of criminal offenses per 1000 residents  
**Variable name**: socenv_crimoff_6    
**Variable description**: Number of criminal offenses per 1000 residents in residential area.       
**Variable type**: integer    
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```

### **Variable label**: Number of vandalism and public disorder per 1000 residents  
**Variable name**: socenv_vandalism_po_0   
**Variable description**: Number of vandalism and public disorder per 1000 residents in residential area.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of vandalism and public disorder per 1000 residents  
**Variable name**: socenv_vandalism_po_1   
**Variable description**: Number of vandalism and public disorder per 1000 residents in residential area.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of vandalism and public disorder per 1000 residents  
**Variable name**: socenv_vandalism_po_2   
**Variable description**: Number of vandalism and public disorder per 1000 residents in residential area.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of vandalism and public disorder per 1000 residents  
**Variable name**: socenv_vandalism_po_3   
**Variable description**: Number of vandalism and public disorder per 1000 residents in residential area.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of vandalism and public disorder per 1000 residents  
**Variable name**: socenv_vandalism_po_4   
**Variable description**: Number of vandalism and public disorder per 1000 residents in residential area.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of vandalism and public disorder per 1000 residents  
**Variable name**: socenv_vandalism_po_5   
**Variable description**: Number of vandalism and public disorder per 1000 residents in residential area.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of vandalism and public disorder per 1000 residents  
**Variable name**: socenv_vandalism_po_6   
**Variable description**: Number of vandalism and public disorder per 1000 residents in residential area.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of violent crimes and sexual offenses per 1000 residents   
**Variable name**: socenv_violentcrim_sexoff_0    
**Variable description**: Number of violent crimes and sexual offenses per 1000 residents in residential area.    **Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of violent crimes and sexual offenses per 1000 residents   
**Variable name**: socenv_violentcrim_sexoff_1    
**Variable description**: Number of violent crimes and sexual offenses per 1000 residents in residential area.    **Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of violent crimes and sexual offenses per 1000 residents   
**Variable name**: socenv_violentcrim_sexoff_2    
**Variable description**: Number of violent crimes and sexual offenses per 1000 residents in residential area.    **Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of violent crimes and sexual offenses per 1000 residents   
**Variable name**: socenv_violentcrim_sexoff_3    
**Variable description**: Number of violent crimes and sexual offenses per 1000 residents in residential area.    **Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of violent crimes and sexual offenses per 1000 residents   
**Variable name**: socenv_violentcrim_sexoff_4    
**Variable description**: Number of violent crimes and sexual offenses per 1000 residents in residential area.    **Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of violent crimes and sexual offenses per 1000 residents   
**Variable name**: socenv_violentcrim_sexoff_5    
**Variable description**: Number of violent crimes and sexual offenses per 1000 residents in residential area.    **Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Number of violent crimes and sexual offenses per 1000 residents   
**Variable name**: socenv_violentcrim_sexoff_6    
**Variable description**: Number of violent crimes and sexual offenses per 1000 residents in residential area.    **Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```

#Area indicators

### **Variable label**: Area indicator: city 
**Variable name**: socenv_city_0    
**Variable description**: City indicator.    
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: city 
**Variable name**: socenv_city_1    
**Variable description**: City indicator.    
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: city 
**Variable name**: socenv_city_2    
**Variable description**: City indicator.    
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: city 
**Variable name**: socenv_city_3    
**Variable description**: City indicator.    
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: city 
**Variable name**: socenv_city_4    
**Variable description**: City indicator.    
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: city 
**Variable name**: socenv_city_5    
**Variable description**: City indicator.    
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: city 
**Variable name**: socenv_city_6    
**Variable description**: City indicator.    
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: municipality
**Variable name**: socenv_municipality_0    
**Variable description**: Municipality indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: municipality
**Variable name**: socenv_municipality_1    
**Variable description**: Municipality indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: municipality
**Variable name**: socenv_municipality_2    
**Variable description**: Municipality indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: complete
**Harmonization comment**:  For HUNT, the indicator variables start with 44.
**R script**:  
```{r, echo=TRUE}  
socenv_HUNT_2$socenv_municipality_2<-as.integer(HUNT3$municipality + 44000000)

```


### **Variable label**: Area indicator: municipality
**Variable name**: socenv_municipality_3    
**Variable description**: Municipality indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: municipality
**Variable name**: socenv_municipality_4     
**Variable description**: Municipality indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: municipality
**Variable name**: socenv_municipality_5    
**Variable description**: Municipality indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: municipality
**Variable name**: socenv_municipality_6    
**Variable description**: Municipality indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: neighbourhood
**Variable name**: socenv_neighbourhood_0    
**Variable description**: Neighbourhood indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: neighbourhood
**Variable name**: socenv_neighbourhood_1    
**Variable description**: Neighbourhood indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: neighbourhood
**Variable name**: socenv_neighbourhood_2    
**Variable description**: Neighbourhood indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: neighbourhood
**Variable name**: socenv_neighbourhood_3    
**Variable description**: Neighbourhood indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: neighbourhood
**Variable name**: socenv_neighbourhood_4    
**Variable description**: Neighbourhood indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: neighbourhood
**Variable name**: socenv_neighbourhood_5    
**Variable description**: Neighbourhood indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: neighbourhood
**Variable name**: socenv_neighbourhood_6    
**Variable description**: Neighbourhood indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 4-digit postal code
**Variable name**: socenv_pc4_0    
**Variable description**:  4-digit postal code (PC4) indicator. 
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 4-digit postal code
**Variable name**: socenv_pc4_1    
**Variable description**:  4-digit postal code (PC4) indicator. 
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 4-digit postal code
**Variable name**: socenv_pc4_2    
**Variable description**:  4-digit postal code (PC4) indicator. 
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 4-digit postal code
**Variable name**: socenv_pc4_3    
**Variable description**:  4-digit postal code (PC4) indicator. 
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 4-digit postal code
**Variable name**: socenv_pc4_4    
**Variable description**:  4-digit postal code (PC4) indicator. 
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 4-digit postal code
**Variable name**: socenv_pc4_5    
**Variable description**:  4-digit postal code (PC4) indicator. 
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 4-digit postal code
**Variable name**: socenv_pc4_6    
**Variable description**:  4-digit postal code (PC4) indicator. 
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 6-digit postal code
**Variable name**: socenv_pc6_0    
**Variable description**:  6-digit postal code (PC6) indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 6-digit postal code
**Variable name**: socenv_pc6_1    
**Variable description**:  6-digit postal code (PC6) indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 6-digit postal code
**Variable name**: socenv_pc6_2    
**Variable description**:  6-digit postal code (PC6) indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 6-digit postal code
**Variable name**: socenv_pc6_3    
**Variable description**:  6-digit postal code (PC6) indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 6-digit postal code
**Variable name**: socenv_pc6_4    
**Variable description**:  6-digit postal code (PC6) indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 6-digit postal code
**Variable name**: socenv_pc6_5    
**Variable description**:  6-digit postal code (PC6) indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 6-digit postal code
**Variable name**: socenv_pc6_6    
**Variable description**:  6-digit postal code (PC6) indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 5-digit postal code
**Variable name**: socenv_pc5_0    
**Variable description**:  5-digit postal code (PC5) indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 5-digit postal code
**Variable name**: socenv_pc5_1    
**Variable description**:  5-digit postal code (PC5) indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 5-digit postal code
**Variable name**: socenv_pc5_2    
**Variable description**:  5-digit postal code (PC5) indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 5-digit postal code
**Variable name**: socenv_pc5_3    
**Variable description**:  5-digit postal code (PC5) indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 5-digit postal code
**Variable name**: socenv_pc5_4    
**Variable description**:  5-digit postal code (PC5) indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 5-digit postal code
**Variable name**: socenv_pc5_5    
**Variable description**:  5-digit postal code (PC5) indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```



### **Variable label**: Area indicator: 5-digit postal code
**Variable name**: socenv_pc5_6    
**Variable description**:  5-digit postal code (PC5) indicator.   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**: impossible 
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```
