---
title: "Social environmental (i.e. geospatial) DataSchema"
output: html_document
---
# Table of Contents
1. [Urbanization grade] #(Urbanzation grade)  
2. [Demographics] #(Demographics)  
3. [Housing] #(Housing)  
4. [Income] #(Income)  
5. [Unemployment rate] #(Unemployment rate)  
6. [Social security] #(Social security)  
7. [Educational level] #(Educational level)  
8. [Immigrants and ethnic minority groups] #(Immigrants and ethnic minority groups)  
9. [Crime] #(Crime)  
10. [Social cohesion] (#Social cohesion)  

# Urbanization grade

### **Variable label**: Urbanization grade in 2006  
**Variable name**: socenv_urbanization_grade_2006    
**Variable description**: Population density of the residential area (number of residents per km2) in 2006.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  

### **Variable label**: Urbanization grade in 2007 
**Variable name**: socenv_urbanization_grade_2007    
**Variable description**: Population density of the residential area (number of residents per km2) in 2007.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  

### **Variable label**: Urbanization grade in 2009 
**Variable name**: socenv_urbanization_grade_2009    
**Variable description**: Population density of the residential area (number of residents per km2) in 2009.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  

### **Variable label**: Urbanization grade in 2011 
**Variable name**: socenv_urbanization_grade_2011    
**Variable description**: Population density of the residential area (number of residents per km2) in 2011.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  

### **Variable label**: Urbanization grade in 2014
**Variable name**: socenv_urbanization_grade_2014    
**Variable description**: Population density of the residential area (number of residents per km2) in 2014.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written  




# Demographics

### **Variable label**: Proportion of men in 2006  
**Variable name**: socenv_proportion_men_2006    
**Variable description**: Proportion of men in the residential area in 2006.  
**Variable type**: decimal
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of men in 2011  
**Variable name**: socenv_proportion_men_2011    
**Variable description**: Proportion of men in the residential area in 2011.  
**Variable type**: decimal
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of women in 2006  
**Variable name**: socenv_proportion_women_2006    
**Variable description**: Proportion of women in the residential area in 2006.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}  
#This is where the R-script will be written  



### **Variable label**: Proportion of women in 2011    
**Variable name**: socenv_proportion_women_2011    
**Variable description**: Proportion of women in the residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written


### **Variable label**: Proportion of residents aged 65 or older in 2006   
**Variable name**: socenv_proportion_65_older_2006   
**Variable description**: Proportion of residents aged 65 or older in residential area in 2006.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of residents aged 65 or older in 2007   
**Variable name**: socenv_proportion_65_older_2007   
**Variable description**: Proportion of residents aged 65 or older in residential area in 2007.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of residents aged 65 or older in 2011   
**Variable name**: socenv_proportion_65_older_2011   
**Variable description**: Proportion of residents aged 65 or older in residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of unmaried residents in 2008   
**Variable name**: socenv_proportion_unmaried_2008   
**Variable description**: Proportion of unmaried residents in residential area in 2008.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of unmaried residents in 2011   
**Variable name**: socenv_proportion_unmaried_2011   
**Variable description**: Proportion of unmaried residents in residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of maried residents in 2006   
**Variable name**: socenv_proportion_maried_2006   
**Variable description**: Proportion of maried residents in residential area in 2006.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of maried residents in 2008   
**Variable name**: socenv_proportion_maried_2008   
**Variable description**: Proportion of maried residents in residential area in 2008.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of maried residents in 2011   
**Variable name**: socenv_proportion_maried_2011   
**Variable description**: Proportion of maried residents in residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of divorced residents in 2006   
**Variable name**: socenv_proportion_divorced_2006   
**Variable description**: Proportion of divorced residents in residential area in 2006.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of divorced residents in 2008   
**Variable name**: socenv_proportion_divorced_2008   
**Variable description**: Proportion of divorced residents in residential area in 2008.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of divorced residents in 2011   
**Variable name**: socenv_proportion_divorced_2011   
**Variable description**: Proportion of divorced residents in residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of widowed residents in 2006   
**Variable name**: socenv_proportion_widowed_2006   
**Variable description**: Proportion of widowed residents in residential area in 2006.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of widowed residents in 2008     
**Variable name**: socenv_proportion_widowed_2008   
**Variable description**: Proportion of widowed residents in residential area in 2008.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Proportion of widowed residents in 2011    
**Variable name**: socenv_proportion_widowed_2011   
**Variable description**: Proportion of widowed residents in residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average household size in 2006   
**Variable name**: socenv_average_household_size_2006   
**Variable description**: Average household size in residential area in 2006.  
**Variable type**: integer 
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average household size in 2009   
**Variable name**: socenv_average_household_size_2009   
**Variable description**: Average household size in residential area in 2009.  
**Variable type**: integer 
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average household size in 2011   
**Variable name**: socenv_average_household_size_2011   
**Variable description**: Average household size in residential area in 2011.  
**Variable type**: integer 
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average household size in 2014   
**Variable name**: socenv_average_household_size_2014   
**Variable description**: Average household size in residential area in 2014.  
**Variable type**: integer 
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average household size in 2015      
**Variable name**: socenv_average_household_size_2015     
**Variable description**: Average household size in residential area in 2015.    
**Variable type**: integer 
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average household size in 2016      
**Variable name**: socenv_average_household_size_2016     
**Variable description**: Average household size in residential area in 2016.    
**Variable type**: integer 
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written

# Housing


### **Variable label**: Average value of dwellings in 1000 euro's in 2006    
**Variable name**: socenv_average_value_dwellings_2006
**Variable description**: Average value of dwellings in 1000 euro's in residential area in 2006.    
**Variable type**: integer 
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average value of dwellings in 1000 euro's in 2011    
**Variable name**: socenv_average_value_dwellings_2011
**Variable description**: Average value of dwellings in 1000 euro's in residential area in 2011.    
**Variable type**: integer 
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written
