---
title: "Social environmental (i.e. geospatial) HUNT"
output: html_document
---
# Connecting with Opal data server
## Login to server and assign study data
```{r, echo=FALSE}
#Load Opal R library
library(opal)
library(dplyr)
# Create an opal object with the login information
erasmus_opal <- opal.login()
#Login to Opal server and assign the content of the HUNT table(s) to your RStudio environment
# HUNT1
opal.assign.table.tibble(erasmus_opal, 'HUNT1', 'HUNT.HUNT1',variables = list(''))
HUNT1 <- opal.execute(erasmus_opal,'HUNT1')
# HUNT2
opal.assign.table.tibble(erasmus_opal, 'HUNT2', 'HUNT.HUNT2', variables=list('')) 
HUNT2<- opal.execute(erasmus_opal,'HUNT2')
# HUNT3
opal.assign.table.tibble(erasmus_opal, 'HUNT3', 'HUNT.HUNT3',variables=list('')) 
HUNT3 <- opal.execute(erasmus_opal,'HUNT3')
```
## Assign participant id as first column of your harmonized dataframes
```{r, echo=FALSE}
socenv_HUNT_0 <- data.frame(id = HUNT1$id)
socenv_HUNT_1 <- data.frame(id = HUNT2$id)
socenv_HUNT_2 <- data.frame(id = HUNT3$id)
```
## When you are done with your work, logout of Opal server
```{r, echo=FALSE}
opal.logout(erasmus_opal) 
```
---
# Table of Contents
1. [Urbanization grade](#Urbanization grade)  
2. [Demographics](#Demographics)  
3. [Housing](#Housing)  
4. [Income](#Income)  
5. [Unemployment](#Unemployment)  
6. [Social security](#Social security)  
7. [Educational level](#Educational level)  
8. [Immigrants and ethnic minority groups](#Immigrants and ethnic minority groups)  
9. [Crime](#Crime)  
  

# Urbanization grade

### **Variable label**: Urbanization grade in 2006  
**Variable name**: socenv_urbanization_grade_2006    
**Variable description**: Population density of the residential area (number of residents per km2) in 2006.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  

### **Variable label**: Urbanization grade in 2007 
**Variable name**: socenv_urbanization_grade_2007    
**Variable description**: Population density of the residential area (number of residents per km2) in 2007.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  

### **Variable label**: Urbanization grade in 2009 
**Variable name**: socenv_urbanization_grade_2009    
**Variable description**: Population density of the residential area (number of residents per km2) in 2009.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  

### **Variable label**: Urbanization grade in 2011 
**Variable name**: socenv_urbanization_grade_2011    
**Variable description**: Population density of the residential area (number of residents per km2) in 2011.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  

### **Variable label**: Urbanization grade in 2014
**Variable name**: socenv_urbanization_grade_2014    
**Variable description**: Population density of the residential area (number of residents per km2) in 2014.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    



# Demographics

### **Variable label**: Proportion of men in 2006  
**Variable name**: socenv_proportion_men_2006    
**Variable description**: Proportion of men in the residential area in 2006.  
**Variable type**: decimal
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of men in 2011  
**Variable name**: socenv_proportion_men_2011    
**Variable description**: Proportion of men in the residential area in 2011.  
**Variable type**: decimal
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of women in 2006  
**Variable name**: socenv_proportion_women_2006    
**Variable description**: Proportion of women in the residential area in 2006.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of women in 2011    
**Variable name**: socenv_proportion_women_2011    
**Variable description**: Proportion of women in the residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of residents aged 65 or older in 2006   
**Variable name**: socenv_proportion_65_older_2006   
**Variable description**: Proportion of residents aged 65 or older in residential area in 2006.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of residents aged 65 or older in 2007   
**Variable name**: socenv_proportion_65_older_2007   
**Variable description**: Proportion of residents aged 65 or older in residential area in 2007.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of residents aged 65 or older in 2011   
**Variable name**: socenv_proportion_65_older_2011   
**Variable description**: Proportion of residents aged 65 or older in residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of unmaried residents in 2008   
**Variable name**: socenv_proportion_unmaried_2008   
**Variable description**: Proportion of unmaried residents in residential area in 2008.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of unmaried residents in 2011   
**Variable name**: socenv_proportion_unmaried_2011   
**Variable description**: Proportion of unmaried residents in residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of maried residents in 2006   
**Variable name**: socenv_proportion_maried_2006   
**Variable description**: Proportion of maried residents in residential area in 2006.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of maried residents in 2008   
**Variable name**: socenv_proportion_maried_2008   
**Variable description**: Proportion of maried residents in residential area in 2008.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of maried residents in 2011   
**Variable name**: socenv_proportion_maried_2011   
**Variable description**: Proportion of maried residents in residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of divorced residents in 2006   
**Variable name**: socenv_proportion_divorced_2006   
**Variable description**: Proportion of divorced residents in residential area in 2006.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of divorced residents in 2008   
**Variable name**: socenv_proportion_divorced_2008   
**Variable description**: Proportion of divorced residents in residential area in 2008.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of divorced residents in 2011   
**Variable name**: socenv_proportion_divorced_2011   
**Variable description**: Proportion of divorced residents in residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of widowed residents in 2006   
**Variable name**: socenv_proportion_widowed_2006   
**Variable description**: Proportion of widowed residents in residential area in 2006.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of widowed residents in 2008     
**Variable name**: socenv_proportion_widowed_2008   
**Variable description**: Proportion of widowed residents in residential area in 2008.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of widowed residents in 2011    
**Variable name**: socenv_proportion_widowed_2011   
**Variable description**: Proportion of widowed residents in residential area in 2011.  
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average household size in 2006   
**Variable name**: socenv_average_hh_size_2006   
**Variable description**: Average household size in residential area in 2006.  
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average household size in 2009   
**Variable name**: socenv_average_hh_size_2009   
**Variable description**: Average household size in residential area in 2009.  
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average household size in 2011   
**Variable name**: socenv_average_hh_size_2011   
**Variable description**: Average household size in residential area in 2011.  
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average household size in 2014   
**Variable name**: socenv_average_hh_size_2014   
**Variable description**: Average household size in residential area in 2014.  
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average household size in 2015      
**Variable name**: socenv_average_hh_size_2015     
**Variable description**: Average household size in residential area in 2015.    
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average household size in 2016      
**Variable name**: socenv_average_hh_size_2016      
**Variable description**: Average household size in residential area in 2016.    
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    


# Housing

### **Variable label**: Average value of dwellings in 1000 euros in 2006    
**Variable name**: socenv_avv_dwellings_2006  
**Variable description**: Average value of dwellings in 1000 euros in residential area in 2006.    
**Variable type**: integer   
**Variable unit**: 1000 euros   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average value of dwellings in 1000 euros in 2011    
**Variable name**: socenv_avv_dwellings_2011  
**Variable description**: Average value of dwellings in 1000 euros in residential area in 2011.    
**Variable type**: integer   
**Variable unit**: 1000 euros   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average value of a plot (m2) in euros in 2007 (dwellings)    
**Variable name**: socenv_avv_dwelling_m2_2007  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area in 2007.    
**Variable type**: integer   
**Variable unit**: euros   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average value of a plot (m2) in euros in 2011 (dwellings)  
**Variable name**: socenv_avv_dwelling_m2_2011  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area in 2011.    
**Variable type**: integer   
**Variable unit**: euros   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average value of a plot (m2) in euros in 2013 (dwellings)  
**Variable name**: socenv_avv_dwelling_m2_2013  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area in 2013.    
**Variable type**: integer   
**Variable unit**: euros   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average value of a plot (m2) in euros in 2014 (dwellings)  
**Variable name**: socenv_avv_dwelling_m2_2014  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area in 2014.    
**Variable type**: integer   
**Variable unit**: euros   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average value of a plot (m2) in euros in 2015 (dwellings)  
**Variable name**: socenv_avv_dwelling_m2_2015   
**Variable description**: Average value of a plot in euros (dwellings) in the residential area in 2015.    
**Variable type**: integer   
**Variable unit**: euros    
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of unoccupied dwellings in 2011   
**Variable name**: socenv_prop_unocc_dwellings_2011
**Variable description**: Proportion of unoccupied dwellings in residential area in 2011.    
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of unoccupied dwellings in 2012   
**Variable name**: socenv_prop_unocc_dwellings_2012
**Variable description**: Proportion of unoccupied dwellings in residential area in 2012.    
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of unoccupied dwellings in 2014   
**Variable name**: socenv_prop_unocc_dwellings_2012
**Variable description**: Proportion of unoccupied dwellings in residential area in 2012.    
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

# Income

### **Variable label**: Average income in 1000 euros in 2005  
**Variable name**: socenv_av_inc1000_2005  
**Variable description**: Average income in 1000 euros of residents in residential area in 2005.    
**Variable type**: integer     
**Variable unit**: 1000 euros   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in 1000 euros in 2006  
**Variable name**: socenv_av_inc1000_2006 
**Variable description**: Average income in 1000 euros of residents in residential area in 2006.    
**Variable type**: integer     
**Variable unit**: 1000 euros    
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in 1000 euros in 2011   
**Variable name**: socenv_av_inc1000_2011 
**Variable description**: Average income in 1000 euros of residents in residential area in 2011.    
**Variable type**: integer     
**Variable unit**: 1000 euros    
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2006  
**Variable name**: socenv_av_inc_2006  
**Variable description**: Average income in euros of residents in residential area in 2006.    
**Variable type**: integer     
**Variable unit**: euros    
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2007  
**Variable name**: socenv_av_inc_2007
**Variable description**: Average income in euros of residents in residential area in 2007.    
**Variable type**: integer     
**Variable unit**: euros    
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2011  
**Variable name**: socenv_av_inc_2011  
**Variable description**: Average income in euros of residents in residential area in 2011.    
**Variable type**: integer     
**Variable unit**: euros    
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2013  
**Variable name**: socenv_av_inc_2013  
**Variable description**: Average income in euros of residents in residential area in 2013.    
**Variable type**: integer     
**Variable unit**: euros    
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2014  
**Variable name**: socenv_av_inc_2014  
**Variable description**: Average income in euros of residents in residential area in 2014.    
**Variable type**: integer     
**Variable unit**: euros    
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2015  
**Variable name**: socenv_av_inc_2015  
**Variable description**: Average income in euros of residents in residential area in 2015.    
**Variable type**: integer     
**Variable unit**: euros     
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Average income in euros in 2016  
**Variable name**: socenv_av_inc_2016  
**Variable description**: Average income in euros of residents in residential area in 2016.    
**Variable type**: integer     
**Variable unit**: euros    
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of income recipients in 2005
**Variable name**: socenv_av_inc_recipients_2005  
**Variable description**: Proportion of income recipients in residential area in 2005.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of income recipients in 2011  
**Variable name**: socenv_av_inc_recipients_2011  
**Variable description**: Proportion of income recipients in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

# Unemployment

### **Variable label**: Proportion of unemployed residents in 2006  
**Variable name**: socenv_prop_unemployment_2006  
**Variable description**: Proportion of unemployed residents in residential area in 2006.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of unemployed residents in 2007    
**Variable name**: socenv_prop_unemployment_2007    
**Variable description**: Proportion of unemployed residents in residential area in 2007.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of unemployed residents in 2011    
**Variable name**: socenv_prop_unemployment_2011    
**Variable description**: Proportion of unemployed residents in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of unemployed residents in 2014  
**Variable name**: socenv_prop_unemployment_2014  
**Variable description**: Proportion of unemployed residents in residential area in 2014.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of unemployed residents in 2015  
**Variable name**: socenv_prop_unemployment_2015  
**Variable description**: Proportion of unemployed residents in residential area in 2015.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

# Social security

### **Variable label**: Proportion of social security beneficiaries in 2006  
**Variable name**: socenv_proportion_socsecben_2006   
**Variable description**: Proportion of social security beneficiaries in residential area in 2006.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of social security beneficiaries in 2007    
**Variable name**: socenv_proportion_socsecben_2007   
**Variable description**: Proportion of social security beneficiaries in residential area in 2007.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of social security beneficiaries in 2010  
**Variable name**: socenv_proportion_socsecben_2010   
**Variable description**: Proportion of social security beneficiaries in residential area in 2010.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of social security beneficiaries in 2011  
**Variable name**: socenv_proportion_socsecben_2011   
**Variable description**: Proportion of social security beneficiaries in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of social security beneficiaries in 2015  
**Variable name**: socenv_proportion_socsecben_2015   
**Variable description**: Proportion of social security beneficiaries in residential area in 2015.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of social security beneficiaries in 2016  
**Variable name**: socenv_proportion_socsecben_2016   
**Variable description**: Proportion of social security beneficiaries in residential area in 2016.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of residents with disability benefit in 2010  
**Variable name**: socenv_proportion_disben_2010   
**Variable description**: Proportion of residents with a disability benefit in residential area in 2010.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of residents with unemployment benefit in 2010  
**Variable name**: socenv_proportion_unemplben_2010   
**Variable description**: Proportion of residents with a unemployment benefit in residential area in 2010.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

# Educational level  

### **Variable label**: Proportion of low educated residents in 2011  
**Variable name**: socenv_prop_low_education_2011  
**Variable description**: Proportion of low educated residents in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of low educated residents in 2014 
**Variable name**: socenv_prop_low_education_2014  
**Variable description**: Proportion of low educated residents in residential area in 2014.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of intermediate educated residents in 2011  
**Variable name**: socenv_prop_itm_education_2011  
**Variable description**: Proportion of intermediate educated residents in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of intermediate educated residents in 2014  
**Variable name**: socenv_prop_itm_education_2014  
**Variable description**: Proportion of intermediate educated residents in residential area in 2014.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of high educated residents in 2011  
**Variable name**: socenv_prop_high_education_2011  
**Variable description**: Proportion of high educated residents in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of high educated residents in 2014  
**Variable name**: socenv_prop_high_education_2014  
**Variable description**: Proportion of high educated residents in residential area in 2014.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

# Immigrants and ethnic minority groups

### **Variable label**: Proportion of immigrants in 2011  
**Variable name**: socenv_prop_immigrants_2011
**Variable description**: Proportion of immigrants in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of western immigrants in 2006  
**Variable name**: socenv_prop_west_imgs_2006  
**Variable description**: Proportion of western immigrants in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of western immigrants in 2011  
**Variable name**: socenv_prop_west_imgs_2011  
**Variable description**: Proportion of western immigrants in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of non-western immigrants in 2006  
**Variable name**: socenv_prop_nonwest_imgs_2006  
**Variable description**: Proportion of non-western immigrants in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of non-western immigrants in 2011  
**Variable name**: socenv_prop_nonwest_imgs_2011  
**Variable description**: Proportion of non-western immigrants in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of immigrants of Moroccan origin in 2006  
**Variable name**: socenv_prop_moroccan_2006  
**Variable description**: Proportion of immigrants of Moroccan origin in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of immigrants of Moroccan origin in 2011  
**Variable name**: socenv_prop_moroccan_2011  
**Variable description**: Proportion of immigrants of Moroccan origin in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of immigrants of Antillian and Aruban origin in 2006  
**Variable name**: socenv_prop_antaru_2006  
**Variable description**: Proportion of immigrants of Antillian and Aruban origin in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of immigrants of Antillian and Aruban origin in 2011  
**Variable name**: socenv_prop_antaru_2011  
**Variable description**: Proportion of immigrants of Antillian and Aruban origin in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of immigrants of Surinamese origin in 2006  
**Variable name**: socenv_prop_surinamese_2006  
**Variable description**: Proportion of immigrants of Surinamese origin in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of immigrants of Surinamese origin in 2011  
**Variable name**: socenv_prop_surinamese_2011  
**Variable description**: Proportion of immigrants of Surinamese origin in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of immigrants of Turkish origin in 2006  
**Variable name**: socenv_prop_turkey_2006  
**Variable description**: Proportion of immigrants of Turkish origin in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of immigrants of Turkish origin in 2011  
**Variable name**: socenv_prop_turkey_2011  
**Variable description**: Proportion of immigrants of Turkish origin in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of immigrants of other origin in 2006  
**Variable name**: socenv_prop_other_2006  
**Variable description**: Proportion of immigrants of other origin in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of immigrants of other origin in 2011  
**Variable name**: socenv_prop_other_2011  
**Variable description**: Proportion of immigrants of other origin in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of foreigners in 2007  
**Variable name**: socenv_prop_foreigners_2007  
**Variable description**: Proportion of foreigners in residential area in 2007.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Proportion of foreigners in 2011  
**Variable name**: socenv_prop_foreigners_2011  
**Variable description**: Proportion of foreigners in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

# Crime  

### **Variable label**: Number of criminal offenses per 1000 residents in 2007  
**Variable name**: socenv_crimoff_2007    
**Variable description**: Number of criminal offenses per 1000 residents in residential area in 2007.       
**Variable type**: integer    
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of criminal offenses per 1000 residents in 2011  
**Variable name**: socenv_crimoff_2011    
**Variable description**: Number of criminal offenses per 1000 residents in residential area in 2011.       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of criminal offenses per 1000 residents in 2014    
**Variable name**: socenv_crimoff_2014    
**Variable description**: Number of criminal offenses per 1000 residents in residential area in 2014.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of criminal offenses per 1000 residents in 2015    
**Variable name**: socenv_crimoff_2015    
**Variable description**: Number of criminal offenses per 1000 residents in residential area in 2015.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of criminal offenses per 1000 residents in 2016    
**Variable name**: socenv_crimoff_2016    
**Variable description**: Number of criminal offenses per 1000 residents in residential area in 2016.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of violent crimes per 1000 residents in 2007  
**Variable name**: socenv_violentcrim_2007    
**Variable description**: Number of violent crimes per 1000 residents in residential area in 2007.       
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of violent crimes per 1000 residents in 2011    
**Variable name**: socenv_violentcrim_2011    
**Variable description**: Number of violent crimes per 1000 residents in residential area in 2011.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of violent crimes per 1000 residents in 2016    
**Variable name**: socenv_violentcrim_2016   
**Variable description**: Number of violent crimes per 1000 residents in residential area in 2016.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of thefts per 1000 residents in 2007  
**Variable name**: socenv_thefts_2007    
**Variable description**: Number of thefts per 1000 residents in residential area in 2007.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of thefts per 1000 residents in 2011    
**Variable name**: socenv_thefts_2011    
**Variable description**: Number of thefts per 1000 residents in residential area in 2011.       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of thefts per 1000 residents in 2016  
**Variable name**: socenv_thefts_2016    
**Variable description**: Number of thefts per 1000 residents in residential area in 2016.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of vandalism and public disorder per 1000 residents in 2011  
**Variable name**: socenv_vandalism_po_2011   
**Variable description**: Number of vandalism and public disorder per 1000 residents in residential area in 2011.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of vandalism and public disorder per 1000 residents in 2016    
**Variable name**: socenv_vandalism_po_2016   
**Variable description**: Number of vandalism and public disorder per 1000 residents in residential area in 2016.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of violent crimes and sexual offenses per 1000 residents in 2011    
**Variable name**: socenv_violentcrim_sexoff_2011    
**Variable description**: Number of violent crimes and sexual offenses per 1000 residents in residential area in 2011.         
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of violent crimes and sexual offenses per 1000 residents in 2016  
**Variable name**: socenv_violentcrim_sexoff_2016   
**Variable description**: Number of violent crimes and sexual offenses per 1000 residents in residential area in 2016.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of vandalism per 1000 residents in 2011   
**Variable name**: socenv_vandalism_2011    
**Variable description**: Number of vandalism per 1000 residents in residential area in 2011.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of vandalism per 1000 residents in 2016    
**Variable name**: socenv_vandalism_2016    
**Variable description**: Number of vandalism per 1000 residents in residential area in 2016.          
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of public disorder per 1000 residents in 2011    
**Variable name**: socenv_po_2011    
**Variable description**: Number of public disorder per 1000 residents in residential area in 2011.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

### **Variable label**: Number of public disorder per 1000 residents in 2016    
**Variable name**: socenv_po_2016    
**Variable description**: Number of public disorder per 1000 residents in residential area in 2016.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```    

