---
title: "Social environmental (i.e. geospatial) DataSchema"
output: html_document
---
# Table of Contents

---
title: "Social environmental (i.e. geospatial) DataSchema"
output: html_document
---
# Table of Contents
1. [Urbanization grade](#Urbanzation grade)  
2. [Demographics](#Demographics)  
3. [Housing](#Housing)  
4. [Income](#Income)  
5. [Unemployment](#Unemployment)  
6. [Social security](#Social security)  
7. [Educational level](#Educational level)  
8. [Immigrants and ethnic minority groups](#Immigrants and ethnic minority groups)  
9. [Crime](#Crime)
10. [Area indicators] (#Area indicators)
  

# Urbanization grade

### **Variable label**: Urbanization grade in 2006  
**Variable name**: socenv_urbanization_grade_2006    
**Variable description**: Population density of the residential area (number of residents per km2) in 2006.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}  
#This is where the R-script will be written  

```  

### **Variable label**: Urbanization grade in 2007 
**Variable name**: socenv_urbanization_grade_2007    
**Variable description**: Population density of the residential area (number of residents per km2) in 2007.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  

### **Variable label**: Urbanization grade in 2009 
**Variable name**: socenv_urbanization_grade_2009    
**Variable description**: Population density of the residential area (number of residents per km2) in 2009.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  

### **Variable label**: Urbanization grade in 2011 
**Variable name**: socenv_urbanization_grade_2011    
**Variable description**: Population density of the residential area (number of residents per km2) in 2011.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
```{r, echo=TRUE}
#This is where the R-script will be written

```  

### **Variable label**: Urbanization grade in 2014
**Variable name**: socenv_urbanization_grade_2014    
**Variable description**: Population density of the residential area (number of residents per km2) in 2014.  
**Variable type**: integer
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written  



# Demographics

### **Variable label**: Percentage of men in 2006  
**Variable name**: socenv_percentage_men_2006    
**Variable description**: Percentage of men in the residential area in 2006.  
**Variable type**: decimal
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of men in 2011  
**Variable name**: socenv_percentage_men_2011    
**Variable description**: Percentage of men in the residential area in 2011.  
**Variable type**: decimal
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of women in 2006  
**Variable name**: socenv_percentage_women_2006    
**Variable description**: Percentage of women in the residential area in 2006.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}  
#This is where the R-script will be written  



### **Variable label**: Percentage of women in 2011    
**Variable name**: socenv_percentage_women_2011    
**Variable description**: Percentage of women in the residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written


### **Variable label**: Percentage of residents aged 65 or older in 2006   
**Variable name**: socenv_percentage_65_older_2006   
**Variable description**: Percentage of residents aged 65 or older in residential area in 2006.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of residents aged 65 or older in 2007   
**Variable name**: socenv_percentage_65_older_2007   
**Variable description**: Percentage of residents aged 65 or older in residential area in 2007.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of residents aged 65 or older in 2011   
**Variable name**: socenv_percentage_65_older_2011   
**Variable description**: Percentage of residents aged 65 or older in residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of unmarried residents in 2008   
**Variable name**: socenv_percentage_unmarried_2008   
**Variable description**: Percentage of unmarried residents in residential area in 2008.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of unmarried residents in 2011   
**Variable name**: socenv_percentage_unmarried_2011   
**Variable description**: Percentage of unmarried residents in residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of married residents in 2006   
**Variable name**: socenv_percentage_married_2006   
**Variable description**: Percentage of married residents in residential area in 2006.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of married residents in 2008   
**Variable name**: socenv_percentage_married_2008   
**Variable description**: Percentage of married residents in residential area in 2008.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of married residents in 2011   
**Variable name**: socenv_percentage_married_2011   
**Variable description**: Percentage of married residents in residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of divorced residents in 2006   
**Variable name**: socenv_percentage_divorced_2006   
**Variable description**: Percentage of divorced residents in residential area in 2006.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of divorced residents in 2008   
**Variable name**: socenv_percentage_divorced_2008   
**Variable description**: Percentage of divorced residents in residential area in 2008.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of divorced residents in 2011   
**Variable name**: socenv_percentage_divorced_2011   
**Variable description**: Percentage of divorced residents in residential area in 2011.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of widowed residents in 2006   
**Variable name**: socenv_percentage_widowed_2006   
**Variable description**: Percentage of widowed residents in residential area in 2006.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of widowed residents in 2008     
**Variable name**: socenv_percentage_widowed_2008   
**Variable description**: Percentage of widowed residents in residential area in 2008.  
**Variable type**: decimal  
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of widowed residents in 2011    
**Variable name**: socenv_percentage_widowed_2011   
**Variable description**: Percentage of widowed residents in residential area in 2011.  
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average household size in 2006   
**Variable name**: socenv_average_hh_size_2006   
**Variable description**: Average household size in residential area in 2006.  
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average household size in 2009   
**Variable name**: socenv_average_hh_size_2009   
**Variable description**: Average household size in residential area in 2009.  
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average household size in 2011   
**Variable name**: socenv_average_hh_size_2011   
**Variable description**: Average household size in residential area in 2011.  
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written


### **Variable label**: Average household size in 2014   
**Variable name**: socenv_average_hh_size_2014   
**Variable description**: Average household size in residential area in 2014.  
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average household size in 2015      
**Variable name**: socenv_average_hh_size_2015     
**Variable description**: Average household size in residential area in 2015.    
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average household size in 2016      
**Variable name**: socenv_average_hh_size_2016      
**Variable description**: Average household size in residential area in 2016.    
**Variable type**: integer   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



# Housing


### **Variable label**: Average value of dwellings in 1000 euros in 2006    
**Variable name**: socenv_avv_dwellings_2006  
**Variable description**: Average value of dwellings in 1000 euros in residential area in 2006.    
**Variable type**: integer   
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average value of dwellings in 1000 euros in 2011    
**Variable name**: socenv_avv_dwellings_2011  
**Variable description**: Average value of dwellings in 1000 euros in residential area in 2011.    
**Variable type**: integer   
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written


### **Variable label**: Average value of a plot (m2) in euros in 2007 (dwellings)    
**Variable name**: socenv_avv_dwelling_m2_2007  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area in 2007.    
**Variable type**: integer   
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average value of a plot (m2) in euros in 2011 (dwellings)  
**Variable name**: socenv_avv_dwelling_m2_2011  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area in 2011.    
**Variable type**: integer   
**Variable unit**: euros   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average value of a plot (m2) in euros in 2013 (dwellings)  
**Variable name**: socenv_avv_dwelling_m2_2013  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area in 2013.    
**Variable type**: integer   
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average value of a plot (m2) in euros in 2014 (dwellings)  
**Variable name**: socenv_avv_dwelling_m2_2014  
**Variable description**: Average value of a plot in euros (dwellings) in the residential area in 2014.    
**Variable type**: integer   
**Variable unit**: euros   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average value of a plot (m2) in euros in 2015 (dwellings)  
**Variable name**: socenv_avv_dwelling_m2_2015   
**Variable description**: Average value of a plot in euros (dwellings) in the residential area in 2015.    
**Variable type**: integer   
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of unoccupied dwellings in 2011   
**Variable name**: socenv_perc_unocc_dwellings_2011
**Variable description**: Percentage of unoccupied dwellings in residential area in 2011.    
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of unoccupied dwellings in 2012   
**Variable name**: socenv_perc_unocc_dwellings_2012
**Variable description**: Percentage of unoccupied dwellings in residential area in 2012.    
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of unoccupied dwellings in 2014   
**Variable name**: socenv_perc_unocc_dwellings_2012
**Variable description**: Percentage of unoccupied dwellings in residential area in 2012.    
**Variable type**: decimal   
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



# Income



### **Variable label**: Average income in 1000 euros in 2005  
**Variable name**: socenv_av_inc1000_2005  
**Variable description**: Average income in 1000 euros of residents in residential area in 2005.    
**Variable type**: integer     
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in 1000 euros in 2006  
**Variable name**: socenv_av_inc1000_2006 
**Variable description**: Average income in 1000 euros of residents in residential area in 2006.    
**Variable type**: integer     
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in 1000 euros in 2011   
**Variable name**: socenv_av_inc1000_2011 
**Variable description**: Average income in 1000 euros of residents in residential area in 2011.    
**Variable type**: integer     
**Variable unit**: 1000 euros  
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in euros in 2006  
**Variable name**: socenv_av_inc_2006  
**Variable description**: Average income in euros of residents in residential area in 2006.    
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in euros in 2007  
**Variable name**: socenv_av_inc_2007
**Variable description**: Average income in euros of residents in residential area in 2007.    
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in euros in 2011  
**Variable name**: socenv_av_inc_2011  
**Variable description**: Average income in euros of residents in residential area in 2011.    
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in euros in 2013  
**Variable name**: socenv_av_inc_2013  
**Variable description**: Average income in euros of residents in residential area in 2013.    
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in euros in 2014  
**Variable name**: socenv_av_inc_2014  
**Variable description**: Average income in euros of residents in residential area in 2014.    
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in euros in 2015  
**Variable name**: socenv_av_inc_2015  
**Variable description**: Average income in euros of residents in residential area in 2015.    
**Variable type**: integer     
**Variable unit**: euros   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in euros in 2016  
**Variable name**: socenv_av_inc_2016  
**Variable description**: Average income in euros of residents in residential area in 2016.    
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in 1000 euros in 2005 (dichotomized)  
**Variable name**: socenv_av_incdich1000_2005  
**Variable description**: Average income in 1000 euros of residents in residential area in 2005 (dichotomized: below/above country-specific net mean household income (OECD)).    
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in 1000 euros in 2006 (dichotomized) 
**Variable name**: socenv_av_inc1000dich_2006 
**Variable description**: Average income in 1000 euros of residents in residential area in 2006 (dichotomized: below/above country-specific net mean household income (OECD)).   
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in 1000 euros in 2011 (dichotomized)   
**Variable name**: socenv_av_inc1000dich_2011 
**Variable description**: Average income in 1000 euros of residents in residential area in 2011 (dichotomized: below/above country-specific net mean household income (OECD)).      
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in euros in 2006 (dichotomized) 
**Variable name**: socenv_av_incdich_2006  
**Variable description**: Average income in euros of residents in residential area in 2006 (dichotomized: below/above country-specific net mean household income (OECD)).     
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in euros in 2007 (dichotomized)  
**Variable name**: socenv_av_incdich_2007
**Variable description**: Average income in euros of residents in residential area in 2007 (dichotomized: below/above country-specific net mean household income (OECD)).      
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in euros in 2011 (dichotomized)  
**Variable name**: socenv_av_incdich_2011 
**Variable description**: Average income in euros of residents in residential area in 2011 (dichotomized: below/above country-specific net mean household income (OECD)).      
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in euros in 2013 (dichotomized)  
**Variable name**: socenv_av_incdich_2013  
**Variable description**: Average income in euros of residents in residential area in 2013 (dichotomized: below/above country-specific net mean household income (OECD)).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in euros in 2014 (dichotomized)  
**Variable name**: socenv_av_incdich_2014  
**Variable description**: Average income in euros of residents in residential area in 2014 (dichotomized: below/above country-specific net mean household income (OECD)).     
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in euros in 2015 (dichotomized)  
**Variable name**: socenv_av_incdich_2015  
**Variable description**: Average income in euros of residents in residential area in 2015 (dichotomized: below/above country-specific net mean household income (OECD)).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in euros in 2016 (dichotomized) 
**Variable name**: socenv_av_incdich_2016  
**Variable description**: Average income in euros of residents in residential area in 2016 (dichotomized: below/above country-specific net mean household income (OECD)).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average household income in euros in 2006
**Variable name**: socenv_av_hhinc_500m_2006  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address in 2006 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average household income in euros in 2006
**Variable name**: socenv_av_hhinc_1000m_2006  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address in 2006 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**: euros  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average household income in euros in 2006
**Variable name**: socenv_av_hhinc_2000m_2006  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address in 2006 
**Variable type**: integer     
**Variable unit**: euros  
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average household income in euros in 2006 (dichotomized)
**Variable name**: socenv_av_hhincdich_500m_2006  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address in 2006 (dichotomized: below/above country-specific net mean household income (OECD)).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average household income in euros in 2006 (dichotomized)
**Variable name**: socenv_av_hhincdich_1000m_2006  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address in 2006 (dichotomized: below/above country-specific net mean household income (OECD)).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average household income in euros in 2006 (dichotomized)
**Variable name**: socenv_av_hhincdich_2000m_2006  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address in 2006 (dichotomized: below/above country-specific net mean household income (OECD)).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:  

**Code** | **Category Label**  
------------- | -------------  
0 | Less than or equal to country-specific net mean household income
1 | Greater than country-specific net mean household income   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in 1000 euros in 2005 (Z standardised)  
**Variable name**: socenv_av_inc1000Z_2005  
**Variable description**: Average income in 1000 euros of residents in residential area in 2005 (standardized: mean=0 and sd=1)
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**: 
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in 1000 euros in 2006 (Z standardized)  
**Variable name**: socenv_av_inc1000Z_2006 
**Variable description**: Average income in 1000 euros of residents in residential area in 2006 (standardized: mean=0 and sd=1)      
**Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**: 
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written
 

### **Variable label**: Average income in 1000 euros in 2011 (Z standardized)   
**Variable name**: socenv_av_inc1000Z_2011 
**Variable description**: Average income in 1000 euros of residents in residential area in 2011 (standardized: mean=0 and sd=1)   
**Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**: 
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written   



### **Variable label**: Average income in euros in 2006 (Z standardized)  
**Variable name**: socenv_av_incZ_2006  
**Variable description**: Average income in euros of residents in residential area in 2006 (standardized: mean=0 and sd=1) 
**Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**: 
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written    



### **Variable label**: Average income in euros in 2007 (Z standardized) 
**Variable name**: socenv_av_incZ_2007
**Variable description**: Average income in euros of residents in residential area in 2007 (standardized: mean=0 and sd=1)        
**Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**: 
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written  



### **Variable label**: Average income in euros in 2011 (Z standardized)  
**Variable name**: socenv_av_incZ_2011  
**Variable description**: Average income in euros of residents in residential area in 2011 (standardized: mean=0 and sd=1)        
**Variable type**: integer     
**Variable unit**:     
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**: 
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written  



### **Variable label**: Average income in euros in 2013 (Z standardized)  
**Variable name**: socenv_av_incZ_2013
**Variable description**: Average income in euros of residents in residential area in 2013 (standardized: mean=0 and sd=1)      
**Variable type**: integer     
**Variable unit**:    
**Category coding**:  

**Harmonization status**:  
**Harmonization comment**: 
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written

### **Variable label**: Average income in euros in 2014 (Z standardized) 
**Variable name**: socenv_av_incZ_2014  
**Variable description**: Average income in euros of residents in residential area in 2014 (standardized: mean=0 and sd=1)       
**Variable type**: integer     
**Variable unit**:  
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**: 
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average income in euros in 2015 (Z standardized) 
**Variable name**: socenv_av_incZ_2015  
**Variable description**: Average income in euros of residents in residential area in 2015 (standardized: mean=0 and sd=1)    
**Variable type**: integer     
**Variable unit**:    
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**: 
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written  

### **Variable label**: Average income in euros in 2016 (Z standardized)  
**Variable name**: socenv_av_incZ_2016  
**Variable description**: Average income in euros of residents in residential area in 2016 (standardized: mean=0 and sd=1)    
**Variable type**: integer     
**Variable unit**:     
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**: 
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written 

### **Variable label**: Average household income in euros in 2006 (Z standardized)
**Variable name**: socenv_av_hhincZ_500m_2006  
**Variable description**: Average household income in euros in 500 meter street network buffer zone around participants address in 2006 (standardized: mean=0 and sd=1)    .       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**: 
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average household income in euros in 2006 (Z standardized)
**Variable name**: socenv_av_hhincZ_1000m_2006  
**Variable description**: Average household income in euros in 1000 meter street network buffer zone around participants address in 2006 (standardized: mean=0 and sd=1).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**: 
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Average household income in euros in 2006 (Z standardized)
**Variable name**: socenv_av_hhincZ_2000m_2006  
**Variable description**: Average household income in euros in 2000 meter street network buffer zone around participants address in 2006 (standardized: mean=0 and sd=1).       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**: 
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of income recipients in 2005
**Variable name**: socenv_perc_inc_recipients_2005  
**Variable description**: Percentage of income recipients in residential area in 2005.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written


### **Variable label**: Percentage of income recipients in 2011  
**Variable name**: socenv_perc_inc_recipients_2011  
**Variable description**: Percentage of income recipients in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



# Unemployment



### **Variable label**: Percentage of unemployed residents in 2006  
**Variable name**: socenv_perc_unemployment_2006  
**Variable description**: Percentage of unemployed residents in residential area in 2006.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of unemployed residents in 2007    
**Variable name**: socenv_perc_unemployment_2007    
**Variable description**: Percentage of unemployed residents in residential area in 2007.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of unemployed residents in 2011    
**Variable name**: socenv_perc_unemployment_2011    
**Variable description**: Percentage of unemployed residents in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of unemployed residents in 2014  
**Variable name**: socenv_perc_unemployment_2014  
**Variable description**: Percentage of unemployed residents in residential area in 2014.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of unemployed residents in 2015  
**Variable name**: socenv_perc_unemployment_2015  
**Variable description**: Percentage of unemployed residents in residential area in 2015.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



# Social security



### **Variable label**: Percentage of social security beneficiaries in 2006  
**Variable name**: socenv_percentage_socsecben_2006   
**Variable description**: Percentage of social security beneficiaries in residential area in 2006.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of social security beneficiaries in 2007    
**Variable name**: socenv_percentage_socsecben_2007   
**Variable description**: Percentage of social security beneficiaries in residential area in 2007.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of social security beneficiaries in 2010  
**Variable name**: socenv_percentage_socsecben_2010   
**Variable description**: Percentage of social security beneficiaries in residential area in 2010.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of social security beneficiaries in 2011  
**Variable name**: socenv_percentage_socsecben_2011   
**Variable description**: Percentage of social security beneficiaries in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of social security beneficiaries in 2015  
**Variable name**: socenv_percentage_socsecben_2015   
**Variable description**: Percentage of social security beneficiaries in residential area in 2015.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of social security beneficiaries in 2016  
**Variable name**: socenv_percentage_socsecben_2016   
**Variable description**: Percentage of social security beneficiaries in residential area in 2016.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of residents with disability benefit in 2006  
**Variable name**: socenv_percentage_disben_2006   
**Variable description**: Percentage of residents with a disability benefit in residential area in 2006.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of residents with disability benefit in 2010  
**Variable name**: socenv_percentage_disben_2010   
**Variable description**: Percentage of residents with a disability benefit in residential area in 2010.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written


### **Variable label**: Percentage of residents with unemployment benefit in 2006  
**Variable name**: socenv_percentage_unemplben_2006   
**Variable description**: Percentage of residents with a unemployment benefit in residential area in 2006.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of residents with unemployment benefit in 2010  
**Variable name**: socenv_percentage_unemplben_2010   
**Variable description**: Percentage of residents with a unemployment benefit in residential area in 2010.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



# Educational level  



### **Variable label**: Percentage of low educated residents in 2011  
**Variable name**: socenv_perc_low_education_2011  
**Variable description**: Percentage of low educated residents in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of low educated residents in 2014 
**Variable name**: socenv_perc_low_education_2014  
**Variable description**: Percentage of low educated residents in residential area in 2014.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of intermediate educated residents in 2011  
**Variable name**: socenv_perc_itm_education_2011  
**Variable description**: Percentage of intermediate educated residents in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of intermediate educated residents in 2014  
**Variable name**: socenv_perc_itm_education_2014  
**Variable description**: Percentage of intermediate educated residents in residential area in 2014.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of high educated residents in 2011  
**Variable name**: socenv_perc_high_education_2011  
**Variable description**: Percentage of high educated residents in residential area in 2011.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of high educated residents in 2014  
**Variable name**: socenv_perc_high_education_2014  
**Variable description**: Percentage of high educated residents in residential area in 2014.    
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



# Immigrants and ethnic minority groups



### **Variable label**: Percentage of immigrants in 2011  
**Variable name**: socenv_perc_immigrants_2011
**Variable description**: Percentage of immigrants in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written

### **Variable label**: Percentage of western immigrants in 2006  
**Variable name**: socenv_perc_west_imgs_2006  
**Variable description**: Percentage of western immigrants in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of western immigrants in 2011  
**Variable name**: socenv_perc_west_imgs_2011  
**Variable description**: Percentage of western immigrants in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of non-western immigrants in 2006  
**Variable name**: socenv_perc_nonwest_imgs_2006  
**Variable description**: Percentage of non-western immigrants in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of non-western immigrants in 2011  
**Variable name**: socenv_perc_nonwest_imgs_2011  
**Variable description**: Percentage of non-western immigrants in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of immigrants of Moroccan origin in 2006  
**Variable name**: socenv_perc_moroccan_2006  
**Variable description**: Percentage of immigrants of Moroccan origin in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of immigrants of Moroccan origin in 2011  
**Variable name**: socenv_perc_moroccan_2011  
**Variable description**: Percentage of immigrants of Moroccan origin in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of immigrants of Antillian and Aruban origin in 2006  
**Variable name**: socenv_perc_antaru_2006  
**Variable description**: Percentage of immigrants of Antillian and Aruban origin in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of immigrants of Antillian and Aruban origin in 2011  
**Variable name**: socenv_perc_antaru_2011  
**Variable description**: Percentage of immigrants of Antillian and Aruban origin in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written


### **Variable label**: Percentage of immigrants of Surinamese origin in 2006  
**Variable name**: socenv_perc_surinamese_2006  
**Variable description**: Percentage of immigrants of Surinamese origin in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of immigrants of Surinamese origin in 2011  
**Variable name**: socenv_perc_surinamese_2011  
**Variable description**: Percentage of immigrants of Surinamese origin in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of immigrants of Turkish origin in 2006  
**Variable name**: socenv_perc_turkey_2006  
**Variable description**: Percentage of immigrants of Turkish origin in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of immigrants of Turkish origin in 2011  
**Variable name**: socenv_perc_turkey_2011  
**Variable description**: Percentage of immigrants of Turkish origin in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of immigrants of other origin in 2006  
**Variable name**: socenv_perc_other_2006  
**Variable description**: Percentage of immigrants of other origin in residential area in 2006.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of immigrants of other origin in 2011  
**Variable name**: socenv_perc_other_2011  
**Variable description**: Percentage of immigrants of other origin in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of foreigners in 2007  
**Variable name**: socenv_perc_foreigners_2007  
**Variable description**: Percentage of foreigners in residential area in 2007.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Percentage of foreigners in 2011  
**Variable name**: socenv_perc_foreigners_2011  
**Variable description**: Percentage of foreigners in residential area in 2011.      
**Variable type**: decimal     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written

# Crime  


### **Variable label**: Number of criminal offenses per 1000 residents in 2007  
**Variable name**: socenv_crimoff_2007    
**Variable description**: Number of criminal offenses per 1000 residents in residential area in 2007.       
**Variable type**: integer    
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of criminal offenses per 1000 residents in 2011  
**Variable name**: socenv_crimoff_2011    
**Variable description**: Number of criminal offenses per 1000 residents in residential area in 2011.       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of criminal offenses per 1000 residents in 2014    
**Variable name**: socenv_crimoff_2014    
**Variable description**: Number of criminal offenses per 1000 residents in residential area in 2014.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of criminal offenses per 1000 residents in 2015    
**Variable name**: socenv_crimoff_2015    
**Variable description**: Number of criminal offenses per 1000 residents in residential area in 2015.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of criminal offenses per 1000 residents in 2016    
**Variable name**: socenv_crimoff_2016    
**Variable description**: Number of criminal offenses per 1000 residents in residential area in 2016.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of violent crimes per 1000 residents in 2007  
**Variable name**: socenv_violentcrim_2007    
**Variable description**: Number of violent crimes per 1000 residents in residential area in 2007.       
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of violent crimes per 1000 residents in 2011    
**Variable name**: socenv_violentcrim_2011    
**Variable description**: Number of violent crimes per 1000 residents in residential area in 2011.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of violent crimes per 1000 residents in 2016    
**Variable name**: socenv_violentcrim_2016   
**Variable description**: Number of violent crimes per 1000 residents in residential area in 2016.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of thefts per 1000 residents in 2007  
**Variable name**: socenv_thefts_2007    
**Variable description**: Number of thefts per 1000 residents in residential area in 2007.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of thefts per 1000 residents in 2011    
**Variable name**: socenv_thefts_2011    
**Variable description**: Number of thefts per 1000 residents in residential area in 2011.       
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of thefts per 1000 residents in 2016  
**Variable name**: socenv_thefts_2016    
**Variable description**: Number of thefts per 1000 residents in residential area in 2016.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of vandalism and public disorder per 1000 residents in 2011  
**Variable name**: socenv_vandalism_po_2011   
**Variable description**: Number of vandalism and public disorder per 1000 residents in residential area in 2011.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of vandalism and public disorder per 1000 residents in 2016    
**Variable name**: socenv_vandalism_po_2016   
**Variable description**: Number of vandalism and public disorder per 1000 residents in residential area in 2016.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of violent crimes and sexual offenses per 1000 residents in 2011    
**Variable name**: socenv_violentcrim_sexoff_2011    
**Variable description**: Number of violent crimes and sexual offenses per 1000 residents in residential area in 2011.         
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of violent crimes and sexual offenses per 1000 residents in 2016  
**Variable name**: socenv_violentcrim_sexoff_2016   
**Variable description**: Number of violent crimes and sexual offenses per 1000 residents in residential area in 2016.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of vandalism per 1000 residents in 2011   
**Variable name**: socenv_vandalism_2011    
**Variable description**: Number of vandalism per 1000 residents in residential area in 2011.        
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of vandalism per 1000 residents in 2016    
**Variable name**: socenv_vandalism_2016    
**Variable description**: Number of vandalism per 1000 residents in residential area in 2016.          
**Variable type**: integer     
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of public disorder per 1000 residents in 2011    
**Variable name**: socenv_po_2011    
**Variable description**: Number of public disorder per 1000 residents in residential area in 2011.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Number of public disorder per 1000 residents in 2016    
**Variable name**: socenv_po_2016    
**Variable description**: Number of public disorder per 1000 residents in residential area in 2016.        
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



#Area indicators

### **Variable label**: Area indicator: city 
**Variable name**: socenv_city_2004    
**Variable description**: City indicator in 2004    
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Area indicator: city 
**Variable name**: socenv_city_2006    
**Variable description**: City indicator in 2006    
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Area indicator: city 
**Variable name**: socenv_city_2007    
**Variable description**: City indicator in 2007    
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Area indicator: city 
**Variable name**: socenv_city_2009    
**Variable description**: City indicator in 2009    
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Area indicator: city 
**Variable name**: socenv_city_2011    
**Variable description**: City indicator in 2011    
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Area indicator: city 
**Variable name**: socenv_city_2014    
**Variable description**: City indicator in 2014   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Area indicator: municipality
**Variable name**: socenv_municipality_2004    
**Variable description**: Municipality indicator in 2004   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Area indicator: municipality
**Variable name**: socenv_municipality_2006    
**Variable description**: Municipality indicator in 2006   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Area indicator: municipality
**Variable name**: socenv_municipality_2007    
**Variable description**: Municipality indicator in 2007   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Area indicator: municipality
**Variable name**: socenv_municipality_2011    
**Variable description**: Municipality indicator in 2011   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Area indicator: municipality
**Variable name**: socenv_municipality_2014    
**Variable description**: Municipality indicator in 2014   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Area indicator: municipality
**Variable name**: socenv_municipality_2016    
**Variable description**: Municipality indicator in 2016   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Area indicator: neighbourhood
**Variable name**: socenv_neighbourhood_2004    
**Variable description**: Neighbourhood indicator in 2004   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Area indicator: neighbourhood
**Variable name**: socenv_neighbourhood_2006    
**Variable description**: Neighbourhood indicator in 2006  
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Area indicator: neighbourhood
**Variable name**: socenv_neighbourhood_2007    
**Variable description**: Neighbourhood indicator in 2007  
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Area indicator: neighbourhood
**Variable name**: socenv_neighbourhood_2009    
**Variable description**: Neighbourhood indicator in 2009   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Area indicator: neighbourhood
**Variable name**: socenv_neighbourhood_2011    
**Variable description**: Neighbourhood indicator in 2011   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Area indicator: neighbourhood
**Variable name**: socenv_neighbourhood_2014    
**Variable description**: Neighbourhood indicator in 2014   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written




### **Variable label**: Area indicator: 4-digit postal code
**Variable name**: socenv_pc4_2004    
**Variable description**:  4-digit postal code (PC4) indicator in 2004   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Area indicator: 4-digit postal code
**Variable name**: socenv_pc4_2006    
**Variable description**:  4-digit postal code (PC4) indicator in 2006  
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Area indicator: 4-digit postal code
**Variable name**: socenv_pc4_2011   
**Variable description**:  4-digit postal code (PC4) indicator in 2011   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Area indicator: 4-digit postal code
**Variable name**: socenv_pc4_2014    
**Variable description**:  4-digit postal code (PC4) indicator in 2014   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Area indicator: 6-digit postal code
**Variable name**: socenv_pc6_2004    
**Variable description**:  6-digit postal code (PC6) indicator in 2004   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Area indicator: 6-digit postal code
**Variable name**: socenv_pc6_2006    
**Variable description**:  6-digit postal code (PC6) indicator in 2006  
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Area indicator: 6-digit postal code
**Variable name**: socenv_pc6_2011   
**Variable description**:  6-digit postal code (PC6) indicator in 2011   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Area indicator: 6-digit postal code
**Variable name**: socenv_pc6_2014    
**Variable description**:  6-digit postal code (PC6) indicator in 2014   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Area indicator: 5-digit postal code
**Variable name**: socenv_pc5_2007    
**Variable description**:  5-digit postal code (PC5) indicator in 2007   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written



### **Variable label**: Area indicator: 5-digit postal code
**Variable name**: socenv_pc5_2011    
**Variable description**:  5-digit postal code (PC5) indicator in 2011   
**Variable type**: integer      
**Variable unit**:   
**Category coding**:   

**Harmonization status**:  
**Harmonization comment**:  
**R script**:  
{r, echo=TRUE}
#This is where the R-script will be written


